### 2010-12-07 articles/MIG/doc_broullion/latex/paper-drop.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\begin{document}

\title[Macro drop and droplet profile detection during PGMAW process by image processing library]{Macro drop and droplet profile detection during PGMAW process by image processing library}

\author{E Romero, C Bordreuil, J Chapuis, F Souliez, G Fras}

\address{IOP 
Publishing, Dirac
House, Temple Back, Bristol BS1 6BE, UK}
\ead{custserv@iop.org}
\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals published by IOP Publishing.
Authors submitting to any IOP journal, i.e.\ 
both single- and double-column ones, should follow the guidelines set out here. 
On acceptance, their TeX code will be converted to 
the appropriate format for the journal concerned.

\end{abstract}

%Uncomment for PACS numbers title message
%\pacs{00.00, 20.00, 42.10}
% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
%\vspace{2pc}
%\noindent{\it Keywords}: Article preparation, IOP journals
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
% Comment out if separate title page not required
\maketitle

\section{Introduction}
A better comprehension of welding objects behavior presents a PGMAW process as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
 and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}. An example to this are the problems linked to productivity. To some process, 
 increase productivity mean increase weld speed, however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
 speed \cite{CHAPUIS} and therefore the productivity. In a PGMAW process the weld quality is strongly relates with the metal transfer process stability 
 (the droplet deposition), then control of metal transfer process implies control of weld quality \cite{WANG}. In both example cases a macro drop kinetic
  study and a droplet dynamic analysis could help to better understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
  fluctuations \cite{WANG} or guarantee the welding quality. In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
  geometrical analysis of macro drop and droplets in order to extract qualitative information of these welding objects.

There have been many studies on visual sensing techniques for observing weld pool image \cite{BAE} and metal transfer process during welding \cite{LIN}.
Optical sensors like high speed CCD cameras and lighting systems have been widely use in GMAW process to realize image acquisition \cite{GUANGJUN},
   control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}. Then image processing plays a critical role in 
   extracting useful information from visual scenes \cite{WANG}. Nevertheless the strong interference from the arc lightning required more than standard 
   image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. Previous work has shown that is possible to perform geometrical 
   analysis in weld pools or droplets \cite{WU2}. Parameters such as macro drop or droplets surface, volumes or height has been measure using different and 
   specifics processing images algorithms \cite{WANG}, \cite{WU2}, \cite{SEED}, \cite{NORDBRUCH}. However, to date, effectively automatic images processing
    of metal transfer has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.

To perform geometrical analysis in macro drop and droplet; a multipurpose C++ based library (erCv) was developed by the Weld/Assembly group of 
    LMGC laboratory. These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical 
    analysis, graph theory applications and image visualization.

In a first step, and despite the different static and dynamic weld conditions, as well as different current regime. A reliable 2D profiles and geometrical
     parameters from macro drop and droplets, has been obtained using the mentioned library. Using this, a dimension and dimensionless analysis has 
     been performing. The intention is to help to simplified futures numerical models of humping phenomena and quality process.

\section{Problems description}
Bradstreet was the first researcher to experimentally study the bead hump formation \cite{CHO}. 
Humping was defined as the series of undulations of the weld bead. Further studies as computer 
simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition
 and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}

Then the shape and size kinetic analysis of macro drop and droplets could help to better understand 
 and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a 
 first step, a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
  is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is 
  one of the only way to access these quantities. Due to the arc light interference and the relatively high 
  speed of wire feed process, a high speed camera and an effective image processing algorithms are 
  required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
  per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others)
   from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related 
   with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies 
   frames and electrical signals.

\section{Image processing background} 
Some definitions and brief description of generals principles used in image processing are required to better understand how is work the algorithms utilized by the erCv library.

\subsection{Some definitions}
\label{some_definitions}

A numerical grey image can be describe as 3D surface discretized by a grid mesh in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis, the grey level.

A strong relief change or high gradient greyness values at the image are perceive by human eyes as light changes, and can be interpreted as objects edges. 
Sometimes, a regular relief patrons or regular greyness variation can be distinguish. The human eyes can perceive these patrons as texture 
and interpret the space between different textures zones as edges.
There exist a large spectrum of algorithms to image treatment, in particular to edges detect. Most of them can be classified by the way that his operate above the image pixels and grey level.

\subsection{Filters}
\label{filters}

The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the 
image; this allows the filter a better edges localisation (see figure \ref{photo-explication-filter}). For this reason, Canny filter is widely 
use at erCv library to detect the welding elements edges. However, it is sensible to noise or secondary greyness gradients in the image
 and, in consequence, it have some difficulties to define closer surface.

\subsection{Snake and level set}
\label{snake-and-level-set}

Curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure 
\ref{photo-explication-snake}). The central idea behind such an approach is to evolve a curve towards the lowest potential of a cost function. 
However at each stage of curve evolution, each curve point potential has to be computed. A lot of point (better curve resolution) take a lot 
computing time, and therefore are not yet apply to real time detection or relatively speed automatic image processing. For this reason snake algorithms are not used at erCv.

\subsection{Segmentation}
\label{segmentation}

Let $B$ an image and let $R_{i}$ a region of $B$ such:

\begin{equation}
B = \bigcup_{i}R_{i} 
\forall i  R_{i} \neq \emptyset
\forall i, j avec i \neq j\ R_{i}\bigcap R_{j} = \emptyset
\label{equation-segmentation}
\end{equation}

A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. Each region is a connected set of pixels with 
common properties (intensity, texture,...) \cite{COCQUEREZ}. The partition is generated by operations or comparisons methods between 
regions. Generally, this treatment offers a good detection edges if the elements and surrounding area have different textures (see figure \ref{photo-explication-segmentation}). 
Note that different regions can belong to the same partition and not be placed together, therefore the surface is not always connected and,
 in consequence, the edges of the interest regions are not always closed.

\begin{figure}[h!]
\begin{center}    
\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
\subfigure[Canny filter treatment]{\label{photo-explication-filters}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filters.png}}\\
\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
\end{center}
\caption{{\small Samples of different methods technique for image processing}}
\label{photo-explication}
\end{figure}

\section{Image treatment library (erCv)}
\label{image-treatment-library-ercv}

As mentioned, a multipurpose image processing library was developed and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different welding objects such: Macro drop, droplets and weld pool.
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable and portable library able to perform real time
 contour detection. erCv is build in Phyton scripts link to C++, making it relatively convivial to use.
erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and noise. In order to obtain the real shape and size of weld elements, this module 
 include calibrations algorithms. To detect the welding objects contours it is necessary to improve the weld element image. This module has the 
 pre-processing treatments to noise reduction and image enhancement. Then to start the edges detection process, this module includes processing
  algorithms as segmentations by samples comparators, watershed transformation, filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module has to end the edge detection process, completing and in some cases extrapolating the weld
   elements edge. It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes. 
   This module uses a full geometry algorithm library, which include different algorithms such as triangulations and mesh generation, alpha shape and 
   convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closer condition.  This module use graph algorithms to convert edges pixels points into connected 
   segments, and therefore, identify and select the welding element edge using the criteria. This module is compose by connect segments, estimates
    minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of functions use to execute, show and/or register the different steps at the image process.
\end{description}

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
\caption{{\small Flow diagram of erCv library composition}}
\label{schema-erCv}
\end{center}
\end{figure}
\end{itemize}

\section{Experimental Setup}
\label{experimental_setup}

\subsection{Multi-physics platform}
\label{multi_physics_platform}

The objective is to perform geometrical analysis and measure characteristic times of the macro drop and the droplet in a PGMAW process. Notes that
 geometrical analysis refers to area section of droplets, height profile of macro drop and wetting contacts angles of the macro drop. And characteristics 
 time’s measures refer to time to height stagnation of macro drop and fall time of droplet between electrodes. The methods choose is the image treatment 
 of recorded image of PGMAW static process by a high speed CCD camera.

To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; therefore an accurate, reliable and synchronizes 
 systems are requires due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).

A platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}). The platform 
 was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go
  per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-platform.png}
\caption{{\small Experimental platform and specific device}}
\label{schema-platform}
\end{center}
\end{figure}

To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data 
  and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).

\subsection{ Image acquisition setup}
\label{ image_acquisition_setup}

The PGMAW static process is recorded by Shadowgraphy optical method. A halogen lamp is use to light the weld process. To guarantee a homogeneous illumination 
  of the welding process, a light diffuser is place in the optical path closer to the halogen lamp. Finally the shadows of welding elements are projected to the other side 
  of the welding place. A Phantom V5.0 high speed camera is place and align at this side above the optical path (see figure \ref{schema-montage-experimental-GMAW}).

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-montage-experimental-GMAW.png}
\caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
\label{schema-montage-experimental-GMAW}
\end{center}
\end{figure}

To enhance the image contrast of the weld elements inside the electric discharge, the intensity rate between arc light and halogen lamp have to be reduce. In order to this
   a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens, to attenuate the arc light. Nevertheless, the raw images remain highly noisy by the arc light.

\subsection{ Welding condition}
\label{ welding_conditions}

Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. The target is a steel disk of $10\ mm$ of thickness and ER70S steel 
   welding wire.
The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and percentage
    of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon). Welding parameters values are summarize in tables \ref{table-parameters-static} to static and 
    \ref{table-parameters-change} to variables parameters.

\begin{table}
\begin{center}
\begin{tabular}{|cc|}
\hline
Welding wire type & ER70S \\ 
Wire diameter ($mm$) or $drw$ & 1 \\  
Contact tip to work distance ($mm$) & 20 \\
Shielding gaz flowrate ($l/min$) & 18 \\ \hline
\end{tabular}
\caption{{\small Determined constant welding parameters used in experiments}}
\label{table-parameters-static}
\end{center}
\end{table}

\begin{table}
begin{center}
\begin{tabular}{|cc|}
\hline
Welding wire type & ER70S \\ 
Wire diameter ($mm$) or $drw$ & 1 \\  
Contact tip to work distance ($mm$) & 20 \\
Shielding gaz flowrate ($l/min$) & 18 \\ \hline
\end{tabular}
\caption{{\small Variable welding parameters used in experiments}}
\label{table-parameters-change}
\end{center}
\end{table}

Welding current and arc voltage are recorded at $30\ kHz$ sampling rate. The images are recorded at $4000$ frames per seconds, which is enough to
     measure macro drop radius and apparent liquid-solid contact angle histories. The images and electrical signals are synchronize, thanks to the
      automatically approach made in the multi physics platform.

Measurements are made using the erCv library.

\section{ System definitions}
\label{system_definitions}
\subsection{ Macro Drop}
\label{ macro_drop}

The purpose is to study the evolution of weld pool object in a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
 of the macro drop according depositing droplets of feed wire.

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
\caption{{\small Profile schematics of welding objects in a GMAW process}
\label{schema-macro-drop-droplet-parameters}
\end{center}
\end{figure}

At figure \ref{figure_1} appears the geometrical elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, the macro drop
  center height $h_{m}$, the macro drop volume $V_{m}$, the penetration below the surface level $p$ and the wetting angles:
   $\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real). With the indices $l$ and $r$ refer to left and
    right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.

\subsection{ Metal Transfer Drop}
\label{ metam_transfer_drop}

To the droplet or metal transfer drop the geometrical parameters to identify are: The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
    Finally in order to better understand the droplet dynamic \cite{}, the physical elements to identify are: the fall time $t_{a}$ and the average 
    speed $U_{a}$ (see figure \ref{figure_1}).

\section{ The Analyze methods}
\label{ the-analyze-methods}
\subsection{ Image Calibration}

As was shown in section \ref{image-acquisition-setup}, the camera recording a shadow projection of the welding process. The projection is
     supposed to be a section of the welding process image, orthogonal to the optical path. However, to correct small angle error in the alignment 
     of the camera, a control image (small chessboard image is use (see figure \ref{photo-calibration}). The real image size are taking from the know width of the welding wire.

\begin{figure}[h!]
\begin{center}    
\subfigure[Weld pool image in static GTAW process]{\label{photo-calibration-cuadro-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-patron.png}}
\subfigure[Canny filter treatment]{\label{photo-calibration-cuadro-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-origin.png}}\\
\subfigure[Snake treatment]{\label{photo-calibration-image-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
\end{center}
\caption{{\small Samples of different methods technique for image processing}}
\label{photo-explication}
\end{figure}

\subsection{ Image Treatment}
\label{ image_treatment}

The idea is to extract the macro drop and droplet shapes from the raw image and therefore to extract the geometrical information. The most common 
     approach is to segment the image \cite{WANG}. That means to separate in two fields (color) the image. The macro drop and droplet in one color and
      the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition (shadowgraphy) the images are already segmented between
       light and shadow zones (see figures \ref{photo-macro-drop-original}); where the shadows zones are the projection of the macro drop and droplet.

However objects within the arc may differ only by few intensity light level from the background. In these images areas a contrast enhancement is necessary. 
       Objects outside the arc, as the some regions of the macro drop profile, are clearly visible against the background. In these regions a contrast enhancement 
       can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}. Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.

To simplify the contrast enhancement, the images are converted from RGB image color to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
       reduce the grey level noise, a first smooth classical filter (Blur) is applied over the image. The filter replace the grey values of squares of $7\times 7$ 
       pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). In consequence, the homogeneity quality is improve into the light and 
       shadows regions, despite the edge contrast reduction induce between these regions.

Then, a regions adaptive threshold can be used to enhance the difference between shadow elements and light zones. To the adaptive threshold it is important 
       to choose the correct size region where it will be applied. Small regions to threshold will generate isolates patters (groups of pixels). Big regions will generate
        a classical like threshold image \cite{SABER}. The region size dominium choose to threshold application is $23\times 23\ pixels$. The threshold criteria choose 
        is binary: $greyL_{thres}(x,y) = max_value$ if $greyL_{origin}(x,y) >  threshold(x,y)$ or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
         to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter, $max_value$ is the grey level value choose to identify the pixels above
          threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
           $threshold(x,y)$ is obtain by subtraction between the average grey level of region pixels neighborhood and a constant parameter $C_{threshold}$.  
           Small edge defects can still be found, due to the previous smooth filter and some arc light interference regions, which are bigger than regions size to
            threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).

A second filter type median is necessary to improve the previous threshold treatment. This filter compute the grayness median value over $7\times 7\ pixels$
             region. The image, which is already binary type due to adaptive threshold processing, is enhancing in his mixed black white regions depending of 
             median value. In consequence contour quality between light and shadows regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).

Finally an impulse response filter to grey level gradient (Canny) is applied to extract the principal edges at image. In a binary image, all edges are principals,
              therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}). Nevertheless to guarantee a full detection of droplet and 
              macro drop profile, the canny parameters are adjusted to maximum, which means maximum edge detection sensibility.

\subsection{Edge extraction}
\label{edge_extraction}
Despite performance achieve by the image treatment, Canny filter generate many edges, or cords, in the image. These cord are composed by white pixels, 
              interpreted by the algorithms as an individuals points. In order to automate the edge extraction process, geometrical and graph algorithms are used 
              to isolate the cords corresponding to macro drop profile and edge section droplet.

To the macro drop profile a user interaction algorithm is responsible to extract the continuous cord (white pixels) corresponding to the profile into a list. Note 
              that the macro drop and the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}. The substrate shadow projection 
              is always the same if the optical path doesn’t change. Therefore the users have only to choose, to first image in the experience series, one extreme 
              of the cord corresponding to substrate profile (see figure \ref{photo-macro-drop-contour}). Then the algorithm finds all new white pixels inside a 
              small neighbor around the pixels selected by the user. Each new white pixel
               is added to the profile list. Starting at each new pixel, this process continues, automatically, until the other extreme of the cord, until the last image of the series.

To the droplet edge section, the white points cord defines the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer cord
                correspond to the droplet section. The idea is to build segments around the cords, and take the longest closer segment.

Give $S$ the set of points in the space image. The segments could be building between wherever two points of $S$. However, to fulfill the cords with 
                segments, only the points placed together could define a segment. To choose the correct points of $S$ a Delaunay triangulation is made 
                over $S$ \cite{CGAL} (see figure \ref{photo-droplet-triangulation-delaunay}). Each point of $S$ is a vertices of a triangle and then each potential 
                segment is a side of a triangle. The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means 
                minimal length sides to the triangles \cite{GEOMETRICAL*}. Give $\beta$ the cord surrounding the external hull of the Delaunay triangulation of $S$. 
                An alpha shape algorithm uses a $\alpha \in \mathbb{N}$ parameter, or square radius of a test circle, to travel from outside $\beta$ to inside 
                the triangulation. The circle has to go through the triangles sides without touch the vertices. Give $n$ the number of triangles sides of triangulation
                 and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ with
                 $i\in\{1,n}$, a segment is build between the respective vertices or points. At the end of the process, a segments set know as $\alpha$-shape has
                  been created.  Note if $\sqrt{alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL-library}. 
                  If $\sqrt{alpha} < l_{i} \forall i$ the circle go through every side in the triangulation, 
                 then no segment are created and $\alpha$-shape became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$ 
                 is sufficient to create a segment set around the droplet (see figure \ref{photo-droplet-alpha-shape}). A graph algorithm connects this segment and finds 
                 the longest closer segment. The longest closer segment corresponds to the metal transfer drop profile (see figure \ref{photo-droplet-contour}).

\subsection{Geometrical Analyze}
\label{geometrical_analize}

Now it is possible to determine the geometrical parameters shown at figure \ref{shema-macro-drop-droplet-parameters}. In order to this, it has been developed several
                  functions linked with the BAME and erCv libraries. For example, to wetting angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
                  are taken from the processed macro drop extracted profiles. A loop algorithm applies this method to all frames at the experience to compute the wetting 
                  angles. Same procedure is use to estimate the macro drop radius and volume \cite{CHAPUIS}.

\section{ Results}
\subsection{ Macro Drop analyzes}
\subsection{ Droplet analyzes}

\section{ Conclusions}

\section*{References}
\begin{thebibliography}{10}
\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{thebibliography}

\end{document}

### 2010-12-08 articles/MIG/doc_broullion/latex/paper-drop.tex

@@
 \section{Introduction}
-A better comprehension of welding objects behavior presents a PGMAW process as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
- and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}. An example to this are the problems linked to productivity. To some process, 
- increase productivity mean increase weld speed, however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
- speed \cite{CHAPUIS} and therefore the productivity. In a PGMAW process the weld quality is strongly relates with the metal transfer process stability 
- (the droplet deposition), then control of metal transfer process implies control of weld quality \cite{WANG}. In both example cases a macro drop kinetic
-  study and a droplet dynamic analysis could help to better understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
-  fluctuations \cite{WANG} or guarantee the welding quality. In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
-  geometrical analysis of macro drop and droplets in order to extract qualitative information of these welding objects.
+A better comprehension of welding objects behavior presents in a PGMAW process
+ as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
+ and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
+% An example to this are the problems linked to productivity. To some process,
+ For example, the
+ increase of productivity means often increase of weld speed,
+ however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
+ speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
+ In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
+ (the droplet deposition). The control of metal transfer process %implies control of
+ will improve weld quality \cite{WANG}. In both example cases a macro drop kinetic
+  study and a droplet dynamic analysis during static PGMAW process could help to better
+ understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
+  fluctuations \cite{WANG} that guarantee the welding quality. 
+ In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
+  geometrical analysis of macro drop and droplets in order to extract 
+  qualitative information of these welding objects. 
+  There have been many studies on visual sensing techniques for observing weld pool 
+  image \cite{BAE} and metal transfer process during welding \cite{LIN}. Optical sensors like high speed 
+ cameras and lighting systems have been widely use in GMAW process to realize 
+ image acquisition \cite{GUANGJUN},
+   control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
+   Image processing plays a critical role in 
+   extracting useful information from visual scenes \cite{WANG}.
+ Nevertheless the strong interference from the arc lightning required more than standard 
+   image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
+Previous work has shown that is possible to perform geometrical 
+   analysis in weld pools or droplets \cite{WU2}.
+   Parameters such as macro drop or droplets surface, volumes 
+or height has been measure using different and 
+   specifics processing images algorithms \cite{WANG}, \cite{WU2}, \cite{SEED},
+ \cite{NORDBRUCH}. However, to date, effectively automatic images processing
+    of metal transfer has not been developed, possibly due to the  difficulty involved 
+for welding researchers \cite{WANG}.
 
-There have been many studies on visual sensing techniques for observing weld pool image \cite{BAE} and metal transfer process during welding \cite{LIN}.
-Optical sensors like high speed CCD cameras and lighting systems have been widely use in GMAW process to realize image acquisition \cite{GUANGJUN},
-   control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}. Then image processing plays a critical role in 
-   extracting useful information from visual scenes \cite{WANG}. Nevertheless the strong interference from the arc lightning required more than standard 
-   image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. Previous work has shown that is possible to perform geometrical 
-   analysis in weld pools or droplets \cite{WU2}. Parameters such as macro drop or droplets surface, volumes or height has been measure using different and 
-   specifics processing images algorithms \cite{WANG}, \cite{WU2}, \cite{SEED}, \cite{NORDBRUCH}. However, to date, effectively automatic images processing
-    of metal transfer has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.
+To perform geometrical analysis in macro drope and droplet; a multipurpose C++ based library (erCv) was developed at the lab. These library results from selected functions  from highly reliable 
+open source libraries to images treatment, geometrical 
+    analysis, graph theory applications and image visualization.
+In a first step, and despite the different static and dynamic weld conditions, 
+as well as different current regime. A reliable 2D profiles and geometrical
+     parameters from macro drop and droplets, has been obtained using the mentioned library.
+ Using this, a dimension and dimensionless analysis will 
+     be done. The intention is to help to simplified futures numerical models of humping phenomena and quality process.
 
-To perform geometrical analysis in macro drop and droplet; a multipurpose C++ based library (erCv) was developed by the Weld/Assembly group of 
-    LMGC laboratory. These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical 
-    analysis, graph theory applications and image visualization.
-
-In a first step, and despite the different static and dynamic weld conditions, as well as different current regime. A reliable 2D profiles and geometrical
-     parameters from macro drop and droplets, has been obtained using the mentioned library. Using this, a dimension and dimensionless analysis has 
-     been performing. The intention is to help to simplified futures numerical models of humping phenomena and quality process.
+     The paper is organized as follows. First, the purpose of the library is explained, then 
+     the experimental setup to study macro drop analysis is detailed. The library and the algorithms
+     developed are explained and some results are shown on the macro drop and droplet study.
 
@@
 simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition
- and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}
-
-Then the shape and size kinetic analysis of macro drop and droplets could help to better understand 
- and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a 
- first step, a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
+ and the hump size. Same relations has been found between metal transfer
+ process and welding quality \cite{}. Then the shape and size kinetic 
+analysis of macro drop and droplets could help to better understand 
+ and enhance the PGMAW process. To monitor the shape and size of these welding 
+objects a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
   is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is 
-  one of the only way to access these quantities. Due to the arc light interference and the relatively high 
+  one of the only way to access these quantities. Due to the arc light 
+interference and the relatively high 
   speed of wire feed process, a high speed camera and an effective image processing algorithms are 
-  required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
-  per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others)
-   from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related 
-   with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies 
-   frames and electrical signals.
+  required \cite{WANG}. The typically frame rate acquisition to metal 
+transfer drop kinetic analysis is $3000$ 
+  per second \cite{WANG}. Therefore the algorithms have to be able 
+to extract the geometrical information (area, size and others)
+    from a huge amount of data. 
+In addition, the voltage and current signals are directly related 
+   with the droplet formation at the wire \cite{BALSAMO}. Good 
+synchronizations methods have to be applied between shadowgraphies 
+   frames and electrical signals \cite{chapuis}.
 
 \section{Image processing background} 
-Some definitions and brief description of generals principles used in image processing are required to better understand how is work the algorithms utilized by the erCv library.
+Some definitions and brief description of generals principles used in
+ image processing are required to better understand how is work the 
+algorithms utilized by the erCv library.
 
-\subsection{Some definitions}
-\label{some_definitions}
+\subsection{Some definitions}\label{some_definitions}
+A numerical grey image can be describe as 3D surface discretized by a grid mesh
+ in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
+ the grey level. 
+A strong relief change or high gradient greyness values at
+ the image are perceive by human eyes as light changes, and can be interpreted
+ as objects edges.
 
-A numerical grey image can be describe as 3D surface discretized by a grid mesh in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis, the grey level.
-
-A strong relief change or high gradient greyness values at the image are perceive by human eyes as light changes, and can be interpreted as objects edges. 
-Sometimes, a regular relief patrons or regular greyness variation can be distinguish. The human eyes can perceive these patrons as texture 
+Sometimes, a regular relief patrons or regular greyness
+ variation can be distinguish. The human eyes can perceive these patrons as texture 
 and interpret the space between different textures zones as edges.
@@
 
-\subsection{Filters}
-\label{filters}
-
+\subsection{Filters}\label{filters}
 The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
-$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
-Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
+$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
 widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the 

### 2010-12-11 articles/MIG/doc_broullion/latex/paper-drop.tex

@@
 \documentclass[12pt]{iopart}
+\usepackage{graphicx}
+\usepackage[sf]{subfigure}
 \newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
@@
 %\usepackage{iopams}
+
 \begin{document}
@@
 \ead{custserv@iop.org}
+
 \begin{abstract}
-This document describes the  preparation of an article using \LaTeXe\ and 
-\verb"iopart.cls" (the IOP \LaTeXe\ preprint class file).
-This class file is designed to help 
-authors produce preprints in a form suitable for submission to any of the
-journals published by IOP Publishing.
-Authors submitting to any IOP journal, i.e.\ 
-both single- and double-column ones, should follow the guidelines set out here. 
-On acceptance, their TeX code will be converted to 
-the appropriate format for the journal concerned.
 
@@
 \section{Introduction}
+
 A better comprehension of welding objects behavior presents in a PGMAW process
@@
 \section{Problems description}
+
 Bradstreet was the first researcher to experimentally study the bead hump formation \cite{CHO}. 
@@
 simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition
- and the hump size. Same relations has been found between metal transfer
- process and welding quality \cite{}. Then the shape and size kinetic 
-analysis of macro drop and droplets could help to better understand 
- and enhance the PGMAW process. To monitor the shape and size of these welding 
-objects a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
+ and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}
+
+Then the shape and size kinetic analysis of macro drop and droplets could help to better understand 
+ and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a 
+ first step, a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
   is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is 
-  one of the only way to access these quantities. Due to the arc light 
-interference and the relatively high 
+  one of the only way to access these quantities. Due to the arc light interference and the relatively high 
   speed of wire feed process, a high speed camera and an effective image processing algorithms are 
-  required \cite{WANG}. The typically frame rate acquisition to metal 
-transfer drop kinetic analysis is $3000$ 
-  per second \cite{WANG}. Therefore the algorithms have to be able 
-to extract the geometrical information (area, size and others)
-    from a huge amount of data. 
-In addition, the voltage and current signals are directly related 
-   with the droplet formation at the wire \cite{BALSAMO}. Good 
-synchronizations methods have to be applied between shadowgraphies 
-   frames and electrical signals \cite{chapuis}.
+  required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
+  per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others)
+   from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related 
+   with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies 
+   frames and electrical signals.
 
 \section{Image processing background}
+
 Some definitions and brief description of generals principles used in
@@
 \subsection{Filters}\label{filters}
+
 The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
-$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
+$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
+Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
 widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the 
@@
 \subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-explication-filters}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filters.png}}\\
+\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filter.png}}\\
 \subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
@@
 \end{figure}
-\end{itemize}
 
@@
 \begin{table}
-begin{center}
+\begin{center}
 \begin{tabular}{|cc|}
@@
 
+At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, the macro drop
+  center height $h_{m}$, the macro drop volume $V_{m}$, the penetration below the surface level $p$ and the wetting angles:
+   $\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real). With the indices $l$ and $r$ refer to left and
+    right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
+
 \begin{figure}
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
-\caption{{\small Profile schematics of welding objects in a GMAW process}
+\includegraphics[width=7cm,height=4cm]{schema-macro-drop-droplet-parameters.png}
+\caption{{\small Profile schematics of welding objects in a GMAW process}}
 \label{schema-macro-drop-droplet-parameters}
@@
 \end{figure}
-
-At figure \ref{figure_1} appears the geometrical elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, the macro drop
-  center height $h_{m}$, the macro drop volume $V_{m}$, the penetration below the surface level $p$ and the wetting angles:
-   $\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real). With the indices $l$ and $r$ refer to left and
-    right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
 
@@
     Finally in order to better understand the droplet dynamic \cite{}, the physical elements to identify are: the fall time $t_{a}$ and the average 
-    speed $U_{a}$ (see figure \ref{figure_1}).
+    speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).
 
@@
 As was shown in section \ref{image-acquisition-setup}, the camera recording a shadow projection of the welding process. The projection is
-     supposed to be a section of the welding process image, orthogonal to the optical path. However, to correct small angle error in the alignment 
-     of the camera, a control image (small chessboard image is use (see figure \ref{photo-calibration}). The real image size are taking from the know width of the welding wire.
-
-\begin{figure}[h!]
-\begin{center}    
-\subfigure[Weld pool image in static GTAW process]{\label{photo-calibration-cuadro-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-calibration-cuadro-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-origin.png}}\\
-\subfigure[Snake treatment]{\label{photo-calibration-image-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
-\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
-\end{center}
-\caption{{\small Samples of different methods technique for image processing}}
-\label{photo-explication}
-\end{figure}
+     supposed to be a section of the welding process image, orthogonal to the optical path. Therefore, to a first approach, not image projection 
+     correction is necessary. Only to calibrate the image dimension (at pixels) to the real objects dimension (at millimeters), a conversion scale is 
+     made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .
 
@@
 
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-original.png}}
+\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-grey.png}}\\
+\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothblur.png}}
+\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-adaptivethreshold.png}}\\
+\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothmedian.png}}
+\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-canny.png}}\\
+\end{center}
+\caption{{\small Image treatment step by step of PGMAW process}}
+\label{photo-macro-drop}
+\end{figure}
+
 \subsection{Edge extraction}
@@
               is always the same if the optical path doesn’t change. Therefore the users have only to choose, to first image in the experience series, one extreme 
-              of the cord corresponding to substrate profile (see figure \ref{photo-macro-drop-contour}). Then the algorithm finds all new white pixels inside a 
+              of the cord corresponding to substrate profile (see figures \ref{photo-results-macro-drop}). Then the algorithm finds all new white pixels inside a 
               small neighbor around the pixels selected by the user. Each new white pixel
                is added to the profile list. Starting at each new pixel, this process continues, automatically, until the other extreme of the cord, until the last image of the series.
+
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t1.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t2.png}}\\
+\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t3.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t4.png}}\\
+\end{center}
+\caption{{\small Images series of macro drop profiles}}
+\label{photo-results-macro-drop}
+\end{figure}
 
@@
                 segments, only the points placed together could define a segment. To choose the correct points of $S$ a Delaunay triangulation is made 
-                over $S$ \cite{CGAL} (see figure \ref{photo-droplet-triangulation-delaunay}). Each point of $S$ is a vertices of a triangle and then each potential 
+                over $S$ \cite{CGAL}. Each point of $S$ is a vertices of a triangle and then each potential 
                 segment is a side of a triangle. The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means 
-                minimal length sides to the triangles \cite{GEOMETRICAL*}. Give $\beta$ the cord surrounding the external hull of the Delaunay triangulation of $S$. 
-                An alpha shape algorithm uses a $\alpha \in \mathbb{N}$ parameter, or square radius of a test circle, to travel from outside $\beta$ to inside 
+                minimal length sides to the triangles \cite{GEOMETRICAL}. Give $\beta$ the cord surrounding the external hull of the Delaunay triangulation of $S$. 
+                An alpha shape algorithm uses a $\alpha \in N$ parameter, or square radius of a test circle, to travel from outside $\beta$ to inside 
                 the triangulation. The circle has to go through the triangles sides without touch the vertices. Give $n$ the number of triangles sides of triangulation
                  and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ with
-                 $i\in\{1,n}$, a segment is build between the respective vertices or points. At the end of the process, a segments set know as $\alpha$-shape has
-                  been created.  Note if $\sqrt{alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL-library}. 
-                  If $\sqrt{alpha} < l_{i} \forall i$ the circle go through every side in the triangulation, 
+                 $i \in\{1,n\}$, a segment is build between the respective vertices or points. At the end of the process, a segments set know as $\alpha$-shape has
+                  been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL-library}. 
+                  If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through every side in the triangulation, 
                  then no segment are created and $\alpha$-shape became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$ 
-                 is sufficient to create a segment set around the droplet (see figure \ref{photo-droplet-alpha-shape}). A graph algorithm connects this segment and finds 
-                 the longest closer segment. The longest closer segment corresponds to the metal transfer drop profile (see figure \ref{photo-droplet-contour}).
+                 is sufficient to create a segment set around the droplet (see figure \ref{photo-droplet-alpha-shape}).
+
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-canny.png}}
+\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-alpha-shape.png}}\\
+\end{center}
+\caption{{\small Images series of macro drop profiles}}
+\label{photo-results-droplet}
+\end{figure}
+
+A graph algorithm connects this segment and finds the longest closer segment. The longest closer segment corresponds to the metal transfer drop profile 
+(see figure \ref{photo-results-droplet}).
+
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[t = ]{\label{photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t1.png}}
+\subfigure[t = ]{\label{photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t2.png}}\\
+\subfigure[t = ]{\label{photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t3.png}}
+\subfigure[t = ]{\label{photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t4.png}}\\
+\end{center}
+\caption{{\small Images series of macro drop profiles}}
+\label{photo-results-droplet}
+\end{figure}
 
@@
 
-Now it is possible to determine the geometrical parameters shown at figure \ref{shema-macro-drop-droplet-parameters}. In order to this, it has been developed several
+Now it is possible to determine the geometrical parameters shown at figure \ref{schema-macro-drop-droplet-parameters}. In order to this, it has been developed several
                   functions linked with the BAME and erCv libraries. For example, to wetting angle measures, linear regressions or least squares (parabolic, ellipse, circle) 

### 2010-12-11 examples/macro_drop/macro_drop.cpp

@@ -72,14 +72,14 @@ int main( int hola, char** file_name)
   boost::tie( ea, loaded) = erLoadImage( name);
   if(!loaded) return 0;
   erSaveImage( &ea, name, exit);
-  ec = erConvertToBlackAndWhite( &ea); /* Conversion en 8 bit single channel */
-  erSaveImage2( &ec, name, exit, "con");
+  eb = erConvertToBlackAndWhite( &ea); /* Conversion en 8 bit single channel */
+  erSaveImage2( &eb, name, exit, "con");
   //erShowImage( "con", &ec);
   /* Conversion de l'image du RGB->GRIS */
   //ca.transform_image( bw);
 
   /* Definision de la zone d'interet ou on souhaite travvailler */
-  //ec = erDef_ROIuser( &eb, &rect, true);
+  ec = erDef_ROIuser( &eb, &rect, true);
 
 
   //erCvEqualizeHistUser( &ec, &pequ);
@@ -95,7 +95,7 @@ int main( int hola, char** file_name)
   /* Pour faire resortir les bordes principaux (par contraste) entres les zones zommbres et eclaires, */
   /* un methode de filtrage par seuil, adapte par zone, est utilise */
   erCvAdaptiveThresholdUser( &ec, &padt, true);
-  erSaveImage2( &ec, name, exit, "ada");
+  //erSaveImage2( &ec, name, exit, "ada");
   //erCvThresholdUser( &ec, &pthr, true);
 
   /* Le Sueillage par zones fait aussi resortir les bordes a l'interior des zones zombres */ 

### 2010-12-11 examples/macro_drop/macro_drop_python.cpp

@@ -20,46 +20,52 @@ int main( int hola, char** file_name)
 {
 
 //-------ATTENTION paramettres pour le CVAnalysis de yo no se quien-------------/ 
-//   CvRect rect;
-//   rect.x=121;rect.y=110;rect.width=814;rect.height=220;
-//   erCerc cerc(135,293,25);
+  CvRect rect;
+  rect.x=17;rect.y=143;rect.width=210;rect.height=93;
+  erCerc cerc(18,212,4);
+  erEqualP equ(0);
+  erSmootP p1(BLUR,5),p2(GAUSSIAN,5);
+  erCannyP cann(355,355);
+  erAdThrP adp(THRESH_BINARY,AM_MEAN,51,17,255); //** < 
+  erMacroDropAnalysis mda("ANmd");
+  mda.defineParameters(rect,cerc,p1,p2,cann,adp,equ);
+  mda.doIt("macro_goutte_1.png");
+  mda.doIt("macro_goutte_2.png");
+  mda.doIt("macro_goutte_3.png");
+  mda.doIt("macro_goutte_4.png");
+  mda.doIt("macro_goutte_5.png");
+  //  emt.doIt("imageExemple_6.bmp");
+  //   std::string img_base="../pictures/macro_drop/MCR_hongo_1.bmp";
+  //   for(int i = 1; i < 15;i++)
+  //     {
+  //       std::string filename = erLoadImageSeriesManipulationWeldPool( img_base, 1);
+  //       std::cout << "file name: " << filename << std::endl;
+  //       std::cout << "hola0" << std::endl;
+  //       mda.doIt(filename);
+  //       img_base = filename;
+  //     };
+  //   mda.saveParameters( "result/test.out");
+  
+  //-----------ATTENTION paramettres pour CvAnalysis de la macro-goutte-champignon--------/
+ //  CvRect rect;
+//   rect.x = 160; rect.y = 126; rect.width = 140; rect.height = 89;
+//   erCerc cerc(160,193,2);
 //   erEqualP equ(0);
 //   erSmootP p1(BLUR,7),p2(GAUSSIAN,5);
 //   erCannyP cann(355,355);
 //   erAdThrP adp(THRESH_BINARY,AM_MEAN,28,130,255); //** < 
 //   erMacroDropAnalysis mda("AN_macro_drop");
 //   mda.defineParameters(rect,cerc,p1,p2,cann,adp,equ);
-//   std::string img_base="../pictures/macro_drop/MCR_hongo_1.bmp";
[…]

### 2010-12-11 examples/metal_transfert/drop_python.cpp

@@ -20,7 +20,8 @@ Canny            : 355, 355
 int main( int hola, char** file_name)
 { 
   CvRect rect;
-  rect.x=100;rect.y=120;rect.width=70;rect.height=70;
+  //rect.x=100;rect.y=120;rect.width=70;rect.height=70;
+  rect.x=0;rect.y=0;rect.width=255;rect.height=255;
   erSmootP p1(BLUR,5),p2(GAUSSIAN,5);
   erCannyP cann(355,355);
   erAdThrP adp(THRESH_BINARY,AM_MEAN,53,19,255); //** <
@@ -28,10 +29,10 @@ int main( int hola, char** file_name)
   erMetalTransfertAnalysis emt("peo","peo");
   emt.defineParameters(rect,p1,p2,cann,adp,alp);
   emt.doIt("imageExemple_1.bmp");
-  //emt.doIt("imageExemple_2.bmp");
-  //emt.doIt("imageExemple_3.bmp");
-  //emt.doIt("imageExemple_4.bmp");
-  //emt.doIt("imageExemple_5.bmp");
-  //emt.doIt("imageExemple_6.bmp");
+  emt.doIt("imageExemple_2.bmp");
+  emt.doIt("imageExemple_3.bmp");
+  emt.doIt("imageExemple_4.bmp");
+  emt.doIt("imageExemple_5.bmp");
+  emt.doIt("imageExemple_6.bmp");
   return(0);
 }

### 2010-12-11 src/erCvAnalysis.cpp

@@ -171,6 +171,7 @@ bool erMacroDropAnalysis::doIt(std::string fich)
        std::list<CvPoint> cvPts;       
        boost::tie( ea, loaded) = erLoadImage( file_name);
        if( !loaded) return false;
+       erSaveImage( &ea, file_name, nom);
        eb = erConvertToBlackAndWhite( &ea);        
        ec = erDef_ROI( &eb, &rectOI); 
        erCvEqualizeHist( &ec, &param_equalizer_histogram);
@@ -178,7 +179,7 @@ bool erMacroDropAnalysis::doIt(std::string fich)
        erCvAdaptiveThreshold( &ec, &param_adaptive_threshold);
        erCvSmooth( &ec, &param_smooth2);
        erCvCanny( &ec, &param_canny);
-       erSaveImage( &ec, file_name, nom);
+       //erSaveImage( &ec, file_name, nom);
        IsEqualTo is_equal_255( 255); 
        erExtractCvPoints( cvPts, &ec, is_equal_255, rectOI);
        erExtractCurveMacroDrop( cvPts, &ec, rectOI, &cercToStart, file_name);
@@ -229,6 +230,7 @@ bool erMetalTransfertAnalysis::defineParametersUI( std::string firstImage)
   erSmootP psmo, psmo1;
   erCannyP pcan;
   erAdThrP padt;
+
   std::list< CvPoint> cvPts;
   std::list< CgalPoint> cgalPts;
   std::list< CgalSegmt> cgalSeg, bgraphSeg;
@@ -283,7 +285,7 @@ void erMetalTransfertAnalysis::setOutputGeometryFile(std::string file) //** Le f
 
 };
 
-bool  erMetalTransfertAnalysis::doIt( std::string fich)
+bool erMetalTransfertAnalysis::doIt( std::string fich)
 {
   bool loaded;
   char* file_name         = const_cast< char*>( fich.c_str());
@@ -293,18 +295,35 @@ bool  erMetalTransfertAnalysis::doIt( std::string fich)
   std::list< CvPoint>   cvPts;
   std::list< CgalPoint> cgalPts;
   std::list< CgalSegmt> cgalSeg, bgraphSeg;
+  //____________
+  erEqualP pequ;
+  //____________
 
   boost::tie(ea, loaded) = erLoadImage( file_name);
[…]

### 2010-12-30 articles/MIG/doc_broullion/latex/paper-drop.tex

@@
 \begin{document}
+\bibliographystyle{unsrt}
 
@@
  cameras and lighting systems have been widely use in GMAW process to realize 
- image acquisition \cite{GUANGJUN},
+ image acquisition \cite{ZHANG4},
    control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
@@
 Previous work has shown that is possible to perform geometrical 
-   analysis in weld pools or droplets \cite{WU2}.
+   analysis in weld pools or droplets \cite{WU1}.
    Parameters such as macro drop or droplets surface, volumes 
 or height has been measure using different and 
-   specifics processing images algorithms \cite{WANG}, \cite{WU2}, \cite{SEED},
+   specifics processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
  \cite{NORDBRUCH}. However, to date, effectively automatic images processing
@@
 
-\begin{equation}
-B = \bigcup_{i}R_{i} 
-\forall i  R_{i} \neq \emptyset
-\forall i, j avec i \neq j\ R_{i}\bigcap R_{j} = \emptyset
+\begin{eqnarray}
+B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
+\mbox{with} R_{i} \neq \emptyset \\
+\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
 \label{equation-segmentation}
-\end{equation}
+\end{eqnarray}
 
@@
 
-\section*{References}
-\begin{thebibliography}{10}
-\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
-(Reading, MA: Addison-Wesley)
-\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
-\end{thebibliography}
+\bibliography{paper_bain}
+
+%\section*{References}
+%\begin{thebibliography}{10}
+%\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
+%(Reading, MA: Addison-Wesley)
+%\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
+%\end{thebibliography}
 

### 2010-12-30 examples/melt_pool_TIG/fusion_bain_move_python.cpp

@@ -33,7 +33,7 @@ int main( int hola, char** file_name)
   //rec_tem.x = 14; rec_tem.y = 20; rec_tem.width = 5; rec_tem.height = 5;
   erTemplP templ(SQDIFF_NORMED, rec_tem, true); 
   erAlphaP alp(1);
-  erWeldPoolAnalysis wpa("full_bain_1");
+  erWeldPoolAnalysis wpa("bain_move");
 
   wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
   wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);

### 2010-12-30 include/erCv/geometry/erGeometricalCharacteristics.hpp

@@ -67,7 +67,7 @@ std::list<CgalPoint> erGeometryExtractConvexPolygon(InputSegmentIterator debut,I
 {
   CDT cdt ;
   std::list<CgalPoint> result;
-  for( InputSegmentIterator icg=debut;icg!=fin;icg++)
+  for( InputSegmentIterator icg = debut; icg != fin; icg++)
     {
       cdt.insert_constraint(icg->source(),icg->target());
     };

### 2010-12-30 src/erCvAnalysis.cpp

@@ -41,6 +41,7 @@
 
 #include <erCv/geometry/erGeometricalCharacteristics.hpp>
 #include <erCv/geometry/erCgalPolygon2.hpp>
+#include <erCv/geometry/erCgalConvexPolygone.hpp>
 #include <erCv/Gui/erCvUserInteraction.hpp>
 #include <erCv/Gui/erCvFiltersUser.hpp>
 #include <erCv/Gui/erCvSegmentationUser.hpp>
@@ -493,7 +494,7 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
   char* nom = const_cast< char*>( output_name.c_str());
   erImage ea, eb, ec, ed, ee;
   std::list< CvPoint>   cvPts;
-  std::list< CgalPoint> cgalPts;
+  std::list< CgalPoint> cgalPts, cgalPts2;
   std::list< CgalSegmt> cgalSeg, bgraphSeg;
   
   boost::tie(ea, loaded) = erLoadImage( file_name);
@@ -543,31 +544,36 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
 
   erPrintCgalPoint( bgraphSeg, file_name, nom);
 
-  double area;
-  if(output_convex_polygon)
-  {
-      std::list<CgalPoint> polygon = erGeometryExtractConvexPolygon(bgraphSeg.begin(),bgraphSeg.end());
+  convex_hull( bgraphSeg, cgalPts2);
 
-      std::string output_nam = (dir_analysis+"/"+name+"_wep_poly");
-      char* name = const_cast< char*>( output_nam.c_str());
-      erPrintCgalPoint(polygon,file_name,name);
-      Polygon_2 poly(polygon.begin(),polygon.end());
-      area = poly.area();
-    };
-  if(output_geometry_characteristics && bgraphSeg.size() > 6)
-    {
-      std::list<CgalTrian> triangs=erGeometryExtractTriangles(bgraphSeg.begin(),bgraphSeg.end());
-      if(!not output_convex_polygon)
-	{
-	 area   = getArea(triangs.begin(),triangs.end());
-	};
-      CgalLine  line;
-      CgalPoint pt;
-      CgalFTrai fit = linear_least_squares_fitting_2(triangs.begin(),triangs.end(),line,pt,CGAL::Dimension_tag<2>());	
-      std::ofstream ot(output_geometry_file.c_str(),std::ios_base::app);
-      CgalVect vect=line.to_vector();
[…]

### 2011-01-25 articles/MIG/paper-drop_v1.tex

--- 2010-12-30 articles/MIG/doc_broullion/latex/paper-drop.tex
@@
 
-\title[Macro drop and droplet profile detection during PGMAW process by image processing library]{Macro drop and droplet profile detection during PGMAW process by image processing library}
+\title[Macro drop and droplet profile detection during PGMAW process by image processing]{Macro drop and droplet profile detection during PGMAW process by image processing}
 
-\author{E Romero, C Bordreuil, J Chapuis, F Souliez, G Fras}
+\author{E Romero, J Chapuis ,C Bordreuil, F Souli\'e, G Fras}
 
-\address{IOP 
-Publishing, Dirac
-House, Temple Back, Bristol BS1 6BE, UK}
-\ead{custserv@iop.org}
+\address{Laboratoire de M\'ecanique et G\'enie Civil,
+CC048, Place Eug\`ene Bataillon, Universit\'e Montpellier 2,
+34095 Montpellier, France}
+\ead{cyril.bordreuil@univ-montp2.fr}
 
@@
 
-A better comprehension of welding objects behavior presents in a PGMAW process
- as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
- and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
-% An example to this are the problems linked to productivity. To some process,
- For example, the
- increase of productivity means often increase of weld speed,
- however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
- speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
+A better observation of behavior of the weld pool or the metal droplet in a PGMAW process
+ could help to  welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
  In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
- (the droplet deposition). The control of metal transfer process %implies control of
- will improve weld quality \cite{WANG}. In both example cases a macro drop kinetic
-  study and a droplet dynamic analysis during static PGMAW process could help to better
- understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
-  fluctuations \cite{WANG} that guarantee the welding quality. 
+ (the droplet deposition). The monitoring of metal transfer process
+ will indicate the good wire feed \cite{WANG}. 
+The macro drop kinetic monitoring during static PGMAW process could help to better
+understand some GMAW related phenomena  \cite{CHO} as free surface 
+fluctuations \cite{WANG}. 
 In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
 geometrical analysis of macro drop and droplets in order to extract 
-  qualitative information of these welding objects. 
+qualitative information.
+
+The monitoring of the shape and size of these welding objects uring
+static PGMAW  is 
+investigated with a 2D method. A shadowgraphy technique, or back lighting,
+is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}.
+ Due to the arc light interference and the relatively high 
+speed of wire feed process, a high speed camera and an effective image processing algorithms are 
+required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
+per second \cite{WANG}. Therefore the algorithms have to be able to extract 
+the geometrical information (area, size and others) from the macro drop and droplets,
+from a huge amount of data. In addition, the voltage and current signals are directly related 
+with the droplet formation at the wire \cite{BALSAMO}.
+
 There have been many studies on visual sensing techniques for observing weld pool 
-  image \cite{BAE} and metal transfer process during welding \cite{LIN}. Optical sensors like high speed 
- cameras and lighting systems have been widely use in GMAW process to realize 
- image acquisition \cite{ZHANG4},
+image \cite{BAE} and metal transfer process during welding \cite{LIN}.
+Optical sensors like high speed  cameras and lighting systems have been
+widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
 control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
-   Image processing plays a critical role in 
-   extracting useful information from visual scenes \cite{WANG}.
+Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
 Nevertheless the strong interference from the arc lightning required more than standard 
@@
 or height has been measure using different and 
-   specifics processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
+specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
 \cite{NORDBRUCH}. However, to date, effectively automatic images processing
@@
 
-To perform geometrical analysis in macro drope and droplet; a multipurpose C++ based library (erCv) was developed at the lab. These library results from selected functions  from highly reliable 
+To perform geometrical analysis in macro drope and droplet;
+ a multipurpose C++ based library (erCv) was developed at the lab. 
+These library results from selected functions  from highly reliable 
 open source libraries to images treatment, geometrical 
@@
 The paper is organized as follows. First, the purpose of the library is explained, then 
-     the experimental setup to study macro drop analysis is detailed. The library and the algorithms
+the experimental setup that will allow to appreciate the performance of the algorithm,
+ to study macro drop analysis is detailed. The library and the algorithms
 developed are explained and some results are shown on the macro drop and droplet study.
-
-\section{Problems description}
-
-Bradstreet was the first researcher to experimentally study the bead hump formation \cite{CHO}. 
-Humping was defined as the series of undulations of the weld bead. Further studies as computer 
-simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition
- and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}
-
-Then the shape and size kinetic analysis of macro drop and droplets could help to better understand 
- and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a 
- first step, a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting,
-  is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is 
-  one of the only way to access these quantities. Due to the arc light interference and the relatively high 
-  speed of wire feed process, a high speed camera and an effective image processing algorithms are 
-  required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
-  per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others)
-   from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related 
-   with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies 
-   frames and electrical signals.
-
-\section{Image processing background}
-
-Some definitions and brief description of generals principles used in
- image processing are required to better understand how is work the 
-algorithms utilized by the erCv library.
-
-\subsection{Some definitions}\label{some_definitions}
-A numerical grey image can be describe as 3D surface discretized by a grid mesh
- in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
- the grey level. 
-A strong relief change or high gradient greyness values at
- the image are perceive by human eyes as light changes, and can be interpreted
- as objects edges.
-
-Sometimes, a regular relief patrons or regular greyness
- variation can be distinguish. The human eyes can perceive these patrons as texture 
-and interpret the space between different textures zones as edges.
-There exist a large spectrum of algorithms to image treatment, in particular to edges detect. Most of them can be classified by the way that his operate above the image pixels and grey level.
-
-\subsection{Filters}\label{filters}
-
-The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
-$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
-Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
-widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the 
-image; this allows the filter a better edges localisation (see figure \ref{photo-explication-filter}). For this reason, Canny filter is widely 
-use at erCv library to detect the welding elements edges. However, it is sensible to noise or secondary greyness gradients in the image
- and, in consequence, it have some difficulties to define closer surface.
-
-\subsection{Snake and level set}
-\label{snake-and-level-set}
-
-Curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure 
-\ref{photo-explication-snake}). The central idea behind such an approach is to evolve a curve towards the lowest potential of a cost function. 
-However at each stage of curve evolution, each curve point potential has to be computed. A lot of point (better curve resolution) take a lot 
-computing time, and therefore are not yet apply to real time detection or relatively speed automatic image processing. For this reason snake algorithms are not used at erCv.
-
-\subsection{Segmentation}
-\label{segmentation}
-
-Let $B$ an image and let $R_{i}$ a region of $B$ such:
-
-\begin{eqnarray}
-B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
-\mbox{with} R_{i} \neq \emptyset \\
-\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
-\label{equation-segmentation}
-\end{eqnarray}
-
-A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. Each region is a connected set of pixels with 
-common properties (intensity, texture,...) \cite{COCQUEREZ}. The partition is generated by operations or comparisons methods between 
-regions. Generally, this treatment offers a good detection edges if the elements and surrounding area have different textures (see figure \ref{photo-explication-segmentation}). 
-Note that different regions can belong to the same partition and not be placed together, therefore the surface is not always connected and,
- in consequence, the edges of the interest regions are not always closed.
-
-\begin{figure}[h!]
-\begin{center}    
-\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filter.png}}\\
-\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
-\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
-\end{center}
-\caption{{\small Samples of different methods technique for image processing}}
-\label{photo-explication}
-\end{figure}
-
-\section{Image treatment library (erCv)}
-\label{image-treatment-library-ercv}
-
-As mentioned, a multipurpose image processing library was developed and currently use at the laboratory, in order to analyze welding process objects.
-erCv is able to perform edge detection and geometrical analysis in a different welding objects such: Macro drop, droplets and weld pool.
-erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable and portable library able to perform real time
- contour detection. erCv is build in Phyton scripts link to C++, making it relatively convivial to use.
-erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
-\begin{description}
-\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD 
- camera are not calibrated and present light inhomogeneities and noise. In order to obtain the real shape and size of weld elements, this module 
- include calibrations algorithms. To detect the welding objects contours it is necessary to improve the weld element image. This module has the 
- pre-processing treatments to noise reduction and image enhancement. Then to start the edges detection process, this module includes processing
-  algorithms as segmentations by samples comparators, watershed transformation, filters edge detectors and histogram based methods.  
-\item[Geometrical Treatment and Analysis:] This module has to end the edge detection process, completing and in some cases extrapolating the weld
-   elements edge. It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes. 
-   This module uses a full geometry algorithm library, which include different algorithms such as triangulations and mesh generation, alpha shape and 
-   convex hull generation and polygonal structures.
-\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the welding object edge from the image; this
-   required some criteria such as continuity, length or closer condition.  This module use graph algorithms to convert edges pixels points into connected 
-   segments, and therefore, identify and select the welding element edge using the criteria. This module is compose by connect segments, estimates
-    minimal cut, determine largest chain segments and others algorithms. 
-\item[Visualization:] This module is a set of functions use to execute, show and/or register the different steps at the image process.
-\end{description}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
-\caption{{\small Flow diagram of erCv library composition}}
-\label{schema-erCv}
-\end{center}
-\end{figure}
 
@@
 
-The objective is to perform geometrical analysis and measure characteristic times of the macro drop and the droplet in a PGMAW process. Notes that
- geometrical analysis refers to area section of droplets, height profile of macro drop and wetting contacts angles of the macro drop. And characteristics 
- time’s measures refer to time to height stagnation of macro drop and fall time of droplet between electrodes. The methods choose is the image treatment 
- of recorded image of PGMAW static process by a high speed CCD camera.
-
-To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; therefore an accurate, reliable and synchronizes 
- systems are requires due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).
-
-A platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}). The platform 
- was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go
-  per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-platform.png}
-\caption{{\small Experimental platform and specific device}}
-\label{schema-platform}
-\end{center}
-\end{figure}
-
-To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data 
-  and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).
+The objective is to perform geometrical analysis and measure characteristic
+times of the macro drop growth and the droplet during the free flight 
+during  a static PGMAW process. 
+A specific data acquisition setup was done at the lab in order to
+synchronize all kind of signals and images versus time and space \cite{ChapuisThesis}.
+The experimental setup is composed of a welding generator, a XY table, a data acquisition
+system and a high speed camera as shown on figure \ref{schema-montage-experimental-GMAW}.
+In this article only details on image acquisition setup and treatment will be outlined.
 
@@
 
-The PGMAW static process is recorded by Shadowgraphy optical method. A halogen lamp is use to light the weld process. To guarantee a homogeneous illumination 
-  of the welding process, a light diffuser is place in the optical path closer to the halogen lamp. Finally the shadows of welding elements are projected to the other side 
-  of the welding place. A Phantom V5.0 high speed camera is place and align at this side above the optical path (see figure \ref{schema-montage-experimental-GMAW}).
+The PGMAW static process is recorded by Shadowgraphy optical method. 
+An halogen lamp is use to light the weld process. To guarantee an homogeneous
+illumination of the welding process, a light diffuser is placed
+in the optical path closer to the halogen lamp. 
+Finally the shadows of welding elements are projected to the other side 
+of the welding place. A Phantom V5.0 high speed camera is placed and aligned 
+at the other of  the optical path (see figure \ref{schema-montage-experimental-GMAW}).
 
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-montage-experimental-GMAW.png}
+\includegraphics[width=7cm,height=4cm]{images/schema-montage-experimental-GMAW.png}
 \caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
@@
 
-To enhance the image contrast of the weld elements inside the electric discharge, the intensity rate between arc light and halogen lamp have to be reduce. In order to this
-   a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens, to attenuate the arc light. Nevertheless, the raw images remain highly noisy by the arc light.
+To enhance the image contrast of the weld elements inside the electric discharge,
+the intensity rate between arc light and halogen lamp have to be reduce. In order to this
+a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens. 650nm
+is around emitting wavelength for the gases. Nevertheless, the raw images remain highly 
+noisy by the arc light.
 
@@
 
-Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. The target is a steel disk of $10\ mm$ of thickness and ER70S steel 
-   welding wire.
-The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and percentage
-    of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon). Welding parameters values are summarize in tables \ref{table-parameters-static} to static and 
-    \ref{table-parameters-change} to variables parameters.
+Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. 
+The target is a steel disk of $10\ mm$ of thickness and 80mm radius.
+The fill wire is ER70S steel welding of 1mm diameter.
+The  wire feed speed is set to $6\ m/min$. The frequency droplets is set to $113\ Hz$. 
+Two kind of  shielding gas were used \ref{tab::gases}. 
+\begin{table}[h]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+Gaz & Argon (\%) & $CO_2$(\%) \\ \hline
+G1 & 100       & 0 \\ \hline
+G2 & 92        & 8 \\ \hline
+\end{tabular}
+\caption{Shielding gas composition}\label{tab::gases}
+\end{table}
+
+Some welding parameters values are summarized in tables \ref{table-parameters-static}.
+For the experiments described all along the paper there is no welding speed.
 
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{|cc|}
-\hline
-Welding wire type & ER70S \\ 
-Wire diameter ($mm$) or $drw$ & 1 \\  
-Contact tip to work distance ($mm$) & 20 \\
-Shielding gaz flowrate ($l/min$) & 18 \\ \hline
-\end{tabular}
-\caption{{\small Variable welding parameters used in experiments}}
-\label{table-parameters-change}
-\end{center}
-\end{table}
-
-Welding current and arc voltage are recorded at $30\ kHz$ sampling rate. The images are recorded at $4000$ frames per seconds, which is enough to
-     measure macro drop radius and apparent liquid-solid contact angle histories. The images and electrical signals are synchronize, thanks to the
-      automatically approach made in the multi physics platform.
+%Welding current and arc voltage are recorded at $30\ kHz$ sampling rate.
+The images are recorded at $4000$ frames per seconds, which is enough to
+measure macro drop radius and apparent liquid-solid contact angle histories. 
+%The images and electrical signals are synchronize, thanks to the
+%automatically approach made in the multi physics platform.
 
@@
 
-\section{ System definitions}
+\subsection{ System definitions}
 \label{system_definitions}
-\subsection{ Macro Drop}
+\subsubsection{ Macro Drop}
 \label{ macro_drop}
 
-The purpose is to study the evolution of weld pool object in a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
+The purpose is to study the evolution of weld pool object in
+a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
 of the macro drop according depositing droplets of feed wire.
 
-At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, the macro drop
-  center height $h_{m}$, the macro drop volume $V_{m}$, the penetration below the surface level $p$ and the wetting angles:
-   $\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real). With the indices $l$ and $r$ refer to left and
-    right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
+At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical 
+elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, 
+the macro drop center height $h_{m}$, the macro drop volume $V_{m}$, the
+penetration below the surface level $p$ and the wetting angles:
+$\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real).
+With the indices $l$ and $r$ refer to left and
+right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer
+to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
 
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-macro-drop-droplet-parameters.png}
+\includegraphics[width=7cm,height=4cm]{images/schema-macro-drop-droplet-parameters.png}
 \caption{{\small Profile schematics of welding objects in a GMAW process}}
@@
 
-\subsection{ Metal Transfer Drop}
+\subsubsection{ Metal Transfer Drop}
 \label{ metam_transfer_drop}
 
-To the droplet or metal transfer drop the geometrical parameters to identify are: The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
-    Finally in order to better understand the droplet dynamic \cite{}, the physical elements to identify are: the fall time $t_{a}$ and the average 
+To the droplet or metal transfer drop the geometrical parameters to identify are:
+The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
+Finally in order to better understand the droplet dynamic \cite{}, 
+the physical elements to identify are: the fall time $t_{a}$ and the average 
 speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).
 
-\section{ The Analyze methods}
-\label{ the-analyze-methods}
-\subsection{ Image Calibration}
+\section{Image processing}
 
-As was shown in section \ref{image-acquisition-setup}, the camera recording a shadow projection of the welding process. The projection is
-     supposed to be a section of the welding process image, orthogonal to the optical path. Therefore, to a first approach, not image projection 
-     correction is necessary. Only to calibrate the image dimension (at pixels) to the real objects dimension (at millimeters), a conversion scale is 
-     made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .
+Some definitions and brief description of generals principles used in
+ image processing are required to better understand  the 
+algorithms and the design of the library.
 
-\subsection{ Image Treatment}
-\label{ image_treatment}
+\subsection{Some definitions}\label{some_definitions}
+A numerical grey image can be describe as 3D surface discretized by a grid mesh
+ in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
+ the grey level. 
+A strong relief change or high gradient greyness values at
+ the image are perceive by human eyes as light changes, and can be interpreted
+ as objects edges.
 
-The idea is to extract the macro drop and droplet shapes from the raw image and therefore to extract the geometrical information. The most common 
-     approach is to segment the image \cite{WANG}. That means to separate in two fields (color) the image. The macro drop and droplet in one color and
-      the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition (shadowgraphy) the images are already segmented between
-       light and shadow zones (see figures \ref{photo-macro-drop-original}); where the shadows zones are the projection of the macro drop and droplet.
+Sometimes, a regular relief patrons or regular greyness
+ variation can be distinguish. The human eyes can perceive these patrons as texture 
+and interpret the space between different textures zones as edges.
+There exist a large spectrum of algorithms to image treatment, in particular to edges detect.
+ Most of them can be classified by the way that his operate above the image pixels and grey level.
 
-However objects within the arc may differ only by few intensity light level from the background. In these images areas a contrast enhancement is necessary. 
-       Objects outside the arc, as the some regions of the macro drop profile, are clearly visible against the background. In these regions a contrast enhancement 
-       can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}. Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.
+\subsection{Filters}\label{filters}
 
-To simplify the contrast enhancement, the images are converted from RGB image color to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
-       reduce the grey level noise, a first smooth classical filter (Blur) is applied over the image. The filter replace the grey values of squares of $7\times 7$ 
-       pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). In consequence, the homogeneity quality is improve into the light and 
-       shadows regions, despite the edge contrast reduction induce between these regions.
+The filters are algorithms that operate as mathematical functions $f$ above the 
+$X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
+$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
+Different kind of filters can be mentioned as median, Gaussian, impulse,
+ adaptive and others. The impulse filters such Canny are 
+widely use to edge detection \cite{COCQUEREZ}. These filter have an
+ impulse response to most important greyness gradient in the 
+image; this allows the filter a better edges localisation
+ (see figure \ref{photo-explication-filter}). 
+For this reason, Canny filter is widely 
+used in the library to detect the welding elements edges. 
+However, it is sensible to noise or secondary greyness gradients in the image
+ and, in consequence, it have some difficulties to define closer surface.
 
-Then, a regions adaptive threshold can be used to enhance the difference between shadow elements and light zones. To the adaptive threshold it is important 
-       to choose the correct size region where it will be applied. Small regions to threshold will generate isolates patters (groups of pixels). Big regions will generate
-        a classical like threshold image \cite{SABER}. The region size dominium choose to threshold application is $23\times 23\ pixels$. The threshold criteria choose 
-        is binary: $greyL_{thres}(x,y) = max_value$ if $greyL_{origin}(x,y) >  threshold(x,y)$ or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
-         to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter, $max_value$ is the grey level value choose to identify the pixels above
-          threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
-           $threshold(x,y)$ is obtain by subtraction between the average grey level of region pixels neighborhood and a constant parameter $C_{threshold}$.  
-           Small edge defects can still be found, due to the previous smooth filter and some arc light interference regions, which are bigger than regions size to
-            threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).
+\subsection{Snake and level set}
+\label{snake-and-level-set}
 
-A second filter type median is necessary to improve the previous threshold treatment. This filter compute the grayness median value over $7\times 7\ pixels$
-             region. The image, which is already binary type due to adaptive threshold processing, is enhancing in his mixed black white regions depending of 
-             median value. In consequence contour quality between light and shadows regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).
+Curve propagation is a popular technique in image analysis for object extraction,
+ object tracking, edge detection and others (see figure 
+\ref{photo-explication-snake}). The central idea behind such an approach
+ is to evolve a curve towards the lowest potential of a cost function. 
+However at each stage of curve evolution, each curve point potential has
+ to be computed. A lot of point (better curve resolution) take a lot 
+computing time, and therefore are not yet apply to real time detection
+ or relatively speed automatic image processing. For this reason snake algorithms are not used in the library.
 
-Finally an impulse response filter to grey level gradient (Canny) is applied to extract the principal edges at image. In a binary image, all edges are principals,
-    therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}). Nevertheless to guarantee a full detection of droplet and 
-         macro drop profile, the canny parameters are adjusted to maximum, which means maximum edge detection sensibility.
+\subsection{Segmentation}
+\label{segmentation}
+
+Let $B$ an image and let $R_{i}$ a region of $B$ such:
+
+\begin{eqnarray}
+B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
+\mbox{with} R_{i} \neq \emptyset \\
+\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
+\label{equation-segmentation}
+\end{eqnarray}
+
+A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. 
+Each region is a connected set of pixels with 
+common properties (intensity, texture,...) \cite{COCQUEREZ}.
+ The partition is generated by operations or comparisons methods between 
+regions. Generally, this treatment offers a good detection edges if
+ the elements and surrounding area have different textures (see figure
+ \ref{photo-explication-segmentation}). 
+Note that different regions can belong to the same partition and not
+ be placed together, therefore the surface is not always connected and,
+ in consequence, the edges of the interest regions are not always closed.
 
@@
 \begin{center}    
-\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-original.png}}
-\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-grey.png}}\\
-\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothblur.png}}
-\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-adaptivethreshold.png}}\\
-\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothmedian.png}}
-\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-canny.png}}\\
+\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-patron.png}}
+\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-filter.png}}\\
+\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-snake.png}}
+\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-segmentation.png}}
+\end{center}
+\caption{{\small Samples of different methods technique for image processing}}
+\label{photo-explication}
+\end{figure}
+
+\subsection{Image treatment library}
+\label{image-treatment-library-ercv}
+
+As mentioned, a multipurpose image processing library was developed 
+and currently use at the laboratory, in order to analyze welding process objects.
+erCv is able to perform edge detection and geometrical analysis in a different 
+welding objects such: Macro drop, droplets and weld pool.
+erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
+and portable library able to perform real time
+ contour detection. erCv is implemented in  C++ with some bindings in python,
+ making it relatively convivial to use.
+erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
+\begin{description}
+\item[Image Treatment:] Due to weld process conditions such arc lightening, 
+ heat and electrodes positions; the raw image registered by CCD 
+ camera are not calibrated and present light inhomogeneities and 
+ noise. In order to obtain the real shape and size of weld elements, this module 
+ include calibrations algorithms. To detect the welding objects contours it is 
+ necessary to improve the weld element image. This module has the 
+ pre-processing treatments to noise reduction and image enhancement.
+ Then to start the edges detection process, this module includes processing
+ algorithms as segmentations by samples comparators, watershed transformation,
+ filters edge detectors and histogram based methods.  
+\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
+   segments to end the edge detection
+  process, completing and in some cases extrapolating the weld
+  elements edge. It is also responsible to compute the geometrical 
+  data of welding elements such weld pool surface and metal transfer drop volumes. 
+  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
+  such as triangulations and mesh generation, alpha shape and 
+  convex hull generation and polygonal structures.
+\item[Graph Theories:] To compute the geometrical data of welding elements
+   it is necessary to extract the welding object edge from the image; this
+   required some criteria such as continuity, length or closer condition.
+   This module use graph algorithms to  identify and select the welding element edge using the
+   criteria. This module is composed by connected segments, estimates
+   minimal cut, determine largest chain segments and others algorithms. 
+\item[Visualization:] This module is a set of 
+  functions use to execute, show and/or register the 
+  different steps at the image process.
+\end{description}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=7cm,height=4cm]{images/schema-erCv.png}
+\caption{{\small Flow diagram of erCv library composition}}
+\label{schema-erCv}
+\end{center}
+\end{figure}
+
+\subsection{ The Analyze methods}
+\label{ the-analyze-methods}
+\subsubsection{ Image Calibration}
+
+As was shown in section \ref{image-acquisition-setup}, the camera recording a 
+shadow projection of the welding process. The projection is 
+supposed to be a section of the welding process image, orthogonal to the optical path.
+Therefore, to a first approach, not image projection 
+correction is necessary. Only to calibrate the image dimension 
+(at pixels) to the real objects dimension (at millimeters), a conversion scale is 
+made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .
+
+\subsubsection{ Image Treatment}
+\label{ image_treatment}
+
+The idea is to extract the macro drop and droplet shapes 
+from the raw images and therefore to extract the geometrical information.
+ The most common approach is to segment the image \cite{WANG}. 
+That means to separate in two fields (color) the image. The macro drop and droplet in one color and
+the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition
+ (shadowgraphy) the images are already segmented between
+light and shadow zones (see figures \ref{photo-macro-drop-original});
+ where the shadows zones are the projection of the macro drop and droplet.
+
+However objects within the arc may differ only by few intensity light level
+from the background. In these images areas a contrast enhancement is necessary. 
+Objects outside the arc, as the some regions of the macro drop profile,
+ are clearly visible against the background. In these regions a contrast enhancement 
+can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
+ Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.
+
+To simplify the contrast enhancement, the images are converted from RGB image color 
+to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
+reduce the grey level noise, a first smooth classical filter 
+(Blur) is applied over the image. The filter replace
+the grey values of squares of $7\times 7$ 
+pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
+In consequence, the homogeneity quality is improve into the light and 
+shadows regions, despite the edge contrast reduction induce between these regions.
+
+Then, a regions adaptive threshold can be used to enhance the difference
+between shadow elements and light zones. To the adaptive threshold it is important 
+to choose the correct size region where it will be applied. Small regions to threshold
+will generate isolates patters (groups of pixels). Big regions will generate
+a classical like threshold image \cite{SABER}. The region size dominium choose
+to threshold application is $23\times 23\ pixels$. The threshold criteria 
+choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
+or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
+to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
+ $max_value$ is the grey level value choose to identify the pixels above
+threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
+ before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
+$threshold(x,y)$ is obtain by subtraction between the average grey level of region
+ pixels neighborhood and a constant parameter $C_{threshold}$.  
+Small edge defects can still be found, due to the previous smooth filter and some arc 
+light interference regions, which are bigger than regions size to
+threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).
+
+A second filter type median is necessary to improve the previous threshold treatment. 
+This filter compute the grayness median value over $7\times 7\ pixels$
+region. The image, which is already binary type due to adaptive threshold processing,
+ is enhancing in his mixed black white regions depending of 
+ median value. In consequence contour quality between light and shadows
+ regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).
+
+Finally an impulse response filter to grey level gradient (Canny) is applied to extract 
+the principal edges at image. In a binary image, all edges are principals,
+therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
+Nevertheless to guarantee a full detection of droplet and 
+ macro drop profile, the canny parameters are adjusted to maximum, 
+which means maximum edge detection sensibility.
+
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
+\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-grey.png}}\\
+\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothblur.png}}
+\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-adaptivethreshold.png}}\\
+\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothmedian.png}}
+\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-canny.png}}\\
 \end{center}
@@
 
-\subsection{Edge extraction}
+\subsubsection{Edge extraction}
 \label{edge_extraction}
-Despite performance achieve by the image treatment, Canny filter generate many edges, or cords, in the image. These cord are composed by white pixels, 
-              interpreted by the algorithms as an individuals points. In order to automate the edge extraction process, geometrical and graph algorithms are used 
-              to isolate the cords corresponding to macro drop profile and edge section droplet.
+Despite performance achieve by the image treatment, Canny filter
+ generate many edges, or cords, in the image. These cord are composed
+ by white pixels, interpreted by the algorithms as an individuals points.
+ In order to automate the edge extraction process, geometrical and
+ graph algorithms are used  to isolate the cords corresponding to
+ macro drop profile and edge section droplet.
 
-To the macro drop profile a user interaction algorithm is responsible to extract the continuous cord (white pixels) corresponding to the profile into a list. Note 
-              that the macro drop and the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}. The substrate shadow projection 
-              is always the same if the optical path doesn’t change. Therefore the users have only to choose, to first image in the experience series, one extreme 
-              of the cord corresponding to substrate profile (see figures \ref{photo-results-macro-drop}). Then the algorithm finds all new white pixels inside a 
-              small neighbor around the pixels selected by the user. Each new white pixel
-               is added to the profile list. Starting at each new pixel, this process continues, automatically, until the other extreme of the cord, until the last image of the series.
+To the macro drop profile a user interaction algorithm is responsible
+ to extract the continuous cord (white pixels) corresponding
+ to the profile into a list. Note  that the macro drop and 
+the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}.
+ The substrate shadow projection is always the same if the optical
+ path doesn’t change. Therefore the users have only to choose, to
+ first image in the experience series, one extreme  of the cord 
+corresponding to substrate profile (see figures \ref{photo-results-macro-drop}).
+ Then the algorithm finds all new white pixels inside small neighbor around
+ the pixels selected by the user. Each new white pixel  is added to the
+ profile list. Starting at each new pixel, this process continues,
+ automatically, until the other extreme of the cord, until the last
+ image of the series.
 
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t1.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t2.png}}\\
-\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t3.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t4.png}}\\
+\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t1.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t2.png}}\\
+\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t3.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t4.png}}\\
 \end{center}
 \caption{{\small Images series of macro drop profiles}}
-\label{photo-results-macro-drop}
+\label{fig::photo-results-macro-drop}
 \end{figure}
 
-To the droplet edge section, the white points cord defines the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer cord
-                correspond to the droplet section. The idea is to build segments around the cords, and take the longest closer segment.
+To the droplet edge section, the white points cord defines 
+the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer
+ cord correspond to the droplet section. The idea is to build segments around
+ the cords, and take the longest closer segment.
 
-Give $S$ the set of points in the space image. The segments could be building between wherever two points of $S$. However, to fulfill the cords with 
-                segments, only the points placed together could define a segment. To choose the correct points of $S$ a Delaunay triangulation is made 
-                over $S$ \cite{CGAL}. Each point of $S$ is a vertices of a triangle and then each potential 
-                segment is a side of a triangle. The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means 
-                minimal length sides to the triangles \cite{GEOMETRICAL}. Give $\beta$ the cord surrounding the external hull of the Delaunay triangulation of $S$. 
-                An alpha shape algorithm uses a $\alpha \in N$ parameter, or square radius of a test circle, to travel from outside $\beta$ to inside 
-                the triangulation. The circle has to go through the triangles sides without touch the vertices. Give $n$ the number of triangles sides of triangulation
-                 and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ with
-                 $i \in\{1,n\}$, a segment is build between the respective vertices or points. At the end of the process, a segments set know as $\alpha$-shape has
-                  been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL-library}. 
-                  If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through every side in the triangulation, 
-                 then no segment are created and $\alpha$-shape became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$ 
-                 is sufficient to create a segment set around the droplet (see figure \ref{photo-droplet-alpha-shape}).
+Give $S$ the set of points in the space image. The segments could 
+be building between wherever two points of $S$. However, to fulfill
+ the cords with segments, only the points placed together could define
+ a segment. To choose the correct points of $S$ a Delaunay triangulation
+ is made over $S$ \cite{CGAL}. Each point of $S$ is a vertices 
+of a triangle and then each potential segment is a side of a triangle. 
+The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
+ Give $\beta$ the cord surrounding the external hull of the Delaunay
+ triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
+ or square radius of a test circle, to travel from outside $\beta$ to inside
+ the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
+$n$ the number of triangles sides of triangulation
+and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
+with $i \in\{1,n\}$, a segment is build between the respective vertices or
+ points. At the end of the process, a segments set know as $\alpha$-shape has been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
+ is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
+ every side in the triangulation,  then no segment are created and $\alpha$-shape
+ became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
+ is sufficient to create a segment set around the droplet
+ (see figure \ref{photo-droplet-alpha-shape}).
 
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t1.png}}
-\subfigure[t = ]{\label{photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t2.png}}\\
-\subfigure[t = ]{\label{photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t3.png}}
-\subfigure[t = ]{\label{photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-droplet-t4.png}}\\
+\subfigure[t = ]{\label{photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t1.png}}
+\subfigure[t = ]{\label{photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t2.png}}\\
+\subfigure[t = ]{\label{photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t3.png}}
+\subfigure[t = ]{\label{photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t4.png}}\\
 \end{center}
@@
 
-\subsection{Geometrical Analyze}
+\subsection{Geometrical Analysis}
 \label{geometrical_analize}
 
-Now it is possible to determine the geometrical parameters shown at figure \ref{schema-macro-drop-droplet-parameters}. In order to this, it has been developed several
-                  functions linked with the BAME and erCv libraries. For example, to wetting angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
-                  are taken from the processed macro drop extracted profiles. A loop algorithm applies this method to all frames at the experience to compute the wetting 
+Now it is possible to determine the geometrical parameters shown 
+at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
+angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
+are taken from the processed macro drop extracted profiles.
+A loop algorithm applies this method to all frames at the experience to compute the wetting 
 angles. Same procedure is use to estimate the macro drop radius and volume \cite{CHAPUIS}.
@@
 \section{ Results}
-\subsection{ Macro Drop analyzes}
-\subsection{ Droplet analyzes}
+In this part some results, performance and reliability of the library for a set of experiment
+are shown. The basic experiment is a static Pulsed Gas Tungsten Arc Welding.
+A macrodrop is feed by droplets that are assumed to flight vertically and
+then  feed the macro drop generated. The macrodrop grows with a geometry that depends on the effects of gravity,
+surface tension, heat transfert,...
+
+To improve weld quality in pulsed GMAW, the dynamic of the droplet is investigated.
+The analysis focus on the regularity of the transfert and some statistics are shown.
+
+The algoritms are tested on a i7 processor from Intel with 1.87Ghz.
+
+\subsection{ Macro Drop growth investigation}
+The investigation of the macro drop growth for the two shielding gas needs the study of two quantities:
+
+\begin{itemize}
+\item The angle between the substrate and the liquid
+\item The speed of growth of the macro drop radius
+\end{itemize}
+
+The first item give information on the capillarity mechanism involved in the macrodrop and
+the second is an indicator of the ease of growth of the macrodrop due to
+heat transfert and tension surface.
+
+The shielding gas has a great effect between the liquid and the gas interface. Gas could diffuse in the
+first layer of the liquid and greatly modify the physical properties. The tension surface is the main physical
+property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
+its equilibrium. It has to be kept in mind that modification of shielding composition will also modify
+the plasma energetical and momentum distribution that could also  influence the shape of the interface.
+
+ To study the influence of the gases on the shape of the gas liquid interface, images must be selected in cold
+regime of the plasma in the period. It is better to select images at the end of the period when the macrodrop is
+stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
+The treatment of each image last around 5ms.
+\subsubsection{Basis and angle evolution} 
+Some profile detection are shown on figure \ref{fig::photo-results-macro-drop} on the macrodrop.
+The shape is shown on figure \ref{fig::photo-results-macro-drop}.
+
+Angle and Radius could be measured with the contour. The workpiece surface is detected on the contour so 
+that the macrodrop could be isolated. The developped algorithm manage to detect profile under the arc.
+The algorithm to extract the macrodrop profile is  a thershold relative to the base material or workpiece.
+The result is shown on figure \ref{fig:profile_extract}. Then, calculation of evolution on the profile can pe performed
+all along  the process.
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=10cm]{images/CO2_2s.png}
+\caption{Profile of macro drop for G1 gas after 2s of welding}
+\label{fig::profile_extract}
+\end{figure}
+First, the evolution of the basis is extracted on figure \ref{fig::basis} by finding 
+the min of the max of the contour on figure \ref{fig::profile_extract}.
+
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/Evolution_Base_Gazs.pdf}
+\caption{Macrodrop growth (basis) in function of welding time}
+\label{fig::macro_drop}
+\end{figure}
+
+The figure \ref{fig::basis} shows the growth of the macrodrop with the two different gas.
+The evolution is almost the same in value. The 8 per cent CO2 gaz seems to be a little bit 
+more noisy than the pure Argon one.
+
+Another important geometrical entity is angle. To approximate it, a simple linear regression is
+performed for the first and last points of the profile. The result are shown on figure \ref{fig::angles}
+for the left angle and the two gases.
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/Evolution_Angle_Gazs.pdf}
+\caption{Macrodrop left Angle in function of welding time}
+\label{fig::angles}
+\end{figure}
+
+The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
+Macrodrop oscillations induced left wetting angle oscillations. Depending of the main oscillations during
+a period, the local angle oscillation is more or less important. For pure Argon
+gas, the equilibrium angle (60 degrees) rapidly reached and stays constant all along the welding.
+For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.
+
+\subsubsection{Discussion}
+The noise in the measure for the basis could be attributed
+to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.
+The interface between the gas and liquid is extremely strained. During a pulse, the surface is perturbated by the
+increase of pressure in the arc due to increase of current and by the impingement of the droplet inside the
+weld pool. These phenomenon near the triple joint are transient. The growth of the macrodrop is a balance mainly between
+the energy balance, the mechanical equilibrium (DuprÈ's law and membrane equilibrium). 
+The energy balance is coupled to fluid flow in the weld pool. 
+The shape of the macrodrop is an important information for
+the mechanical equilibrium of the interface and to have information of mechanical acting on it.
+For example, the macrodrop made with  pure Argon grows by step denoting an interesting instability 
+of the interface.
+
+The modification of gas influences surface tension but also modifies the energy transfert from the plasma
+to the workpiece. Even with same welding parameters, 
+the difference of gas will modify the current lines distribution but also the arc length.
+Nevertheless, the evolution of the basis for the two gases are almost the same (figure \ref{fig::macrodrop}) as well
+almost the same overall shape (figure \ref{fig::comp_gazs}). This means that at first order the two evolution
+are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
+
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/Comparaison_gazs_2s.pdf}
+\caption{Macrodrop shape at 2s for the two gases}
+\label{fig::comp_angles}
+\end{figure}
+
+This investigation demonstrates the interest of these kind of analysis for understanding of the phenomenon
+involved in welding. It is also precise information for validation or comparison with numerical
+computation.
+
+\subsection{ Droplet flight}
+Droplet flight investigation is of interest for weld quality and the metal deposition process.
+The determination of the motion and the impact point is then a good indicator of the quality of the
+process. The droplet flight is only investigated for the 8 per cent $CO_2$ for a pulse of 113 Hertz.
+The treatment of each image takes between 5 to 45ms with geometrical algorithm (triangulation) and output
+(surface computation and position of the center of mass).
+
+\subsubsection{Trajectories and droplet velocities}
+During one pulse, the droplet are detected. The shape are shown on figure \ref{fig::droplets}.
+
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/FreeFlight.pdf}
+\caption{One droplet at two different times during the free flight}
+\label{fig::droplets}
+\end{figure}
+
+The shape of the droplet changes during the free flight denoting oscillations of the droplet.
+Once the points of the contour of the droplet, the center of mass could be found as well as the principal axis.
+The center of mass is drawn during several pulses on figure \ref{fig::center_mass}.
+
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/Trajectory.pdf}
+\caption{Locations of the center of mass of the droplet for four different pulses}
+\label{fig::center_mass}
+\end{figure}
+The motions of the center of mass are almost linear and repetitive for the different times.
+The trajectories show that the motion is aligned more or less with the vertical axis.
+The position relative to the vertical axis can then be drawn for the four free 
+flight of droplets (figure \ref{fig::velocities}).
+
+\begin{figure}[h!]
+\centering    
+\includegraphics[width=7cm,angle=90]{images/Velocities.pdf}
+\caption{Locations of the center of mass of the droplet for four different pulses}
+\label{fig::velocities}
+\end{figure}
+
+The position of the center of mass of the droplet relative to the vertical axis shows that the 
+droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse.
+
+\subsubsection{Discussions}
+The oscillations of the droplet gives informations on the competition between surface tension and gravity.
+For the welding conditions of the experiment, the trajectories of the different pulse indicates 
+that the forces acting on the droplet are in equilibrium
+or are negligible in respect to the size of the droplet.
+% Ajouter qq chose
+Despite the two dimensional analysis, the result gives important informations for 
+simulation of metal transfert process.
+
+Even if the four trajectories are similar, some discrepancies could be outlined. The short time 
+for the analysis let nice perspectives for the algorithm for the monitoring of the transfert.
 
@@
 %\end{thebibliography}
-
+\bibitem{CGAL} http://www.cgal.org 
 \end{document}

### 2011-01-25 articles/MIG/source/viewImages.py

@@ -1,0 +1,14 @@
+from analysis.analysis        import *
+from GUI.imagesAndCurveViewer import *
+
+ms=bameTests(['MCR_19042010_4','MCR_02042010_9','MCR_31052010_4'])
+bameConfigureExtraction(ms, config=({'name':'intensity','type':'intensity','file':'current.dat','K':-63,'inc':1},
+                                    {'name':'tension','type':'tension','file':'arcvoltage.dat','K':11.,'inc':2},
+                                        {'type':'cameras'}))
+#bamePlotValues(ms,'intensity',offset=False)
+#bamePlotValues(ms,'tension',offset=False,figure_number=2)
+#pylab.show()
+app   = QApplication([])
+frame = FrameForImageAndCurve(manip=ms[2],valeur='intensity')
+frame.show()
+app.exec_()

### 2011-01-26 articles/MIG/paper-drop_v1.tex
cb:maj Article MIG

@@
 
-A better observation of behavior of the weld pool or the metal droplet in a PGMAW process
- could help to  welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
- In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
- (the droplet deposition). The monitoring of metal transfer process
- will indicate the good wire feed \cite{WANG}. 
-The macro drop kinetic monitoring during static PGMAW process could help to better
-understand some GMAW related phenomena  \cite{CHO} as free surface 
-fluctuations \cite{WANG}. 
-In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
-geometrical analysis of macro drop and droplets in order to extract 
-qualitative information.
+A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arx Welding (PGMAW)
+ process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
+ In a PGMAW process, the weld quality is strongly related with the metal transfer  stability 
+ (droplet deposition). The monitoring of metal transfer process
+ will indicate the good deposition process \cite{WANG}. 
+The macro drop kinetic measurement during static PGMAW process could improve the
+understanding of some GMAW related phenomenon  \cite{CHO} as free surface 
+fluctuations \cite{WANG}. The measurement of the geometry of the free surface 
+of macrodrop or droplets is an important information for the understanding and
+the validation of the simulation.
 
@@
 Parameters such as macro drop or droplets surface, volumes 
-or height has been measure using different and 
+or height has been measured using different and 
 specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
-\cite{NORDBRUCH}. However, to date, effectively automatic images processing
+\cite{NORDBRUCH}. However, to date, effective automatic image processing
 of metal transfer has not been developed, possibly due to the  difficulty involved 
@@
 
-To perform geometrical analysis in macro drope and droplet;
- a multipurpose C++ based library (erCv) was developed at the lab. 
+To perform geometrical analysis in macrodrop and droplet,
+ a multipurpose C++  library (erCv) was developed at the lab. 
 These library results from selected functions  from highly reliable 
@@
  Using this, a dimension and dimensionless analysis will 
-be done. The intention is to help to simplified futures numerical models of humping phenomena and quality process.
+be done. The intention is to help to simplify future numerical models and enhance monitoring by direct observation.
 
-The paper is organized as follows. First, the purpose of the library is explained, then 
-the experimental setup that will allow to appreciate the performance of the algorithm,
- to study macro drop analysis is detailed. The library and the algorithms
-developed are explained and some results are shown on the macro drop and droplet study.
+The paper is organized as follows. First, the experimental setup that will allow to appreciate the performance of the algorithm,
+ to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
+during welding process. Then 
+ The library and the algorithms are explained and some results are shown on the macro drop and droplet study.
 
@@
 The PGMAW static process is recorded by Shadowgraphy optical method. 
-An halogen lamp is use to light the weld process. To guarantee an homogeneous
+An halogen lamp is used to light the weld process. To guarantee an homogeneous
 illumination of the welding process, a light diffuser is placed
 in the optical path closer to the halogen lamp. 
-Finally the shadows of welding elements are projected to the other side 
-of the welding place. A Phantom V5.0 high speed camera is placed and aligned 
-at the other of  the optical path (see figure \ref{schema-montage-experimental-GMAW}).
+Finally the shadows of welding elements are projected to the other side where
+ a Phantom V5.0 high speed camera is placed and aligned in
+ the optical path (see figure \ref{schema-montage-experimental-GMAW}).
 
@@
 To enhance the image contrast of the weld elements inside the electric discharge,
-the intensity rate between arc light and halogen lamp have to be reduce. In order to this
-a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens. 650nm
-is around emitting wavelength for the gases. Nevertheless, the raw images remain highly 
+the intensity rate between arc light and halogen lamp have to be reduced. In order to this
+a $650\ \pm 10\ nm$ band pass filter is placed in front the camera lens. 650nm
+is around a no emitting wavelength from the arc. Nevertheless, the raw images remain highly 
 noisy by the arc light.
@@
 The  wire feed speed is set to $6\ m/min$. The frequency droplets is set to $113\ Hz$. 
-Two kind of  shielding gas were used \ref{tab::gases}. 
+Two kind of  shielding gases were used \ref{tab::gases}. 
 \begin{table}[h]
@@
 
-Measurements are made using the erCv library.
+%Measurements are made using the erCv library.
 
@@
 
-The purpose is to study the evolution of weld pool object in
-a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
-of the macro drop according depositing droplets of feed wire.
+%The purpose is to study the evolution of weld pool object in
+%a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
+%of the macro drop according depositing droplets of feed wire.
 
@@
 to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
+The angles and the base are the two main quantities to be measured. but the overall shape of
+the macrodrop is an important information for computation.
 
@@
 
-Some definitions and brief description of generals principles used in
- image processing are required to better understand  the 
-algorithms and the design of the library.
-
-\subsection{Some definitions}\label{some_definitions}
+Some definitions and brief description of general principles used in
+ image processing are required to measure the profiles. Then, the design of the library is briefly detailed
+to succeed to detect the profile in the noisy environment.
+\subsection{Image treatment basics}
+\subsubsection{Some definitions}\label{some_definitions}
 A numerical grey image can be describe as 3D surface discretized by a grid mesh
@@
 
-\subsection{Filters}\label{filters}
+\subsubsection{Filters}\label{filters}
 
@@
 
-\subsection{Snake and level set}
+\subsubsection{Snake and level set}
 \label{snake-and-level-set}
@@
 
-\subsection{Segmentation}
+\subsubsection{Segmentation}
 \label{segmentation}
@@
  contour detection. erCv is implemented in  C++ with some bindings in python,
- making it relatively convivial to use.
-erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
+ making it relatively convivial to use for non-programmers.
+erCv is composed by four processing modules: 
 \begin{description}
@@
  noise. In order to obtain the real shape and size of weld elements, this module 
- include calibrations algorithms. To detect the welding objects contours it is 
+ includes calibration algorithms. To detect the welding objects contours it is 
  necessary to improve the weld element image. This module has the 
@@
 \item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
-   segments to end the edge detection
+   segments to conclude the edge detection
   process, completing and in some cases extrapolating the weld
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{images/schema-erCv.png}
+\includegraphics[width=10cm]{images/schema-erCv.png}
 \caption{{\small Flow diagram of erCv library composition}}
@@
 \end{figure}
+
+The originality of the library comes from the agregation and complementarity of the different numerical tools.
+The main difficulty is to find algorithms with good parameters all along the process.
 
@@
 (at pixels) to the real objects dimension (at millimeters), a conversion scale is 
-made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .
+made. In our experiment, the known width of the welding wire leads to $conv = 1\ mm/ 20\ pixels$ .
 
@@
 
-However objects within the arc may differ only by few intensity light level
+However objects within the image under the arc may differ only by few intensity light level
 from the background. In these images areas a contrast enhancement is necessary. 
@@
 pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
-In consequence, the homogeneity quality is improve into the light and 
+In consequence, the homogeneity quality is improved into the light and 
 shadows regions, despite the edge contrast reduction induce between these regions.
@@
 to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
- $max_value$ is the grey level value choose to identify the pixels above
+ $max(value)$ is the grey level value choose to identify the pixels above
 threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
@@
 Give $S$ the set of points in the space image. The segments could 
-be building between wherever two points of $S$. However, to fulfill
+be built between wherever two points of $S$. However, to fulfill
  the cords with segments, only the points placed together could define
  a segment. To choose the correct points of $S$ a Delaunay triangulation
- is made over $S$ \cite{CGAL}. Each point of $S$ is a vertices 
+ is made over $S$ \cite{CGAL}. Each point of $S$ is a vertice 
 of a triangle and then each potential segment is a side of a triangle. 
-The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
+The Delaunay triangulations guarantee a unique solution with minimal
+ internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
  Give $\beta$ the cord surrounding the external hull of the Delaunay
@@
 with $i \in\{1,n\}$, a segment is build between the respective vertices or
- points. At the end of the process, a segments set know as $\alpha$-shape has been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
+ points. At the end of the process, a  set of segments knows as $\alpha$-shape has been created.
+  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
  is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
- every side in the triangulation,  then no segment are created and $\alpha$-shape
+ every side in the triangulation,  then no segment is created and $\alpha$-shape
  became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-canny.png}}
-\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-alpha-shape.png}}\\
+\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-canny.png}}
+\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-alpha-shape.png}}\\
 \end{center}
@@
 A loop algorithm applies this method to all frames at the experience to compute the wetting 
-angles. Same procedure is use to estimate the macro drop radius and volume \cite{CHAPUIS}.
+angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.
+
+The metal transfert droplet is approximate and close with a combination of $\alpha$-shape and
+graph algorithm. Once the set of segments are extracted a triangulation is created. The triangles 
+are then used to compute the surface and the position of the centroid. It is assumed that there is a kind
+of axisymmetry  and an homogeneous density in the droplet. With the triangles, the principal axis could also be 
+computed.
 
@@
 In this part some results, performance and reliability of the library for a set of experiment
-are shown. The basic experiment is a static Pulsed Gas Tungsten Arc Welding.
+are shown. The basic experiment is a static PGMAW.
 A macrodrop is feed by droplets that are assumed to flight vertically and
-then  feed the macro drop generated. The macrodrop grows with a geometry that depends on the effects of gravity,
+then feed the macrodrop. The macrodrop grows with a geometry that depends on the effects of gravity,
 surface tension, heat transfert,...
 
-To improve weld quality in pulsed GMAW, the dynamic of the droplet is investigated.
-The analysis focus on the regularity of the transfert and some statistics are shown.
+To improve weld pool stability in pulsed GMAW, the growth of the droplet is investigated.
+To improve weld quality, the transfert during some pulses are analyzed.
 
@@
 \begin{itemize}
+\item The speed of growth of the macro drop radius
 \item The angle between the substrate and the liquid
-\item The speed of growth of the macro drop radius
 \end{itemize}
 
-The first item give information on the capillarity mechanism involved in the macrodrop and
-the second is an indicator of the ease of growth of the macrodrop due to
-heat transfert and tension surface.
+The first is an indicator of the ease of growth of the macrodrop due to
+heat transfert and tension surface and the second  item gives information
+ on the capillarity mechanism involved in the macrodrop
 
@@
 property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
-its equilibrium. It has to be kept in mind that modification of shielding composition will also modify
-the plasma energetical and momentum distribution that could also  influence the shape of the interface.
+its equilibrium.
+% It has to be kept in mind that modification of shielding composition will also modify
+% the plasma energetical and momentum distribution that could also  influence the shape of the interface.
 
  To study the influence of the gases on the shape of the gas liquid interface, images must be selected in cold
-regime of the plasma in the period. It is better to select images at the end of the period when the macrodrop is
+regime of the plasma in the pulse. It is better to select images at the end of the period when the macrodrop is
 stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
-The treatment of each image last around 5ms.
+The treatment of each image lasts around 5ms.
 \subsubsection{Basis and angle evolution} 
@@
 
-Angle and Radius could be measured with the contour. The workpiece surface is detected on the contour so 
-that the macrodrop could be isolated. The developped algorithm manage to detect profile under the arc.
-The algorithm to extract the macrodrop profile is  a thershold relative to the base material or workpiece.
-The result is shown on figure \ref{fig:profile_extract}. Then, calculation of evolution on the profile can pe performed
+ The developped algorithm manage to detect profile under the arc.
+ To isolate only 
+macrodrop profile, a thershold relative to the base material is used to extract the macrodrop profile.
+The result is shown on figure \ref{fig:profile_extract}. Then, basis and angle of the profile can be computed
 all along  the process.
@@
 
-Another important geometrical entity is angle. To approximate it, a simple linear regression is
+Another important geometrical entity is the angle of the macrodrop surface on the substrate.
+ To approximate it, a simple linear regression is
 performed for the first and last points of the profile. The result are shown on figure \ref{fig::angles}
@@
 The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
-Macrodrop oscillations induced left wetting angle oscillations. Depending of the main oscillations during
+Macrodrop oscillations induced  wetting angle oscillations. Depending of the main oscillations during
 a period, the local angle oscillation is more or less important. For pure Argon
@@
 to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.
+
 The interface between the gas and liquid is extremely strained. During a pulse, the surface is perturbated by the
 increase of pressure in the arc due to increase of current and by the impingement of the droplet inside the
-weld pool. These phenomenon near the triple joint are transient. The growth of the macrodrop is a balance mainly between
-the energy balance, the mechanical equilibrium (DuprÈ's law and membrane equilibrium). 
-The energy balance is coupled to fluid flow in the weld pool. 
+weld pool. These perturbations create oscillations of the macrodrop and on the free surface.
+ These phenomenon induce also oscillations near the triple joint.
+
+ The growth of the macrodrop is a balance mainly between
+the energy balance (thermo convection) and the mechanical equilibrium (Dupr\'e's law and membrane equilibrium). 
 The shape of the macrodrop is an important information for
-the mechanical equilibrium of the interface and to have information of mechanical acting on it.
+the local and global equilibrium of the interface. 
 For example, the macrodrop made with  pure Argon grows by step denoting an interesting instability 
@@
 the difference of gas will modify the current lines distribution but also the arc length.
-Nevertheless, the evolution of the basis for the two gases are almost the same (figure \ref{fig::macrodrop}) as well
-almost the same overall shape (figure \ref{fig::comp_gazs}). This means that at first order the two evolution
+Nevertheless, the evolution of the basis and the  shape 
+(figure \ref{fig::comp_gazs}) for the two gases are almost the same (figure \ref{fig::macrodrop}).
+ This means that at first order the two evolutions
 are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
+Pure Argon shielding lead to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
+at the triple joint (liquid-gas-substrate) is higher modifying then the behaviour of the overall interface.
 
@@
 The treatment of each image takes between 5 to 45ms with geometrical algorithm (triangulation) and output
-(surface computation and position of the center of mass).
+(surface computation and position of the center of mass), within the python interpreter.
 
@@
 The shape of the droplet changes during the free flight denoting oscillations of the droplet.
-Once the points of the contour of the droplet, the center of mass could be found as well as the principal axis.
+Once the points of the contour of the droplet are detected, the center of mass are extracted  as well as the principal axis.
 The center of mass is drawn during several pulses on figure \ref{fig::center_mass}.
@@
 \end{figure}
-The motions of the center of mass are almost linear and repetitive for the different times.
+The motions of the center of mass are almost linear and repetitive for the different transferts.
 The trajectories show that the motion is aligned more or less with the vertical axis.
@@
 The position of the center of mass of the droplet relative to the vertical axis shows that the 
-droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse.
+droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse
+and the free flight of the droplet last 6ms.
 
 \subsubsection{Discussions}
-The oscillations of the droplet gives informations on the competition between surface tension and gravity.
+The oscillations of the droplet gives informations on the competition between surface tension and gravity
+\cite{White}.
 For the welding conditions of the experiment, the trajectories of the different pulse indicates 
@@
 or are negligible in respect to the size of the droplet.
-% Ajouter qq chose
+
 Despite the two dimensional analysis, the result gives important informations for 
-simulation of metal transfert process.
+simulation of metal transfert process. If  the droplet is assumed to be a sphere
+ the kinetic energy of the droplet just before impact could be estimated. For our case,
+The radius of the droplet is estimated at 0.56mm and the kinetic energy is around 6e-8J.
 

### 2011-01-27 articles/MIG/doc_broullion/latex/paper-drop.tex

@@
 
-\title[Macro drop and droplet profile detection during PGMAW process by image processing library]{Macro drop and droplet profile detection during PGMAW process by image processing library}
+\title[Macro drop and droplet profile detection during PGMAW process by image processing]{Macro drop and droplet profile detection during PGMAW process by image processing}
 
-\author{E Romero, C Bordreuil, J Chapuis, F Souliez, G Fras}
+\author{E Romero, C Bordreuil, J Chapuis, F Souli\'e, G Fras}
 
-\address{IOP 
-Publishing, Dirac
-House, Temple Back, Bristol BS1 6BE, UK}
-\ead{custserv@iop.org}
+\address{Laboratoire de MÈcanique et GÈnie Civil,
+CC048, Place EugËne Bataillon, UniversitÈ Montpellier 2,
+34095 Montpellier, France}
+\ead{cyril.bordreuil@univ-montp2.fr}
 
@@
 
-A better comprehension of welding objects behavior presents in a PGMAW process
- as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
+A better comprehension of  behavior of the weld pool or the metal droplet  in a PGMAW process
+ could help to improve numerical simulations
  and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
@@
  For example, the
- increase of productivity means often increase of weld speed,
- however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
+ increase of productivity means often increase of welding speed.
+ However welding defects  related to bad shape, as the hump formations, limit the maximum weld 
  speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
@@
   geometrical analysis of macro drop and droplets in order to extract 
-  qualitative information of these welding objects. 
+  qualitative information of these welding entities.
+
 There have been many studies on visual sensing techniques for observing weld pool 
-  image \cite{BAE} and metal transfer process during welding \cite{LIN}. Optical sensors like high speed 
- cameras and lighting systems have been widely use in GMAW process to realize 
- image acquisition \cite{ZHANG4},
+image \cite{BAE} and metal transfer process during welding \cite{LIN}.
+Optical sensors like high speed  cameras and lighting systems have been
+widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
 control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
-   Image processing plays a critical role in 
-   extracting useful information from visual scenes \cite{WANG}.
+Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
 Nevertheless the strong interference from the arc lightning required more than standard 
@@
 The paper is organized as follows. First, the purpose of the library is explained, then 
-     the experimental setup to study macro drop analysis is detailed. The library and the algorithms
+the experimental setup that will allow to appreciate the performance of the algorithm,
+ to study macro drop analysis is detailed. The library and the algorithms
 developed are explained and some results are shown on the macro drop and droplet study.
@@
  and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}
+% Il semble alors important de quantifier expÈrimentalement des donnÈes
 
-Then the shape and size kinetic analysis of macro drop and droplets could help to better understand 
+Then the shape and kinetic analysis of macro drop and droplets could help to better understand 
 and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a 
@@
 required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
-  per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others)
-   from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related 
-   with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies 
-   frames and electrical signals.
+per second \cite{WANG}. Therefore the algorithms have to be able to extract 
+the geometrical information (area, size and others) from the macro drop and droplets,
+from a huge amount of data. In addition, the voltage and current signals are directly related 
+with the droplet formation at the wire \cite{BALSAMO}.
+% Good synchronizations methods have to 
+%be applied between shadowgraphies 
+%frames and electrical signals.
 
@@
 Some definitions and brief description of generals principles used in
- image processing are required to better understand how is work the 
-algorithms utilized by the erCv library.
+ image processing are required to better understand  the 
+algorithms and the design of the library.
 
@@
 and interpret the space between different textures zones as edges.
-There exist a large spectrum of algorithms to image treatment, in particular to edges detect. Most of them can be classified by the way that his operate above the image pixels and grey level.
+There exist a large spectrum of algorithms to image treatment, in particular to edges detect.
+ Most of them can be classified by the way that his operate above the image pixels and grey level.
 
@@
 
-The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
+The filters are algorithms that operate as mathematical functions $f$ above the 
+$X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
 $f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
-Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are 
-widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the 
-image; this allows the filter a better edges localisation (see figure \ref{photo-explication-filter}). For this reason, Canny filter is widely 
-use at erCv library to detect the welding elements edges. However, it is sensible to noise or secondary greyness gradients in the image
+Different kind of filters can be mentioned as median, Gaussian, impulse,
+ adaptive and others. The impulse filters such Canny are 
+widely use to edge detection \cite{COCQUEREZ}. These filter have an
+ impulse response to most important greyness gradient in the 
+image; this allows the filter a better edges localisation
+ (see figure \ref{photo-explication-filter}). 
+For this reason, Canny filter is widely 
+used in the library to detect the welding elements edges. 
+However, it is sensible to noise or secondary greyness gradients in the image
  and, in consequence, it have some difficulties to define closer surface.
@@
 
-Curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure 
-\ref{photo-explication-snake}). The central idea behind such an approach is to evolve a curve towards the lowest potential of a cost function. 
-However at each stage of curve evolution, each curve point potential has to be computed. A lot of point (better curve resolution) take a lot 
-computing time, and therefore are not yet apply to real time detection or relatively speed automatic image processing. For this reason snake algorithms are not used at erCv.
+Curve propagation is a popular technique in image analysis for object extraction,
+ object tracking, edge detection and others (see figure 
+\ref{photo-explication-snake}). The central idea behind such an approach
+ is to evolve a curve towards the lowest potential of a cost function. 
+However at each stage of curve evolution, each curve point potential has
+ to be computed. A lot of point (better curve resolution) take a lot 
+computing time, and therefore are not yet apply to real time detection
+ or relatively speed automatic image processing. For this reason snake algorithms are not used in the library.
 
@@
 
-A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. Each region is a connected set of pixels with 
-common properties (intensity, texture,...) \cite{COCQUEREZ}. The partition is generated by operations or comparisons methods between 
-regions. Generally, this treatment offers a good detection edges if the elements and surrounding area have different textures (see figure \ref{photo-explication-segmentation}). 
-Note that different regions can belong to the same partition and not be placed together, therefore the surface is not always connected and,
+A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. 
+Each region is a connected set of pixels with 
+common properties (intensity, texture,...) \cite{COCQUEREZ}.
+ The partition is generated by operations or comparisons methods between 
+regions. Generally, this treatment offers a good detection edges if
+ the elements and surrounding area have different textures (see figure
+ \ref{photo-explication-segmentation}). 
+Note that different regions can belong to the same partition and not
+ be placed together, therefore the surface is not always connected and,
  in consequence, the edges of the interest regions are not always closed.
@@
 \begin{center}    
-\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filter.png}}\\
-\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
-\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
+\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-patron.png}}
+\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-filter.png}}\\
+\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-snake.png}}
+\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-segmentation.png}}
 \end{center}
@@
 
-As mentioned, a multipurpose image processing library was developed and currently use at the laboratory, in order to analyze welding process objects.
-erCv is able to perform edge detection and geometrical analysis in a different welding objects such: Macro drop, droplets and weld pool.
-erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable and portable library able to perform real time
- contour detection. erCv is build in Phyton scripts link to C++, making it relatively convivial to use.
+As mentioned, a multipurpose image processing library was developed 
+and currently use at the laboratory, in order to analyze welding process objects.
+erCv is able to perform edge detection and geometrical analysis in a different 
+welding objects such: Macro drop, droplets and weld pool.
+erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
+and portable library able to perform real time
+ contour detection. erCv is implemented in  C++ with some bindings in python,
+ making it relatively convivial to use.
 erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
 \begin{description}
-\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD 
- camera are not calibrated and present light inhomogeneities and noise. In order to obtain the real shape and size of weld elements, this module 
- include calibrations algorithms. To detect the welding objects contours it is necessary to improve the weld element image. This module has the 
- pre-processing treatments to noise reduction and image enhancement. Then to start the edges detection process, this module includes processing
-  algorithms as segmentations by samples comparators, watershed transformation, filters edge detectors and histogram based methods.  
-\item[Geometrical Treatment and Analysis:] This module has to end the edge detection process, completing and in some cases extrapolating the weld
-   elements edge. It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes. 
-   This module uses a full geometry algorithm library, which include different algorithms such as triangulations and mesh generation, alpha shape and 
+\item[Image Treatment:] Due to weld process conditions such arc lightening, 
+ heat and electrodes positions; the raw image registered by CCD 
+ camera are not calibrated and present light inhomogeneities and 
+ noise. In order to obtain the real shape and size of weld elements, this module 
+ include calibrations algorithms. To detect the welding objects contours it is 
+ necessary to improve the weld element image. This module has the 
+ pre-processing treatments to noise reduction and image enhancement.
+ Then to start the edges detection process, this module includes processing
+ algorithms as segmentations by samples comparators, watershed transformation,
+ filters edge detectors and histogram based methods.  
+\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
+   segments to end the edge detection
+  process, completing and in some cases extrapolating the weld
+  elements edge. It is also responsible to compute the geometrical 
+  data of welding elements such weld pool surface and metal transfer drop volumes. 
+  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
+  such as triangulations and mesh generation, alpha shape and 
   convex hull generation and polygonal structures.
-\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the welding object edge from the image; this
-   required some criteria such as continuity, length or closer condition.  This module use graph algorithms to convert edges pixels points into connected 
-   segments, and therefore, identify and select the welding element edge using the criteria. This module is compose by connect segments, estimates
+\item[Graph Theories:] To compute the geometrical data of welding elements
+   it is necessary to extract the welding object edge from the image; this
+   required some criteria such as continuity, length or closer condition.
+   This module use graph algorithms to  identify and select the welding element edge using the
+   criteria. This module is composed by connected segments, estimates
    minimal cut, determine largest chain segments and others algorithms. 
-\item[Visualization:] This module is a set of functions use to execute, show and/or register the different steps at the image process.
+\item[Visualization:] This module is a set of 
+  functions use to execute, show and/or register the 
+  different steps at the image process.
 \end{description}
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
+\includegraphics[width=7cm,height=4cm]{images/schema-erCv.png}
 \caption{{\small Flow diagram of erCv library composition}}
@@
 
-The objective is to perform geometrical analysis and measure characteristic times of the macro drop and the droplet in a PGMAW process. Notes that
- geometrical analysis refers to area section of droplets, height profile of macro drop and wetting contacts angles of the macro drop. And characteristics 
- time’s measures refer to time to height stagnation of macro drop and fall time of droplet between electrodes. The methods choose is the image treatment 
+The objective is to perform geometrical analysis and measure characteristic
+times of the macro drop and the droplet in a PGMAW process. Notes that
+geometrical analysis refers to area section of droplets, height profile
+of macro drop and wetting contacts angles of the macro drop. 
+And characteristic times measures refer to time to height stagnation 
+of macro drop and fall time of droplet between electrodes. The method
+is the image treatment 
 of recorded image of PGMAW static process by a high speed CCD camera.
+% cb : Je vois pas ce que ca fout la?
+%--To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; 
+%--therefore an accurate, reliable and synchronizes  systems are requires due to the high amount
+%-- of data and highly noisy environment (electromagnetic noise and arc light radiation).
 
-To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; therefore an accurate, reliable and synchronizes 
- systems are requires due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).
+%--A platform has been developed at the laboratory to perform multi-physics measures 
+%--in arc welding process (see figure \ref{schema-platform}). The platform 
+%-- was conceive with an automatically procedure to synchronize, to acquire,
+%-- to manage and to exploit large flow of multi-physical experimental data (up to 2 Go
+%--  per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.
 
-A platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}). The platform 
- was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go
-  per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.
+%--\begin{figure}
+%--\begin{center}
+%--\includegraphics[width=7cm,height=4cm]{schema-platform.png}
+%--\caption{{\small Experimental platform and specific device}}
+%--\label{schema-platform}
+%--\end{center}
+%--\end{figure}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=7cm,height=4cm]{schema-platform.png}
-\caption{{\small Experimental platform and specific device}}
-\label{schema-platform}
-\end{center}
-\end{figure}
-
-To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data 
-  and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).
+%--To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data 
+%--  and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).
 
@@
 
-The PGMAW static process is recorded by Shadowgraphy optical method. A halogen lamp is use to light the weld process. To guarantee a homogeneous illumination 
-  of the welding process, a light diffuser is place in the optical path closer to the halogen lamp. Finally the shadows of welding elements are projected to the other side 
-  of the welding place. A Phantom V5.0 high speed camera is place and align at this side above the optical path (see figure \ref{schema-montage-experimental-GMAW}).
+The PGMAW static process is recorded by Shadowgraphy optical method. 
+A halogen lamp is use to light the weld process. To guarantee a homogeneous
+illumination of the welding process, a light diffuser is placed
+in the optical path closer to the halogen lamp. 
+Finally the shadows of welding elements are projected to the other side 
+of the welding place. A Phantom V5.0 high speed camera is place and align 
+at this side above the optical path (see figure \ref{schema-montage-experimental-GMAW}).
 
@@
 
-To enhance the image contrast of the weld elements inside the electric discharge, the intensity rate between arc light and halogen lamp have to be reduce. In order to this
-   a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens, to attenuate the arc light. Nevertheless, the raw images remain highly noisy by the arc light.
+To enhance the image contrast of the weld elements inside the electric discharge,
+the intensity rate between arc light and halogen lamp have to be reduce. In order to this
+a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens, 
+to attenuate the arc light. Nevertheless, the raw images remain highly 
+noisy by the arc light.
 
@@
 
-Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. The target is a steel disk of $10\ mm$ of thickness and ER70S steel 
-   welding wire.
-The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and percentage
-    of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon). Welding parameters values are summarize in tables \ref{table-parameters-static} to static and 
+Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. 
+The target is a steel disk of $10\ mm$ of thickness and 
+ER70S steel welding wire.
+The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$,
+ wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and 
+percentage of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon). 
+Welding parameters values are summarized in tables \ref{table-parameters-static} to static and 
 \ref{table-parameters-change} to variables parameters.
@@
 
-Welding current and arc voltage are recorded at $30\ kHz$ sampling rate. The images are recorded at $4000$ frames per seconds, which is enough to
-     measure macro drop radius and apparent liquid-solid contact angle histories. The images and electrical signals are synchronize, thanks to the
-      automatically approach made in the multi physics platform.
+%Welding current and arc voltage are recorded at $30\ kHz$ sampling rate.
+The images are recorded at $4000$ frames per seconds, which is enough to
+measure macro drop radius and apparent liquid-solid contact angle histories. 
+%The images and electrical signals are synchronize, thanks to the
+%automatically approach made in the multi physics platform.
 
@@
 
-The purpose is to study the evolution of weld pool object in a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
+The purpose is to study the evolution of weld pool object in
+a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
 of the macro drop according depositing droplets of feed wire.
 
-At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, the macro drop
-  center height $h_{m}$, the macro drop volume $V_{m}$, the penetration below the surface level $p$ and the wetting angles:
-   $\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real). With the indices $l$ and $r$ refer to left and
-    right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
+At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical 
+elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, 
+the macro drop center height $h_{m}$, the macro drop volume $V_{m}$, the
+penetration below the surface level $p$ and the wetting angles:
+$\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real).
+With the indices $l$ and $r$ refer to left and
+right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer
+to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
 
@@
 
-To the droplet or metal transfer drop the geometrical parameters to identify are: The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
-    Finally in order to better understand the droplet dynamic \cite{}, the physical elements to identify are: the fall time $t_{a}$ and the average 
+To the droplet or metal transfer drop the geometrical parameters to identify are:
+The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
+Finally in order to better understand the droplet dynamic \cite{}, 
+the physical elements to identify are: the fall time $t_{a}$ and the average 
 speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).
@@
 
-As was shown in section \ref{image-acquisition-setup}, the camera recording a shadow projection of the welding process. The projection is
-     supposed to be a section of the welding process image, orthogonal to the optical path. Therefore, to a first approach, not image projection 
-     correction is necessary. Only to calibrate the image dimension (at pixels) to the real objects dimension (at millimeters), a conversion scale is 
+As was shown in section \ref{image-acquisition-setup}, the camera recording a 
+shadow projection of the welding process. The projection is 
+supposed to be a section of the welding process image, orthogonal to the optical path.
+Therefore, to a first approach, not image projection 
+correction is necessary. Only to calibrate the image dimension 
+(at pixels) to the real objects dimension (at millimeters), a conversion scale is 
 made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .
@@
 
-The idea is to extract the macro drop and droplet shapes from the raw image and therefore to extract the geometrical information. The most common 
-     approach is to segment the image \cite{WANG}. That means to separate in two fields (color) the image. The macro drop and droplet in one color and
-      the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition (shadowgraphy) the images are already segmented between
-       light and shadow zones (see figures \ref{photo-macro-drop-original}); where the shadows zones are the projection of the macro drop and droplet.
+The idea is to extract the macro drop and droplet shapes 
+from the raw images and therefore to extract the geometrical information.
+ The most common approach is to segment the image \cite{WANG}. 
+That means to separate in two fields (color) the image. The macro drop and droplet in one color and
+the rest of the image in other \cite{COCQUEREZ}. Thanks to the optical method acquisition
+ (shadowgraphy) the images are already segmented between
+light and shadow zones (see figures \ref{photo-macro-drop-original});
+ where the shadows zones are the projection of the macro drop and droplet.
 
-However objects within the arc may differ only by few intensity light level from the background. In these images areas a contrast enhancement is necessary. 
-       Objects outside the arc, as the some regions of the macro drop profile, are clearly visible against the background. In these regions a contrast enhancement 
-       can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}. Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.
+However objects within the arc may differ only by few intensity light level
+from the background. In these images areas a contrast enhancement is necessary. 
+Objects outside the arc, as the some regions of the macro drop profile,
+ are clearly visible against the background. In these regions a contrast enhancement 
+can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
+ Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.
 
-To simplify the contrast enhancement, the images are converted from RGB image color to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
-       reduce the grey level noise, a first smooth classical filter (Blur) is applied over the image. The filter replace the grey values of squares of $7\times 7$ 
-       pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). In consequence, the homogeneity quality is improve into the light and 
+To simplify the contrast enhancement, the images are converted from RGB image color 
+to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
+reduce the grey level noise, a first smooth classical filter 
+(Blur) is applied over the image. The filter replace
+the grey values of squares of $7\times 7$ 
+pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
+In consequence, the homogeneity quality is improve into the light and 
 shadows regions, despite the edge contrast reduction induce between these regions.
 
-Then, a regions adaptive threshold can be used to enhance the difference between shadow elements and light zones. To the adaptive threshold it is important 
-       to choose the correct size region where it will be applied. Small regions to threshold will generate isolates patters (groups of pixels). Big regions will generate
-        a classical like threshold image \cite{SABER}. The region size dominium choose to threshold application is $23\times 23\ pixels$. The threshold criteria choose 
-        is binary: $greyL_{thres}(x,y) = max_value$ if $greyL_{origin}(x,y) >  threshold(x,y)$ or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
-         to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter, $max_value$ is the grey level value choose to identify the pixels above
-          threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
-           $threshold(x,y)$ is obtain by subtraction between the average grey level of region pixels neighborhood and a constant parameter $C_{threshold}$.  
-           Small edge defects can still be found, due to the previous smooth filter and some arc light interference regions, which are bigger than regions size to
+Then, a regions adaptive threshold can be used to enhance the difference
+between shadow elements and light zones. To the adaptive threshold it is important 
+to choose the correct size region where it will be applied. Small regions to threshold
+will generate isolates patters (groups of pixels). Big regions will generate
+a classical like threshold image \cite{SABER}. The region size dominium choose
+to threshold application is $23\times 23\ pixels$. The threshold criteria 
+choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
+or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
+to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
+ $max_value$ is the grey level value choose to identify the pixels above
+threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
+ before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
+$threshold(x,y)$ is obtain by subtraction between the average grey level of region
+ pixels neighborhood and a constant parameter $C_{threshold}$.  
+Small edge defects can still be found, due to the previous smooth filter and some arc 
+light interference regions, which are bigger than regions size to
 threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).
 
-A second filter type median is necessary to improve the previous threshold treatment. This filter compute the grayness median value over $7\times 7\ pixels$
-             region. The image, which is already binary type due to adaptive threshold processing, is enhancing in his mixed black white regions depending of 
-             median value. In consequence contour quality between light and shadows regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).
+A second filter type median is necessary to improve the previous threshold treatment. 
+This filter compute the grayness median value over $7\times 7\ pixels$
+region. The image, which is already binary type due to adaptive threshold processing,
+ is enhancing in his mixed black white regions depending of 
+ median value. In consequence contour quality between light and shadows
+ regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).
 
-Finally an impulse response filter to grey level gradient (Canny) is applied to extract the principal edges at image. In a binary image, all edges are principals,
-    therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}). Nevertheless to guarantee a full detection of droplet and 
-         macro drop profile, the canny parameters are adjusted to maximum, which means maximum edge detection sensibility.
+Finally an impulse response filter to grey level gradient (Canny) is applied to extract 
+the principal edges at image. In a binary image, all edges are principals,
+therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
+Nevertheless to guarantee a full detection of droplet and 
+ macro drop profile, the canny parameters are adjusted to maximum, 
+which means maximum edge detection sensibility.
 
@@
 \begin{center}    
-\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-original.png}}
-\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-grey.png}}\\
-\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothblur.png}}
-\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-adaptivethreshold.png}}\\
-\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-smoothmedian.png}}
-\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-macro-drop-canny.png}}\\
+\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
+\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-grey.png}}\\
+\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothblur.png}}
+\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-adaptivethreshold.png}}\\
+\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothmedian.png}}
+\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-canny.png}}\\
 \end{center}
@@
 \label{edge_extraction}
-Despite performance achieve by the image treatment, Canny filter generate many edges, or cords, in the image. These cord are composed by white pixels, 
-              interpreted by the algorithms as an individuals points. In order to automate the edge extraction process, geometrical and graph algorithms are used 
-              to isolate the cords corresponding to macro drop profile and edge section droplet.
+Despite performance achieve by the image treatment, Canny filter
+ generate many edges, or cords, in the image. These cord are composed
+ by white pixels, interpreted by the algorithms as an individuals points.
+ In order to automate the edge extraction process, geometrical and
+ graph algorithms are used  to isolate the cords corresponding to
+ macro drop profile and edge section droplet.
 
-To the macro drop profile a user interaction algorithm is responsible to extract the continuous cord (white pixels) corresponding to the profile into a list. Note 
-              that the macro drop and the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}. The substrate shadow projection 
-              is always the same if the optical path doesn’t change. Therefore the users have only to choose, to first image in the experience series, one extreme 
-              of the cord corresponding to substrate profile (see figures \ref{photo-results-macro-drop}). Then the algorithm finds all new white pixels inside a 
-              small neighbor around the pixels selected by the user. Each new white pixel
-               is added to the profile list. Starting at each new pixel, this process continues, automatically, until the other extreme of the cord, until the last image of the series.
+To the macro drop profile a user interaction algorithm is responsible
+ to extract the continuous cord (white pixels) corresponding
+ to the profile into a list. Note  that the macro drop and 
+the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}.
+ The substrate shadow projection is always the same if the optical
+ path doesn’t change. Therefore the users have only to choose, to
+ first image in the experience series, one extreme  of the cord 
+corresponding to substrate profile (see figures \ref{photo-results-macro-drop}).
+ Then the algorithm finds all new white pixels inside small neighbor around
+ the pixels selected by the user. Each new white pixel  is added to the
+ profile list. Starting at each new pixel, this process continues,
+ automatically, until the other extreme of the cord, until the last
+ image of the series.
 
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t1.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t2.png}}\\
-\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t3.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{photo-results-macro-drop-t4.png}}\\
+\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t1.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t2.png}}\\
+\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t3.png}}
+\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t4.png}}\\
 \end{center}
@@
 
-To the droplet edge section, the white points cord defines the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer cord
-                correspond to the droplet section. The idea is to build segments around the cords, and take the longest closer segment.
+To the droplet edge section, the white points cord defines 
+the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer
+ cord correspond to the droplet section. The idea is to build segments around
+ the cords, and take the longest closer segment.
 
-Give $S$ the set of points in the space image. The segments could be building between wherever two points of $S$. However, to fulfill the cords with 
-                segments, only the points placed together could define a segment. To choose the correct points of $S$ a Delaunay triangulation is made 
-                over $S$ \cite{CGAL}. Each point of $S$ is a vertices of a triangle and then each potential 
-                segment is a side of a triangle. The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means 
-                minimal length sides to the triangles \cite{GEOMETRICAL}. Give $\beta$ the cord surrounding the external hull of the Delaunay triangulation of $S$. 
-                An alpha shape algorithm uses a $\alpha \in N$ parameter, or square radius of a test circle, to travel from outside $\beta$ to inside 
-                the triangulation. The circle has to go through the triangles sides without touch the vertices. Give $n$ the number of triangles sides of triangulation
-                 and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ with
-                 $i \in\{1,n\}$, a segment is build between the respective vertices or points. At the end of the process, a segments set know as $\alpha$-shape has
-                  been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL-library}. 
-                  If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through every side in the triangulation, 
-                 then no segment are created and $\alpha$-shape became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$ 
-                 is sufficient to create a segment set around the droplet (see figure \ref{photo-droplet-alpha-shape}).
+Give $S$ the set of points in the space image. The segments could 
+be building between wherever two points of $S$. However, to fulfill
+ the cords with segments, only the points placed together could define
+ a segment. To choose the correct points of $S$ a Delaunay triangulation
+ is made over $S$ \cite{CGAL}. Each point of $S$ is a vertices 
+of a triangle and then each potential segment is a side of a triangle. 
+The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
+ Give $\beta$ the cord surrounding the external hull of the Delaunay
+ triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
+ or square radius of a test circle, to travel from outside $\beta$ to inside
+ the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
+$n$ the number of triangles sides of triangulation
+and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
+with $i \in\{1,n\}$, a segment is build between the respective vertices or
+ points. At the end of the process, a segments set know as $\alpha$-shape has been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
+ is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
+ every side in the triangulation,  then no segment are created and $\alpha$-shape
+ became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
+ is sufficient to create a segment set around the droplet
+ (see figure \ref{photo-droplet-alpha-shape}).
 
@@
 \section{ Results}
-\subsection{ Macro Drop analyzes}
-\subsection{ Droplet analyzes}
+In this part some results, performance and reliability of the library for a set of experiment
+are shown. The basic experiment is static Pulse Gas Tungsten Arc Welding.
+A macrodrop is feed by droplets at a frequency of 110 Hertz. The droplets are assumed to flight vertically and
+then to feed the macro drop generated. The macrodrop grows with a geometry that depends on the effects of gravity
+but also of surface tension,.....
+For the same welding parameters, the shielding gas will be modified and the modification of
+the advance of the basis radius will be demonstrated.
+
+To improve weld quality in pulsed GMAW, the dynamic of the droplet is investigated.
+The analysis focus on the regularity of the transfert and some statistics are shown.
+
+Some analysing time are given in order to appreciate the performance of the library with sophisticated
+algorithm.
+
+\subsection{ Macro Drop growth investigation}
+The investigation of the macro drop growth needs the study of two quantities:
+
+\begin{itemize}
+\item The angle between the substrate and the liquid
+\item The speed of growth of the macro drop radius
+\end{itemize}
+
+The macro drop is assumed to be axisymmetric so this two quantities are representative of the 
+geometry or its evolution.
+
+\subsection{ Droplet flight}
 

### 2011-02-15 articles/MIG/paper-drop_v1.tex

@@
 \usepackage[sf]{subfigure}
-\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
+%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
 %Uncomment next line if AMS fonts required
@@
 
-\title[Macro drop and droplet profile detection during PGMAW process by image processing]{Macro drop and droplet profile detection during PGMAW process by image processing}
+\title[Macro drop and droplet profile detection during PGMAW process by image processing]
+{Macro drop and droplet profile detection during PGMAW process by image processing}
 
@@
 \begin{abstract}
-
+The paper describes some new image treatment algorithm used to 
+detect profiles during arc welding process. The new algorithm 
+are an agregation of some available algorithm of image treatement,
+computational geometry and graph theory. The algorithm allows to extract precise
+geometrical entities as closed or open profiles that could be used for monitoring
+of welding process. The algorithm even if used external libraries is really efficient
+and could be used for real time monitoring.
 \end{abstract}
@@
 %\vspace{2pc}
-%\noindent{\it Keywords}: Article preparation, IOP journals
+\noindent{\it Keywords}: Arc welding, Image treatment, Melt pool,  Profile detection, Monitoring, 
 % Uncomment for Submitted to journal title message
-%\submitto{\JPA}
+\submitto{\MST}
 % Comment out if separate title page not required
@@
 
-A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arx Welding (PGMAW)
+A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arc Welding (PGMAW)
  process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
@@
 fluctuations \cite{WANG}. The measurement of the geometry of the free surface 
-of macrodrop or droplets is an important information for the understanding and
-the validation of the simulation.
+of macrodrop or droplets is an important information for the understanding of the physical phenomenom 
+during welding and
+the validation of the simulation of welding process.
 
-The monitoring of the shape and size of these welding objects uring
+In this article, the monitoring of the shape and size of these welding objects during
 static PGMAW  is 
@@
 speed of wire feed process, a high speed camera and an effective image processing algorithms are 
-required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
-per second \cite{WANG}. Therefore the algorithms have to be able to extract 
+required \cite{WANG}. The  frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
+per second. Therefore the algorithms have to be able to extract 
 the geometrical information (area, size and others) from the macro drop and droplets,
@@
 Nevertheless the strong interference from the arc lightning required more than standard 
-image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
+image treatment to analyse the raw images of the welding process \cite{NORDBRUCH}. 
 Previous work has shown that is possible to perform geometrical 
@@
 parameters from macro drop and droplets, has been obtained using the mentioned library.
- Using this, a dimension and dimensionless analysis will 
-be done. The intention is to help to simplify future numerical models and enhance monitoring by direct observation.
+  The purpose is to help simplification of future numerical models and enhance monitoring by direct observation.
 
@@
  to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
-during welding process. Then 
- The library and the algorithms are explained and some results are shown on the macro drop and droplet study.
+during welding process. 
+Then The library and the algorithms are explained and some results are shown on the macro drop and droplet study.
+The objective  is to perform geometrical analysis and measure characteristic
+times of the macro drop growth and the droplet during the free flight 
+during  a static PGMAW process.
 
@@
 
-The objective is to perform geometrical analysis and measure characteristic
-times of the macro drop growth and the droplet during the free flight 
-during  a static PGMAW process. 
 A specific data acquisition setup was done at the lab in order to
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{images/schema-montage-experimental-GMAW.png}
+\includegraphics[width=7cm,height=4cm]{images/setup.png}
 \caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
@@
 
-To the droplet or metal transfer drop the geometrical parameters to identify are:
+For the droplet or metal transfer drop, the geometrical parameters to identify are:
 The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
@@
 erCv is able to perform edge detection and geometrical analysis in a different 
-welding objects such: Macro drop, droplets and weld pool.
+welding objects such as Macro drop, droplets and weld pool.
 erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
 and portable library able to perform real time
- contour detection. erCv is implemented in  C++ with some bindings in python,
+ contour detection. The library is implemented in  C++ with some bindings in python,
  making it relatively convivial to use for non-programmers.
-erCv is composed by four processing modules: 
+The library is composed by four processing modules: 
 \begin{description}
@@
 
-The originality of the library comes from the agregation and complementarity of the different numerical tools.
+The originality of the library comes from the agregation 
+and complementarity of the different numerical tools.
 The main difficulty is to find algorithms with good parameters all along the process.
 
-\subsection{ The Analyze methods}
+\subsection{ The Analyzing methods}
 \label{ the-analyze-methods}
@@
 light and shadow zones (see figures \ref{photo-macro-drop-original});
- where the shadows zones are the projection of the macro drop and droplet.
+ where the shadow zones are the projection of the macro drop and droplet.
 
 However objects within the image under the arc may differ only by few intensity light level
-from the background. In these images areas a contrast enhancement is necessary. 
-Objects outside the arc, as the some regions of the macro drop profile,
+from the background. In these images areas, a contrast enhancement is necessary. 
+Objects outside the arc, as  some regions of the macro drop profile,
  are clearly visible against the background. In these regions a contrast enhancement 
 can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
- Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.
+ Therefore the contrast enhancements, or threshold, have to be adapted per regions in the image.
 
@@
 
-Then, a regions adaptive threshold can be used to enhance the difference
+Then, a  adaptive threshold can be used to enhance the difference
 between shadow elements and light zones. To the adaptive threshold it is important 
 to choose the correct size region where it will be applied. Small regions to threshold
-will generate isolates patters (groups of pixels). Big regions will generate
+will generate isolated patterns (groups of pixels). Big regions will generate
 a classical like threshold image \cite{SABER}. The region size dominium choose
@@
 Finally an impulse response filter to grey level gradient (Canny) is applied to extract 
-the principal edges at image. In a binary image, all edges are principals,
+the principal edges at image. In a binary image, all edges are principal,
 therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
@@
  The substrate shadow projection is always the same if the optical
- path doesn’t change. Therefore the users have only to choose, to
+ path doesn't change. Therefore the users have only to choose, the
  first image in the experience series, one extreme  of the cord 
@@
  a segment. To choose the correct points of $S$ a Delaunay triangulation
- is made over $S$ \cite{CGAL}. Each point of $S$ is a vertice 
-of a triangle and then each potential segment is a side of a triangle. 
+ is made over $S$ \cite{CGAL}. Each point of $S$ is a vertex
+of a triangle and then each potential segment is a edge of a triangle. 
 The Delaunay triangulations guarantee a unique solution with minimal
- internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
+ internal angles for each triangle, which means  minimal
+ length sides to the triangles \cite{GEOMETRICAL}.
  Give $\beta$ the cord surrounding the external hull of the Delaunay
@@
  or square radius of a test circle, to travel from outside $\beta$ to inside
- the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
+ the triangulation. The circle has to go through the triangles sides without touching the vertices. Give 
 $n$ the number of triangles sides of triangulation
 and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
-with $i \in\{1,n\}$, a segment is build between the respective vertices or
+with $i \in\{1,n\}$, a segment is marked between the respective vertices or
  points. At the end of the process, a  set of segments knows as $\alpha$-shape has been created.
-  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
+  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can't go inside $\beta$, then $\alpha$-shape
  is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
@@
 
-A graph algorithm connects this segment and finds the longest closer segment. The longest closer segment corresponds to the metal transfer drop profile 
+A graph algorithm connects this segment and finds the longest closer segment.
+ The longest closer segment corresponds to the metal transfer drop profile 
 (see figure \ref{photo-results-droplet}).
@@
 at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
-angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
+angle measure, linear regressions or least squares (parabolic, ellipse, circle) 
 are taken from the processed macro drop extracted profiles.
@@
 \section{ Results}
-In this part some results, performance and reliability of the library for a set of experiment
+In this part some results, performance and reliability of the library for a set of experiments
 are shown. The basic experiment is a static PGMAW.
@@
 
-The algoritms are tested on a i7 processor from Intel with 1.87Ghz.
+The algoritms are tested on a i7 processor from Intel with 1.87Ghz RAM.
 
@@
 
-The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
+The evolution curves are also noisy. Videos investigation shows that the macrodrop oscillates during welding. 
 Macrodrop oscillations induced  wetting angle oscillations. Depending of the main oscillations during
 a period, the local angle oscillation is more or less important. For pure Argon
-gas, the equilibrium angle (60 degrees) rapidly reached and stays constant all along the welding.
+gas, the equilibrium angle (60 degrees) is rapidly reached and stays constant all along the welding.
 For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.
 
-\subsubsection{Discussion}
+\subsubsection{Discussions}
 The noise in the measure for the basis could be attributed
@@
 are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
-Pure Argon shielding lead to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
+Pure Argon shielding leads to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
 at the triple joint (liquid-gas-substrate) is higher modifying then the behaviour of the overall interface.
@@
  the kinetic energy of the droplet just before impact could be estimated. For our case,
-The radius of the droplet is estimated at 0.56mm and the kinetic energy is around 6e-8J.
+The radius of the droplet is estimated at 0.56mm. % and the kinetic energy is around 6e-8J.
 
@@
 
-\bibliography{paper_bain}
+%\bibliography{paper_bain}
 
@@
 %\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
+
+% \cite{BALSAMO}
+%\cite{WANG}
+%\cite{CHO}
+%\cite{LIN}
+% \cite{ZHANG4}
+%\cite{BAE}
+%\cite{NORDBRUCH}
+%\bibitem{CGAL} http://www.cgal.org 
+%\cite{ChapuisThesis}
+%\cite{WU1}
+%\cite{SEED}
+% \cite{COCQUEREZ}
+% \cite{OPENCV}
+% \cite{GEOMETRICAL}
 %\end{thebibliography}
-\bibitem{CGAL} http://www.cgal.org 
 \end{document}

### 2011-02-15 articles/MIG/doc_broullion/latex/paper-drop.tex

@@
 \begin{center}    
-\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-filter.png}}\\
+\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
+\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filter.png}}\\
 \subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-snake.png}}

### 2011-02-15 articles/MIG/paper-drop.tex

--- 2011-01-27 articles/MIG/doc_broullion/latex/paper-drop.tex
@@
 
-\author{E Romero, C Bordreuil, J Chapuis, F Souli\'e, G Fras}
+\author{E Romero, J Chapuis ,C Bordreuil, F Souli\'e, G Fras}
 
@@
  However welding defects  related to bad shape, as the hump formations, limit the maximum weld 
- speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
+ speed \cite{CHAPUIS} and therefore the productivity. 
  In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
@@
 or height has been measure using different and 
-specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
+specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SAEED},
 \cite{NORDBRUCH}. However, to date, effectively automatic images processing
@@
 simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition
- and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}
+ and the hump size. Same relations has been found between metal transfer process and welding quality \cite{BINGUL}
 % Il semble alors important de quantifier expÈrimentalement des donnÈes
@@
 B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
-\mbox{with} R_{i} \neq \emptyset \\
-\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
+\mbox{with}\ R_{i} \neq \emptyset \\
+\mbox{and}\  R_{i}\bigcap R_{j} = \emptyset\  \forall i, j\ \mbox{with}\ i \neq j\ 
 \label{equation-segmentation}
@@
 Each region is a connected set of pixels with 
-common properties (intensity, texture,...) \cite{COCQUEREZ}.
+common prope	rties (intensity, texture,...) \cite{COCQUEREZ}.
  The partition is generated by operations or comparisons methods between 
@@
 The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
-Finally in order to better understand the droplet dynamic \cite{}, 
+Finally in order to better understand the droplet dynamic, 
 the physical elements to identify are: the fall time $t_{a}$ and the average 
@@
 
-As was shown in section \ref{image-acquisition-setup}, the camera recording a 
+The high speed camera use to the process monitorization, recording a 
 shadow projection of the welding process. The projection is 
@@
 to threshold application is $23\times 23\ pixels$. The threshold criteria 
-choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
-or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
+choose is binary: $grey_level_threshold(x,y) = max_value$ if $grey_level_origin(x,y) >  threshold(x,y)$
+or $grey_level_threshold(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
 to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
@@
 \begin{center}    
-\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
+\subfigure[Macro drop raw image]{\label{photo-macro-drop-original}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
 \subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-grey.png}}\\
@@
 of a triangle and then each potential segment is a side of a triangle. 
-The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
+The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{BERG}.
  Give $\beta$ the cord surrounding the external hull of the Delaunay
@@
  points. At the end of the process, a segments set know as $\alpha$-shape has been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
- is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
+ is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i}\ \forall i$ the circle go through
  every side in the triangulation,  then no segment are created and $\alpha$-shape
@@
 In this part some results, performance and reliability of the library for a set of experiment
-are shown. The basic experiment is static Pulse Gas Tungsten Arc Welding.
+are shown. The basic experiment is a static Pulsed Gas Tungsten Arc Welding.
 A macrodrop is feed by droplets at a frequency of 110 Hertz. The droplets are assumed to flight vertically and
 then to feed the macro drop generated. The macrodrop grows with a geometry that depends on the effects of gravity
-but also of surface tension,.....
+but also of surface tension, heat transfert,...
 For the same welding parameters, the shielding gas will be modified and the modification of
@@
 
-Some analysing time are given in order to appreciate the performance of the library with sophisticated
+Some characteristic time are given in order to appreciate the performance of the library with sophisticated
 algorithm.
@@
 
-The macro drop is assumed to be axisymmetric so this two quantities are representative of the 
-geometry or its evolution.
+The first item give information on the capillarity mechanism involved in the macrodrop and
+the second is an indicator of the ease of growth of the macrodrop that is a double effect between
+heat transfert and tension surface.
+
+\subsubsection{Experiments}
+Two different shielding gases were used.
+Their composition is given in table \ref{tab::gases}.
+
+\begin{table}[h]
+\begin{tabular}{|c|c|c|}
+\hline
+Gaz & Argon (\%) & $CO_2$(\%) \\ \hline
+G1 & 100       & 0 \\ \hline
+G2 & 92        & 8 \\ \hline
+\end{tabular}
+\caption{Shielding gas composition}\label{tab::gases}
+\end{table}
+
+The shielding gas has a great effect between the liquid and the gas interface. Gas could diffuse in the
+first layer of the liquid and greatly modify the physical properties. The tension surface is the main physical
+property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
+its equilibrium. It has to be kept in mind that modification of shielding composition will also modify
+the plasma energetical and momentum distribution that could also  influence the shape of the interface.
+
+The optical technic is the ombroscopy technic that will reveal contour. Because the static PGMAW will generate
+almost an axisymmetrical shape, the projection of the scene on the CCD sensor can give information on the shape of the 
+macrodrop.
+
+To study the influence of the gases on the shape of the gas liquid interface, images must be selected in cold
+regime of the plasma in the period. It is better to select images at the end of the period when the macrodrop is
+stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
+
+\subsubsection{Contour Detection}
+
+\subsubsection{Discussion}
 
 \subsection{ Droplet flight}
+Droplet flight investigation is of interest for weld quality and the metal deposition process.
+The determination of the motion and the impact point is then a good indicator of the quality of the
+process.
 
@@
 
-\bibliography{paper_bain}
+\bibliography{paper_bain_drop}
 
@@
 %\end{thebibliography}
-\bibitem{CGAL} http://www.cgal.org 
+%\bibitem{CGAL} http://www.cgal.org 
 \end{document}

### 2011-02-15 examples/melt_pool_TIG/fusion_bain_python.cpp

@@ -33,7 +33,7 @@ int main( int hola, char** file_name)
   //rec_tem.x = 14; rec_tem.y = 20; rec_tem.width = 5; rec_tem.height = 5;
   erTemplP templ(SQDIFF_NORMED, rec_tem, true); 
   erAlphaP alp(1);
-  erWeldPoolAnalysis wpa("full_bain_1");
+  erWeldPoolAnalysis wpa("full_bain_2");
 
   wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
   wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);
@@ -51,7 +51,6 @@ int main( int hola, char** file_name)
 //     };
 //   wpa.saveParameters( "result/test.out");
 //=======
-
   wpa.doIt( "example_full_bain_1.bmp");
   wpa.doIt( "example_full_bain_2.bmp");
   wpa.doIt( "example_full_bain_3.bmp");

### 2011-02-15 include/erCv/geometry/erCgalConvexPolygone.hpp

@@ -1,3 +1,37 @@
+// Copyright Universite Montpellier 2/CNRS 
+// Contributor(s) : 
+//         Edward Romero 
+//         Cyril Bordreuil
+// Contact: cyril.bordreuil@univ-montp2.fr
+// 
+// This software is a computer program whose purpose is to [describe
+//  functionalities and technical features of your software].
+//
+// This software is governed by the CeCILL license under French law and
+// abiding by the rules of distribution of free software.  You can  use, 
+// modify and/ or redistribute the software under the terms of the CeCILL
+// license as circulated by CEA, CNRS and INRIA at the following URL
+// "http://www.cecill.info". 
+//
+// As a counterpart to the access to the source code and  rights to copy,
+// modify and redistribute granted by the license, users are provided only
+// with a limited warranty  and the software's author,  the holder of the
+// economic rights,  and the successive licensors  have only  limited
+// liability. 
+//
+// In this respect, the user's attention is drawn to the risks associated
+// with loading,  using,  modifying and/or developing or reproducing the
+// software by the user in light of its specific status of free software,
+// that may mean  that it is complicated to manipulate,  and  that  also
+// therefore means  that it is reserved for developers  and  experienced
+// professionals having in-depth computer knowledge. Users are therefore
+// encouraged to load and test the software's suitability as regards their
+// requirements in conditions enabling the security of their systems and/or 
+// data to be ensured and,  more generally, to use and operate it in the 
+// same conditions as regards security. 
+// 
+// The fact that you are presently reading this means that you have had
+// knowledge of the CeCILL license and that you accept its terms.
 //#ifndef _ER_CGAL_POLYGON_2_HPP_
 //#define _ER_CGAL_POLYGON_2_HPP_
 #ifndef _ERCV_CGAL_CONVEX_HULL_HPP_

### 2011-02-23 articles/MIG/paper-drop_v1.tex

@@
 
-\title[Macro drop and droplet profile detection during PGMAW process by image processing]
-{Macro drop and droplet profile detection during PGMAW process by image processing}
+\title[Image Processing  for  profile detection during PGMAW]
+{Image Processing and geometrical analysis for  profile detection during P-Gas Metal Arc Welding}
 
@@
 detect profiles during arc welding process. The new algorithm 
-are an agregation of some available algorithm of image treatement,
+is an agregation of some available algorithm of image treatement,
 computational geometry and graph theory. The algorithm allows to extract precise
 geometrical entities as closed or open profiles that could be used for monitoring
-of welding process. The algorithm even if used external libraries is really efficient
+of welding process. The algorithm  is shown to be really efficient
 and could be used for real time monitoring.
@@
 
-A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arc Welding (PGMAW)
+A better observation of behavior of the weld pool or the metal droplet 
+in a Pulsed Gas Metal Arc Welding (PGMAW)
  process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
@@
 of macrodrop or droplets is an important information for the understanding of the physical phenomenom 
-during welding and
-the validation of the simulation of welding process.
+during welding and the validation of the simulation of welding process.
+
+There have been many studies on visual sensing techniques for observing weld pool 
+image \cite{BAE} and metal transfer process during welding \cite{LIN}.
+Optical sensors like high speed  cameras and lighting systems have been
+widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
+control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
+After image acquisition, image processing plays a critical role in extracting useful 
+information from visual scenes \cite{WANG}.
+Nevertheless the strong interference from the arc lightning required more than standard 
+image treatment to analyse the raw images of the welding process \cite{NORDBRUCH}. 
+Previous work has shown that is possible to perform geometrical 
+analysis in weld pools or droplets \cite{WU1}.
+Parameters such as macro drop or droplets surface, volumes 
+or height has been measured using different and 
+specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SAEED},
+\cite{NORDBRUCH}. However, to date, effective automatic image processing
+of metal transfer has not been developed, possibly due to the  difficulty involved 
+for welding researchers \cite{WANG}.
 
@@
 speed of wire feed process, a high speed camera and an effective image processing algorithms are 
-required \cite{WANG}. The  frame rate acquisition to metal transfer drop kinetic analysis is $3000$ 
-per second. Therefore the algorithms have to be able to extract 
+required \cite{WANG}.  To have indicator on quality of the process,  the algorithms have to be able to extract 
 the geometrical information (area, size and others) from the macro drop and droplets,
-from a huge amount of data. In addition, the voltage and current signals are directly related 
+from these acquisition. In addition, the voltage and current signals are directly related 
 with the droplet formation at the wire \cite{BALSAMO}.
-
-There have been many studies on visual sensing techniques for observing weld pool 
-image \cite{BAE} and metal transfer process during welding \cite{LIN}.
-Optical sensors like high speed  cameras and lighting systems have been
-widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
-control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
-Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
-Nevertheless the strong interference from the arc lightning required more than standard 
-image treatment to analyse the raw images of the welding process \cite{NORDBRUCH}. 
-Previous work has shown that is possible to perform geometrical 
-analysis in weld pools or droplets \cite{WU1}.
-Parameters such as macro drop or droplets surface, volumes 
-or height has been measured using different and 
-specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
-\cite{NORDBRUCH}. However, to date, effective automatic image processing
-of metal transfer has not been developed, possibly due to the  difficulty involved 
-for welding researchers \cite{WANG}.
 
@@
 analysis, graph theory applications and image visualization.
-In a first step, and despite the different static and dynamic weld conditions, 
-as well as different current regime. A reliable 2D profiles and geometrical
-parameters from macro drop and droplets, has been obtained using the mentioned library.
-  The purpose is to help simplification of future numerical models and enhance monitoring by direct observation.
+The originality of the library comes from the gathering of these different
+theories on image treatment. The library use in depth algorithm from the different fields.
+The algorithm mixing graph theory, computational geometry, image processing are then applied to obtain 
+ 2D profiles and geometrical
+parameters from macro drop and droplets.
+The purpose is to help simplification of future numerical models 
+and improve welding monitoring setup by direct observation.
 
-The paper is organized as follows. First, the experimental setup that will allow to appreciate the performance of the algorithm,
- to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
+The paper is organized as follows. First, the experimental setup for the application
+ that will allow to appreciate the performance of the algorithm with
+  macro drop analysis is detailed in order to appreciate the difficulies of profile detection
 during welding process. 
-Then The library and the algorithms are explained and some results are shown on the macro drop and droplet study.
-The objective  is to perform geometrical analysis and measure characteristic
-times of the macro drop growth and the droplet during the free flight 
-during  a static PGMAW process.
+Then The library and the mixed algorithms are explained and some results are shown on the macro drop and droplet study.
+%The objective  is to perform geometrical analysis and measure characteristic
+%times of the macro drop growth and the droplet during the free flight 
+%during  a static PGMAW process.
 
@@
 
+The Gas Metal Arc Welding (GMAW) is set in pulsed mode in order that one droplet 
+is detached by pulsed from the wire. As an indicator, the peak current is measured at 300A and the wire speed
+is around 6m/min. The wire has 1mm diameter.
+
 \subsection{ Image acquisition setup}
-\label{ image_acquisition_setup}
+\label{image_acquisition_setup}
 
@@
 %automatically approach made in the multi physics platform.
-
 %Measurements are made using the erCv library.
 
-\subsection{ System definitions}
+% Algo dependant de l acquisition
+
+\subsection{Geometrical parameters}
 \label{system_definitions}
@@
 penetration below the surface level $p$ and the wetting angles:
-$\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real).
-With the indices $l$ and $r$ refer to left and
-right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer
-to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
-The angles and the base are the two main quantities to be measured. but the overall shape of
-the macrodrop is an important information for computation.
+$\Theta_{m(l))}$, $\Theta_{m(r)}$ (apparent) 
+with the indices $(l)$ and $(r)$ refer to left and
+right angles, the indice  $m$ refers to macro drop.
+The angles and the base are the two main quantities to be measured.
+The profile of the macrodrop and in particular its evolution vs time is
+interesting for the investigation of fluid dynamic inside the weld pool.
 
@@
 For the droplet or metal transfer drop, the geometrical parameters to identify are:
-The estimate volume $V_{a}$ and the estimate radius $R_{a}$. 
-Finally in order to better understand the droplet dynamic \cite{}, 
+ the measured radius $R_{a}$. 
+Finally in order to better understand the droplet dynamic, 
 the physical elements to identify are: the fall time $t_{a}$ and the average 
@@
 Some definitions and brief description of general principles used in
- image processing are required to measure the profiles. Then, the design of the library is briefly detailed
-to succeed to detect the profile in the noisy environment.
+ image processing are required to measure the profiles. Then, the design of the library 
+mixing different technics
+is briefly detailed  to detect the profile in the noisy environment.
+
 \subsection{Image treatment basics}
 \subsubsection{Some definitions}\label{some_definitions}
-A numerical grey image can be describe as 3D surface discretized by a grid mesh
+A numerical grey image can be described as 3D surface discretized by a grid mesh
  in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
@@
 A strong relief change or high gradient greyness values at
- the image are perceive by human eyes as light changes, and can be interpreted
+ the image are perceived by human eyes as light changes, and can be interpreted
  as objects edges.
@@
 Sometimes, a regular relief patrons or regular greyness
- variation can be distinguish. The human eyes can perceive these patrons as texture 
+ variation can be distinguished. The human eyes can perceive these patrons as texture 
 and interpret the space between different textures zones as edges.
-There exist a large spectrum of algorithms to image treatment, in particular to edges detect.
- Most of them can be classified by the way that his operate above the image pixels and grey level.
+There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
+ Most of them can be classified by the way  is operated above the image pixels and grey level.
 
@@
  adaptive and others. The impulse filters such Canny are 
-widely use to edge detection \cite{COCQUEREZ}. These filter have an
+widely use to edge detection \cite{COCQUEREZ}. These filters have an
  impulse response to most important greyness gradient in the 
@@
 However, it is sensible to noise or secondary greyness gradients in the image
- and, in consequence, it have some difficulties to define closer surface.
+ and, in consequence, it have some difficulties to define closed surface.
 
@@
  \ref{photo-explication-segmentation}). 
-Note that different regions can belong to the same partition and not
- be placed together, therefore the surface is not always connected and,
+Note that different regions can belong to the same partition,
+ therefore the surface is not always connected and,
  in consequence, the edges of the interest regions are not always closed.
@@
 
-As mentioned, a multipurpose image processing library was developed 
+A multipurpose image processing library was developed 
 and currently use at the laboratory, in order to analyze welding process objects.
@@
 welding objects such as Macro drop, droplets and weld pool.
-erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
+The library can manage
+different kinds of image acquisition (optical setup). 
+erCv is assembled in a oriented object C++ language.
+Then,  erCv is a scalable 
 and portable library able to perform real time
@@
  making it relatively convivial to use for non-programmers.
-The library is composed by four processing modules: 
+To manage the edge detection during welding process,
+the library is composed by four processing modules: 
 \begin{description}
@@
  necessary to improve the weld element image. This module has the 
- pre-processing treatments to noise reduction and image enhancement.
+ pre-processing treatments for noise reduction and image enhancement.
  Then to start the edges detection process, this module includes processing
- algorithms as segmentations by samples comparators, watershed transformation,
+ algorithms as segmentations by samples comparator, watershed transformation,
  filters edge detectors and histogram based methods.  
+ Most of the functionality comes from \cite{OPENCV}.
 \item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
@@
    it is necessary to extract the welding object edge from the image; this
-   required some criteria such as continuity, length or closer condition.
+   required some criteria such as continuity, length or closing condition.
    This module use graph algorithms to  identify and select the welding element edge using the
@@
    minimal cut, determine largest chain segments and others algorithms. 
+   The algorithm of \cite{BOOSTGRAPH} are used.
 \item[Visualization:] This module is a set of 
@@
 \label{ the-analyze-methods}
+Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
+Nevertheless even if shadowgraphy technic is modified, the algorithm to detect and measure profile during
+welding will still be valid by modifying some parameters.
 \subsubsection{ Image Calibration}
 
-As was shown in section \ref{image-acquisition-setup}, the camera recording a 
+As was shown in section \ref{image_acquisition_setup}, the camera recording a 
 shadow projection of the welding process. The projection is 
@@
  (shadowgraphy) the images are already segmented between
-light and shadow zones (see figures \ref{photo-macro-drop-original});
+light and shadow zones (see figures \ref{photo-macro-drop-patron});
  where the shadow zones are the projection of the macro drop and droplet.
@@
 
-Then, a  adaptive threshold can be used to enhance the difference
+Then, an  adaptive threshold can be used to enhance the difference
 between shadow elements and light zones. To the adaptive threshold it is important 
@@
 \label{edge_extraction}
-Despite performance achieve by the image treatment, Canny filter
- generate many edges, or cords, in the image. These cord are composed
+\textbf{Macrodrop}
+
+Despite performance achieved by the image treatment, Canny filter
+ generates many edges, or cords, in the image. These cords are composed
  by white pixels, interpreted by the algorithms as an individuals points.
@@
 
-To the macro drop profile a user interaction algorithm is responsible
+For the macro drop profile, a user interaction algorithm is responsible
  to extract the continuous cord (white pixels) corresponding
  to the profile into a list. Note  that the macro drop and 
-the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}.
+the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}).
  The substrate shadow projection is always the same if the optical
@@
  first image in the experience series, one extreme  of the cord 
-corresponding to substrate profile (see figures \ref{photo-results-macro-drop}).
+corresponding to substrate profile (see figures \ref{photo-results-macro-drop-t1}).
  Then the algorithm finds all new white pixels inside small neighbor around
@@
 \end{figure}
+
+\textbf{Droplets}
 
@@
 \label{geometrical_analize}
-
+Some of the geometrical analysis computation are directly in the
+library in order to allow low computation time cost.
+\subsubsection{Macrodrop}
+After passing in the preceding, a chained list of points is obtained.
 Now it is possible to determine the geometrical parameters shown 
@@
 angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.
-
-The metal transfert droplet is approximate and close with a combination of $\alpha$-shape and
-graph algorithm. Once the set of segments are extracted a triangulation is created. The triangles 
+\subsubsection{Droplets}
+The metal transfert droplet is approximate and closed with a combination of $\alpha$-shape and
+graph algorithm as outlined in the preceding section.
+For the droplet, the external surface and the speed is searched.
+The speed is computed with the successive computation of the position of the centroid.
+The easiest way to compute it is to goes throught the volume (here the surface) and then
+to build the triangulation. From the triangulation, the triangles 
 are then used to compute the surface and the position of the centroid. It is assumed that there is a kind
-of axisymmetry  and an homogeneous density in the droplet. With the triangles, the principal axis could also be 
+of axisymmetry  and an homogeneous density inside the droplet. With the triangles, the principal axis could also be 
 computed.
@@
 then feed the macrodrop. The macrodrop grows with a geometry that depends on the effects of gravity,
-surface tension, heat transfert,...
+surface tension, heat transfert,etc ...
 
@@
 property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
-its equilibrium.
+its equilibrium. The gas will probably also modify the energy transfert in the arc.
 % It has to be kept in mind that modification of shielding composition will also modify
@@
 regime of the plasma in the pulse. It is better to select images at the end of the period when the macrodrop is
-stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
-The treatment of each image lasts around 5ms.
+almost stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
+The treatment of each image lasts around 5ms. All the images was correctly treated by the algorithm and there is no loss
+of profile detection.
+
 \subsubsection{Basis and angle evolution} 
-Some profile detection are shown on figure \ref{fig::photo-results-macro-drop} on the macrodrop.
-The shape is shown on figure \ref{fig::photo-results-macro-drop}.
+Some profile detections are shown on figure \ref{fig::photo-results-macro-drop-t1,fig::photo-results-macro-drop-t4} on the macrodrop.
+ The developped algorithm manage to detect profile under the arc.
+ To isolate only macrodrop profile, a thershold relative to the base material is used to extract the macrodrop profile.
+The result is shown on figure \ref{fig::profile_extract}. Then, basis and angle of the profile can be computed
+all along  the process.
 
- The developped algorithm manage to detect profile under the arc.
- To isolate only 
-macrodrop profile, a thershold relative to the base material is used to extract the macrodrop profile.
-The result is shown on figure \ref{fig:profile_extract}. Then, basis and angle of the profile can be computed
-all along  the process.
 \begin{figure}[h!]
@@
 \end{figure}
+
 First, the evolution of the basis is extracted on figure \ref{fig::basis} by finding 
@@
 \caption{Macrodrop growth (basis) in function of welding time}
-\label{fig::macro_drop}
+\label{fig::basis}
 \end{figure}
@@
 
-Another important geometrical entity is the angle of the macrodrop surface on the substrate.
+The other geometrical entity is the angle of the macrodrop surface on the substrate.
  To approximate it, a simple linear regression is
@@
 for the left angle and the two gases.
+
 \begin{figure}[h!]
@@
 weld pool. These perturbations create oscillations of the macrodrop and on the free surface.
- These phenomenon induce also oscillations near the triple joint.
+ These phenomenon induce then oscillations near the triple joint.
 
@@
 The shape of the macrodrop is an important information for
-the local and global equilibrium of the interface. 
+the equilibrium of the interface. 
 For example, the macrodrop made with  pure Argon grows by step denoting an interesting instability 
@@
 Nevertheless, the evolution of the basis and the  shape 
-(figure \ref{fig::comp_gazs}) for the two gases are almost the same (figure \ref{fig::macrodrop}).
+(figure \ref{fig::basis}) for the two gases are almost the same (figure \ref{fig::comp_gazs}).
  This means that at first order the two evolutions
@@
 
+The errors of the detection with the algorithm are hard to estimate due to the noisy environment. It is hard
+to appreciate with the eye the exact location of the macrodrop profile.
+
 \begin{figure}[h!]
@@
 \caption{Macrodrop shape at 2s for the two gases}
-\label{fig::comp_angles}
+\label{fig::comp_gazs}
 \end{figure}
@@
 (surface computation and position of the center of mass), within the python interpreter.
+There is around  10 per cent bad image treatment  due to to some noise induced by welding. For these
+images, it was almost impossible to detect any profile.
 
@@
 \includegraphics[width=7cm,angle=90]{images/FreeFlight.pdf}
-\caption{One droplet at two different times during the free flight}
+\caption{One droplet at two different times during the free flight in a same pulse}
 \label{fig::droplets}
@@
 \end{figure}
+
 The motions of the center of mass are almost linear and repetitive for the different transferts.
@@
 The position of the center of mass of the droplet relative to the vertical axis shows that the 
-droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse
-and the free flight of the droplet last 6ms.
+droplet has a constant speed. The speed is estimated between 350mm/s to 500mm/s depending on the pulse
+and the free flight of the droplet lasts around  3ms.
 
@@
 \section{ Conclusions}
+The aggregation of different libraries to identify profiles during noisy environment of welding process
+was successfully applied in static PGMAW. The different algorithms developped allows to detect PGMAW weld pool
+as well as metal transfert automatically. These could be very helpful the investigation of dynamic behaviour
+of the weld pool or for the real time monitoring of the transfert.
 
-%\bibliography{paper_bain}
+From the measurement point of the view, the
+coupling between image treatment, graph theory and computational
+ geometry to identify profile during image treatment
+gives excellent results. 
+% A revoir 
+This strategy enters the multiply and conqueer concepts
+to find the right tool when necessary.
+ The different algorithm are robust. The complex algorithm which work on droplet
+has a non detection of profile of around 10 per cent.
+The quality of the detection is also proven all along the result section. 
+The quick treatment of images let nice perspectives for analysing transient phenomenon in welding 
+ that is one of the major challenge for quality enhancement.
+
+The algorithm for droplet detection can be directly used with same optical settings for real 
+process when there is a relative motion between the wire and weld pool. In this case, the macrodrop
+is useless but could be used to appreciate the back arc profile of the weld pool.
+
+\section{References}
+\bibliography{paper_bain_drop}
 
@@
 % \cite{GEOMETRICAL}
+% \cite{white}
 %\end{thebibliography}

### 2011-02-23 examples/laser_weld_pool/visu.py

@@ -1,0 +1,23 @@
+from pylab import *
+
+for i in arange(1,6):
+    base='laser_prototypage_wep_curveCgal_'
+    try:
+        X=loadtxt(base+str(i)+'.txt')
+        loaded= True
+    except:
+        loaded = False
+    im=imread('../example_laser_prototypage_'+str(i)+'.png')
+    figure(i)
+    imshow(im)
+    print im.shape
+    hold('on')
+    if (loaded):
+        for x in X:
+            plot(x[::2],x[1::2],linewidth=2,color='red')
+    #plot(X[:,0],X[:,1],color='red',linewidth=2)
+
+   
+   
+
+show()

### 2011-02-23 include/erCv/erCvExtract.hpp

@@ -352,9 +352,9 @@ void erExtractCurveMacroDrop( Container &pts, IplImage* simag, CvRect recROI, er
     }
   pts.clear();
   
-  std::pair< CvPoint, int> cercle( cerc->centro, cerc->radio);
-  CvPoint p_cercleDepart, p_polyvalent;
-  std::vector< int> ptsDmin, ptsY0;
+  std::pair< CvPoint, int>    cercle( cerc->centro, cerc->radio);
+  CvPoint                     p_cercleDepart, p_polyvalent;
+  std::vector< int>           ptsDmin, ptsY0;
   std::vector< int>::iterator iterDmin;
   bool Dmin = false;
   int a = 0, b = 0, c = 0;
@@ -362,8 +362,10 @@ void erExtractCurveMacroDrop( Container &pts, IplImage* simag, CvRect recROI, er
   for( iterV_cercleDepart = iterMap->second.begin(); iterV_cercleDepart != iterMap->second.end(); iterV_cercleDepart++)
     {
       a = abs( iterV_cercleDepart->y - cercle.first.y);
+
       if( a <= cercle.second)
 	{
+	 
 	  if( a < b || Dmin==false)
 	    {
 	      c = iterV_cercleDepart->y;
@@ -385,6 +387,7 @@ void erExtractCurveMacroDrop( Container &pts, IplImage* simag, CvRect recROI, er
       std::ofstream file( nameGoodImagesFile( INFOFILE), std::ios_base::app );
       file << file_name << std::endl; // A proscrire
       file << std::endl;
+      std::cout << "On ne trouve pas de point de depart" << std::endl;
       pts.clear();
       return; 
     }
@@ -408,6 +411,7 @@ void erExtractCurveMacroDrop( Container &pts, IplImage* simag, CvRect recROI, er
 	  file << file_name << std::endl;
 	  file << std::endl;
 	  pts.clear();
+	  std::cout << "On sort parceque les points sorte de la zone" << std::endl;
 	  return;
 	}
       iterV_polyvalent = erFindCvPoint( iterMap->second.begin(), iterMap->second.end(), cvPoint( iterMap->first, cpt.y));
@@ -461,6 +465,7 @@ void erExtractCurveMacroDrop( Container &pts, IplImage* simag, CvRect recROI, er
 			      file << file_name << std::endl;
 			      file << std::endl;
 			      pts.clear();
+			      std::cout << "On sort parcequ'on revient au debut" << std::endl;
[…]

### 2011-02-23 src/erCvAnalysis.cpp

@@ -105,7 +105,7 @@ erMacroDropAnalysis::erMacroDropAnalysis( std::string name, std::string infofile
 bool erMacroDropAnalysis::defineParametersUI( std::string firstImage)
 {
   std::cout <<"-----------------------------------------------\n\n";
-  std::cout <<"\tMagic treatment for metal transfer\n\tBy Edward Romero\n\tNovember 2009\n\tLMGC/UM2/UM5508\n\tANR-TEMMSA\n\n";
+  std::cout <<"\tMagic treatment for macroDrop\n\tBy Edward Romero\n\tNovember 2009\n\tLMGC/UM2/UM5508\n\tANR-TEMMSA\n\n";
   std::cout <<"-----------------------------------------------\n\n";
   
   /* Declaration de variables a utiliser par les fonctions */
@@ -175,16 +175,18 @@ bool erMacroDropAnalysis::doIt(std::string fich)
        erSaveImage( &ea, file_name, nom);
        eb = erConvertToBlackAndWhite( &ea);        
        ec = erDef_ROI( &eb, &rectOI); 
+       //erShowImage("essai",&eb);
        erCvEqualizeHist( &ec, &param_equalizer_histogram);
        erCvSmooth( &ec, &param_smooth1);
        erCvAdaptiveThreshold( &ec, &param_adaptive_threshold);
        erCvSmooth( &ec, &param_smooth2);
        erCvCanny( &ec, &param_canny);
-       //erSaveImage( &ec, file_name, nom);
+       erSaveImage( &ec, file_name, nom);
        IsEqualTo is_equal_255( 255); 
        erExtractCvPoints( cvPts, &ec, is_equal_255, rectOI);
        erExtractCurveMacroDrop( cvPts, &ec, rectOI, &cercToStart, file_name);
        erPrintCvPoint( cvPts, file_name, nom); 
+       
        return true;
 };
 

### 2011-03-24 articles/MIG/paper-drop_v1.tex

@@
 A specific data acquisition setup was done at the lab in order to
-synchronize all kind of signals and images versus time and space \cite{ChapuisThesis}.
+synchronize all kind of signals and images versus time and space \cite{CHAPUIS2}.
 The experimental setup is composed of a welding generator, a XY table, a data acquisition
-system and a high speed camera as shown on figure \ref{schema-montage-experimental-GMAW}.
+system and a high speed camera as shown on figure \ref{fig::schema-montage-experimental-GMAW}.
 In this article only details on image acquisition setup and treatment will be outlined.
@@
 The Gas Metal Arc Welding (GMAW) is set in pulsed mode in order that one droplet 
-is detached by pulsed from the wire. As an indicator, the peak current is measured at 300A and the wire speed
-is around 6m/min. The wire has 1mm diameter.
+is detached by pulsed from the wire. As an indicator, the peak current is measured at $300\ A$ and the wire speed
+is around $6\ m/min$. The wire has $1\ mm$ diameter.
 
@@
  a Phantom V5.0 high speed camera is placed and aligned in
- the optical path (see figure \ref{schema-montage-experimental-GMAW}).
+ the optical path (see figure \ref{fig::schema-montage-experimental-GMAW}).
 
@@
 \begin{center}
-\includegraphics[width=7cm,height=4cm]{images/setup.png}
+\includegraphics[width=7cm,height=4cm]{images/schema-montage-experimental-GMAW.png}
 \caption{{\small Experimental setup to detect macro drop and droplet edges in GMAW process}}
-\label{schema-montage-experimental-GMAW}
+\label{fig::schema-montage-experimental-GMAW}
 \end{center}
@@
 the intensity rate between arc light and halogen lamp have to be reduced. In order to this
-a $650\ \pm 10\ nm$ band pass filter is placed in front the camera lens. 650nm
+a $650\ \pm 10\ nm$ band pass filter is placed in front the camera lens. $650\ nm$
 is around a no emitting wavelength from the arc. Nevertheless, the raw images remain highly 
@@
 
-At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical 
+At figure \ref{fig::schema-macro-drop-droplet-parameters} appears the geometrical 
 elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, 
@@
 \caption{{\small Profile schematics of welding objects in a GMAW process}}
-\label{schema-macro-drop-droplet-parameters}
+\label{fig::schema-macro-drop-droplet-parameters}
 \end{center}
@@
 the physical elements to identify are: the fall time $t_{a}$ and the average 
-speed $U_{a}$ (see figure \ref{schema-macro-drop-droplet-parameters}).
+speed $U_{a}$ (see figure \ref{fig::schema-macro-drop-droplet-parameters}).
 
 \section{Image processing} 
+\label{ image_processing}
 
@@
 \subsection{Image treatment basics}
-\subsubsection{Some definitions}\label{some_definitions}
+\subsubsection{Some definitions}
+\label{some_definitions}
+
 A numerical grey image can be described as 3D surface discretized by a grid mesh
@@
 
-\subsubsection{Filters}\label{filters}
+\subsubsection{Filters}
+\label{filters}
 
@@
 image; this allows the filter a better edges localisation
- (see figure \ref{photo-explication-filter}). 
+ (see figure \ref{fig::photo-explication-filter}). 
 For this reason, Canny filter is widely 
@@
 \subsubsection{Snake and level set}
-\label{snake-and-level-set}
+\label{snake_and_level_set}
 
@@
  object tracking, edge detection and others (see figure 
-\ref{photo-explication-snake}). The central idea behind such an approach
+\ref{fig::photo-explication-snake}). The central idea behind such an approach
  is to evolve a curve towards the lowest potential of a cost function. 
@@
 B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
-\mbox{with} R_{i} \neq \emptyset \\
-\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
+\mbox{with}\ R_{i} \neq \emptyset \\
+\mbox{and}\  R_{i}\bigcap R_{j} = \emptyset\ \forall i, j\ \mbox{with}\ i \neq j\ 
 \label{equation-segmentation}
@@
  the elements and surrounding area have different textures (see figure
- \ref{photo-explication-segmentation}). 
+ \ref{fig::photo-explication-segmentation}). 
 Note that different regions can belong to the same partition,
@@
 \begin{center}    
-\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-patron.png}}
-\subfigure[Canny filter treatment]{\label{photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-filter.png}}\\
-\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-snake.png}}
-\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-segmentation.png}}
+\subfigure[Weld pool image in static GTAW process]{\label{fig::photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-patron.png}}
+\subfigure[Canny filter treatment]{\label{fig::photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-filter.png}}\\
+\subfigure[Snake treatment]{\label{fig::photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-snake.png}}
+\subfigure[Segmentation image by 2 cluster sample comparison]{\label{fig::photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-explication-segmentation.png}}
 \end{center}
 \caption{{\small Samples of different methods technique for image processing}}
-\label{photo-explication}
+\label{fig::photo-explication}
 \end{figure}
@@
 \subsection{Image treatment library}
-\label{image-treatment-library-ercv}
+\label{image_treatment_library}
 
@@
 \caption{{\small Flow diagram of erCv library composition}}
-\label{schema-erCv}
+\label{fig::schema-erCv}
 \end{center}
@@
 \subsection{ The Analyzing methods}
-\label{ the-analyze-methods}
+\label{ the_analyze_methods}
 Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
@@
 welding will still be valid by modifying some parameters.
+
 \subsubsection{ Image Calibration}
+\label{ image_calibration}
 
@@
 \subsubsection{ Image Treatment}
-\label{ image_treatment}
+\label{image_treatment}
 
@@
  (shadowgraphy) the images are already segmented between
-light and shadow zones (see figures \ref{photo-macro-drop-patron});
+light and shadow zones (see figures \ref{fig::photo-macro-drop-patron});
  where the shadow zones are the projection of the macro drop and droplet.
@@
 To simplify the contrast enhancement, the images are converted from RGB image color 
-to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
+to grey levels image (see figure \ref{fig::photo-macro-drop-grey}). To 
 reduce the grey level noise, a first smooth classical filter 
@@
 the grey values of squares of $7\times 7$ 
-pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
+pixels by they average value (see figure \ref{fig::photo-macro-drop-smoothblur}). 
 In consequence, the homogeneity quality is improved into the light and 
@@
 light interference regions, which are bigger than regions size to
-threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).
+threshold (see figure \ref{fig::photo-macro-drop-adaptivethreshold}).
 
@@
  median value. In consequence contour quality between light and shadows
- regions at the binary image are improved (see figure \ref{photo-macro-drop-smoothmedian}).
+ regions at the binary image are improved (see figure \ref{fig::photo-macro-drop-smoothmedian}).
 
@@
 the principal edges at image. In a binary image, all edges are principal,
-therefore canny detect all edge at the image (see figure \ref{photo-macro-drop-canny}).
+therefore canny detect all edge at the image (see figure \ref{fig::photo-macro-drop-canny}).
 Nevertheless to guarantee a full detection of droplet and 
@@
 \begin{center}    
-\subfigure[Macro drop raw image]{\label{photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
-\subfigure[Macro drop grayness image]{\label{photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-grey.png}}\\
-\subfigure[First smooth filter]{\label{photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothblur.png}}
-\subfigure[Adaptive threshold per regions]{\label{photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-adaptivethreshold.png}}\\
-\subfigure[Median filter]{\label{photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothmedian.png}}
-\subfigure[Canny filter]{\label{photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-canny.png}}\\
+\subfigure[Macro drop raw image]{\label{fig::photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-original.png}}
+\subfigure[Macro drop grayness image]{\label{fig::photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-grey.png}}\\
+\subfigure[First smooth filter]{\label{fig::photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothblur.png}}
+\subfigure[Adaptive threshold per regions]{\label{fig::photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-adaptivethreshold.png}}\\
+\subfigure[Median filter]{\label{fig::photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-smoothmedian.png}}
+\subfigure[Canny filter]{\label{fig::photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-macro-drop-canny.png}}\\
 \end{center}
 \caption{{\small Image treatment step by step of PGMAW process}}
-\label{photo-macro-drop}
+\label{fig::photo-macro-drop}
 \end{figure}
@@
  to the profile into a list. Note  that the macro drop and 
-the substrate have the same continuous profile (see figure \ref{photo-macro-drop-canny}).
+the substrate have the same continuous profile (see figure \ref{fig::photo-macro-drop-canny}).
  The substrate shadow projection is always the same if the optical
@@
  first image in the experience series, one extreme  of the cord 
-corresponding to substrate profile (see figures \ref{photo-results-macro-drop-t1}).
+corresponding to substrate profile (see figures \ref{fig::photo-results-macro-drop-t1}).
  Then the algorithm finds all new white pixels inside small neighbor around
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t1.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t2.png}}\\
-\subfigure[t = ]{\label{photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t3.png}}
-\subfigure[t = ]{\label{photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t4.png}}\\
+\subfigure[t1 ]{\label{fig::photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t1.png}}
+\subfigure[t2 ]{\label{fig::photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t2.png}}\\
+\subfigure[t3 ]{\label{fig::photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t3.png}}
+\subfigure[t4 ]{\label{fig::photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-macro-drop-t4.png}}\\
 \end{center}
@@
 To the droplet edge section, the white points cord defines 
-the surface of the droplet. Note at figure \ref{photo-droplet-canny} that the biggest closer
+the surface of the droplet. Note at figure \ref{fig::photo-droplet-canny} that the biggest closer
  cord correspond to the droplet section. The idea is to build segments around
@@
  internal angles for each triangle, which means  minimal
- length sides to the triangles \cite{GEOMETRICAL}.
+ length sides to the triangles \cite{BERG}.
  Give $\beta$ the cord surrounding the external hull of the Delaunay
@@
  is sufficient to create a segment set around the droplet
- (see figure \ref{photo-droplet-alpha-shape}).
+ (see figure \ref{fig::photo-droplet-alpha-shape}).
 
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-canny.png}}
-\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-alpha-shape.png}}\\
+\subfigure[t = ]{\label{fig::photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-canny.png}}
+\subfigure[t = ]{\label{fig::photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-alpha-shape.png}}\\
 \end{center}
 \caption{{\small Images series of macro drop profiles}}
-\label{photo-results-droplet}
+\label{fig::photo-results-droplet}
 \end{figure}
@@
  The longest closer segment corresponds to the metal transfer drop profile 
-(see figure \ref{photo-results-droplet}).
+(see figure \ref{fig::photo-results-droplet}).
 
@@
 \begin{center}    
-\subfigure[t = ]{\label{photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t1.png}}
-\subfigure[t = ]{\label{photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t2.png}}\\
-\subfigure[t = ]{\label{photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t3.png}}
-\subfigure[t = ]{\label{photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t4.png}}\\
+\subfigure[t1 ]{\label{fig::photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t1.png}}
+\subfigure[t2 ]{\label{fig::photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t2.png}}\\
+\subfigure[t3 ]{\label{fig::photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t3.png}}
+\subfigure[t4 ]{\label{fig::photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-results-droplet-t4.png}}\\
 \end{center}
 \caption{{\small Images series of macro drop profiles}}
-\label{photo-results-droplet}
+\label{fig::photo-results-droplet}
 \end{figure}
@@
 library in order to allow low computation time cost.
+
 \subsubsection{Macrodrop}
+\label{macrodrop}
+
 After passing in the preceding, a chained list of points is obtained.
 Now it is possible to determine the geometrical parameters shown 
-at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
+at figure \ref{fig::schema-macro-drop-droplet-parameters}. To compute the wetting 
 angle measure, linear regressions or least squares (parabolic, ellipse, circle) 
@@
 angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.
+
 \subsubsection{Droplets}
+\label{droplets}
+
 The metal transfert droplet is approximate and closed with a combination of $\alpha$-shape and
@@
 \section{ Results}
+\label{results}
+
 In this part some results, performance and reliability of the library for a set of experiments
@@
 \subsection{ Macro Drop growth investigation}
+\label{macro_drop_growth_investigation}
+
 The investigation of the macro drop growth for the two shielding gas needs the study of two quantities:
@@
 \subsubsection{Basis and angle evolution} 
-Some profile detections are shown on figure \ref{fig::photo-results-macro-drop-t1,fig::photo-results-macro-drop-t4} on the macrodrop.
+\label{basis_and_angle_evolution}
+Some profile detections are shown on figure \ref{fig::photo-results-macro-drop} on the macrodrop.
  The developped algorithm manage to detect profile under the arc.
@@
 \subsubsection{Discussions}
+\label{discussion}
+
 The noise in the measure for the basis could be attributed
@@
 \subsection{ Droplet flight}
+\label{ droplet_flight}
+
 Droplet flight investigation is of interest for weld quality and the metal deposition process.
@@
 \subsubsection{Trajectories and droplet velocities}
+\label{trajectories_and_droplet_velocities}
+
 During one pulse, the droplet are detected. The shape are shown on figure \ref{fig::droplets}.
@@
 \subsubsection{Discussions}
+\label{discussions}
+
 The oscillations of the droplet gives informations on the competition between surface tension and gravity
@@
 \section{ Conclusions}
+\label{conclusions}
+
 The aggregation of different libraries to identify profiles during noisy environment of welding process

### 2011-03-24 src/erCvAnalysis.cpp

@@ -550,32 +550,32 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
 
   erPrintCgalPoint( cgalPts2, file_name, nom);
 
- //  double area;
+  double area;
 
-//   if(output_convex_polygon)
-//   {
-//     std::list<CgalPoint> polygon = erGeometryExtractConvexPolygon(bgraphSeg.begin(),bgraphSeg.end());
+  if(output_convex_polygon)
+  {
+    std::list<CgalPoint> polygon = erGeometryExtractConvexPolygon(bgraphSeg.begin(),bgraphSeg.end());
 
-//       std::string output_nam = (dir_analysis+"/"+name+"_wep_poly");
-//       char* name = const_cast< char*>( output_nam.c_str());
-//       erPrintCgalPoint(polygon,file_name,name);
-//       Polygon_2 poly(polygon.begin(),polygon.end());
-//       area = poly.area();
-//     };
-//   if(output_geometry_characteristics && bgraphSeg.size() > 6)
-//     {
-//       std::list<CgalTrian> triangs=erGeometryExtractTriangles(bgraphSeg.begin(),bgraphSeg.end());
-//       if(!not output_convex_polygon)
-// 	{
-// 	 area   = getArea(triangs.begin(),triangs.end());
-// 	};
-//       CgalLine  line;
-//       CgalPoint pt;
-//       CgalFTrai fit = linear_least_squares_fitting_2(triangs.begin(),triangs.end(),line,pt,CGAL::Dimension_tag<2>());	
-//       std::ofstream ot(output_geometry_file.c_str(),std::ios_base::app);
-//       CgalVect vect=line.to_vector();
-//       ot << std::setprecision(10) << fich << "\t" << pt.x() << "\t" << pt.y() << "\t" << area << "\t" << vect.x() << "\t" << vect.y() <<"\t" << fit << std::endl;    
-//     };
+      std::string output_nam = (dir_analysis+"/"+name+"_wep_poly");
+      char* name = const_cast< char*>( output_nam.c_str());
+      erPrintCgalPoint(polygon,file_name,name);
+      Polygon_2 poly(polygon.begin(),polygon.end());
+      area = poly.area();
+    };
+  if(output_geometry_characteristics && bgraphSeg.size() > 6)
+    {
+      std::list<CgalTrian> triangs=erGeometryExtractTriangles(bgraphSeg.begin(),bgraphSeg.end());
[…]

### 2011-03-25 articles/MIG/paper-drop_v1.tex

@@
 
-\section{Image processing} 
-\label{ image_processing}
+\section{Image processing tools} 
+\label{ image_processing_tools}
 
@@
 
-A multipurpose image processing library was developed 
+A multipurpose image processing library has been developed 
 and currently use at the laboratory, in order to analyze welding process objects.
@@
 
-\subsection{ The Analyzing methods}
+\section{ The Analyzing methods}
 \label{ the_analyze_methods}
@@
 
-\subsubsection{ Image Calibration}
+\subsection{ Image Calibration}
 \label{ image_calibration}
@@
 
-\subsubsection{ Image Treatment}
+\subsection{ Image Treatment}
 \label{image_treatment}
@@
 to threshold application is $23\times 23\ pixels$. The threshold criteria 
-choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
-or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
+choose is binary: $grey\_level\_threshold(x,y) = max\_value$ if $grey\_level\_origin(x,y) >  threshold(x,y)$
+or $grey\_level\_threshold(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
 to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
- $max(value)$ is the grey level value choose to identify the pixels above
-threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
- before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
+ $max\_value$ is the grey level value choose to identify the pixels above
+threshold parameter, $grey\_level\_origin(x,y)$ is the grey level value of pixel
+ before threshold and $grey\_level\_threshold(x,y)$ is the pixel grey level after threshold.
 $threshold(x,y)$ is obtain by subtraction between the average grey level of region
@@
 \label{edge_extraction}
-\textbf{Macrodrop}
+\begin{description}
+\item[ Macrodrop]
 
@@
 
-\textbf{Droplets}
-
+\item[ Droplet]
 To the droplet edge section, the white points cord defines 
@@
 \end{figure}
+
+\end{description}
 

### 2011-03-25 articles/MIG/paper-drop_v1.tex

@@
 
-\section{ The Analyzing methods}
-\label{ the_analyze_methods}
+\section{ Applying image processing}
+\label{ applying_image_processing}
 Image treatment and implemented algorithms are dependent of the optical setup and recording of images.
@@
 
-\subsubsection{Edge extraction}
+\subsection{Edge extraction}
 \label{edge_extraction}
-\begin{description}
-\item[ Macrodrop]
+
+\subsubsection{Macrodrop}
 
@@
 
-\item[ Droplet]
+\subsubsection{Droplet}
+
 To the droplet edge section, the white points cord defines 
@@
 \end{figure}
-
-\end{description}
 

### 2011-04-08 src/Gui/erCvFiltersUser.cpp

@@ -270,7 +270,7 @@ void erCvThresholdUser( IplImage* simg, erThresP* parm, bool with_trackbar)
 	  std::cin >> threshold[0];
 	  //  threshold[0] = 230;
 	  std::cout << std::endl;
-	  if( threstype == 1 or threstype == 2)
+	  if( threstype == 1 || threstype == 2)
 	    {
 	      std::cout << "Put the value of Second Threshold fonction (to 8-bit image = 255): ";
 	      std::cin >> threshold[1];
@@ -281,7 +281,7 @@ void erCvThresholdUser( IplImage* simg, erThresP* parm, bool with_trackbar)
       else
 	{
 	  itrak[0] = cvCreateTrackbar( "max_threshold", "Threshold_trackbar", &threshold[0], maxt, NULL);
-	  if( threstype == 1 or threstype == 2)
+	  if( threstype == 1 || threstype == 2)
 	    {
 	      itrak[1] = cvCreateTrackbar( "threshold", "Threshold_trackbar", &threshold[1], maxt, NULL);
 	    }
@@ -309,7 +309,7 @@ void erCvThresholdUser( IplImage* simg, erThresP* parm, bool with_trackbar)
   //parm->trh1 = cvGetTrackbarPos( "max_threshold", "Threshold_trackbar");
   //parm->trh2 = cvGetTrackbarPos( "threshold", "Threshold_trackbar");
   parm->trh1 = threshold[0];
-  if( threstype == 1 or threstype == 2)
+  if( threstype == 1 || threstype == 2)
     {
       parm->trh2 = threshold[1];
     }
@@ -319,7 +319,7 @@ void erCvThresholdUser( IplImage* simg, erThresP* parm, bool with_trackbar)
   file << "***********Filter fonction THRESHOLD***********\n";
   file << "Threshold :------------ " << parm->trh1 << std::endl;
   std::cout << "trh2: " << parm->trh1 << std::endl;
-  if( threstype == 1 or threstype == 2)
+  if( threstype == 1 || threstype == 2)
     {
       file << "SubThreshold:---------- " << parm->trh2 << std::endl;
       std::cout << "trh2: " << parm->trh2 << std::endl;

### 2011-04-08 articles/TIG/doc_broullion/latex/paper_bain.tex

\title{ Weld pool detection and geometrical analysis during GTAW process by image processing library}

\section{Introduction}

Gas Tungsten Arc Welding (GTAW), which uses a non-consumable tungsten electrode and an inert gas for arc shielding, is an extremely important arc welding process. It is commonly used for welding hard-to-weld metals such as stainless steel \cite{JUANG} and therefore widely use in modern and basic industries. To achieve good weld quality in GTAW process, several weldment characteristics or objects should be sensed and controlled \cite{DOUMANIDIS}. It is shown that the geometry of the weld pool, in particular his shape and size, contains sufficient information about weld penetration to evaluate the weld quality \cite{ZHANG}. Furthermore it has been shown that the welding arc parameters to simulation and weld quality are directly relate to the weld pool geometry \cite{LU}.
Basically the weld pool object is the key in quality control to automated welding process \cite{KOVACEVIC}. 
According to this a better comprehension of weld pool behavior presents a GTAW process, could help to improve numerical simulations and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.

There have been many studies on visual sensing techniques for observing weld pool image \cite{BAE}. Optical sensors like high speed CCD cameras and lighting systems have been widely use in GTAW process to realize image acquisition \cite{GUANGJUN}, control process \cite{BAE} and parametric studies \cite{BALSAMO}. Then image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}. Nevertheless the strong interference from the arc lightning required more than standard image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. Previous work has shown that is possible to perform geometrical analysis in weld pools \cite{WU1}. Parameters such as weld pool contour and surface has been detected and measure using different and specifics processing images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}. However, to date, effectively automatic images processing of GTAW process has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.

To perform geometrical analysis in weld pool; a multipurpose C++ based library (erCv) was developed by the Weld/Assembly group of LMGC laboratory. These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical analysis, graph theory applications and image visualization.

In a first step, and despite the different static and dynamic weld conditions, as well as different current regime, a reliable 2D profiles and geometrical parameters from weld pool, has been obtained using the mentioned library. Using this, a dimension and dimensionless analysis has been performed into a static and dynamic GTAW process. The intention is contribute to simplify futures numerical models of weld pool-arc interaction and quality process.

\section{Problems description}
\label{problem_description}

Indirectly, the weld pool geometry could be detected by different methods such pool oscillations \cite{RENWICK}, ultrasonic sensing \cite{CARLSON}, radiography \cite{ROKHLIN}. However to obtain more precise measurements, direct acquisition methods, as vision based techniques, should be use \cite{KOVACEVIC}.     Bradstreet was the first researcher to experimentally study the bead hump formation \cite{CHO}. Humping was defined as the series of undulations of the weld bead. Further studies as computer simulation made by CHO et al. \cite{CHO} shown a relation between the droplet momentum deposition and the hump size. Same relations has been found between metal transfer process and welding quality \cite{}

Then the shape and size kinetic analysis of macro drop and droplets could help to better understand and enhance the PGMAW process. To monitoring the shape and size of these welding objects, to a first step, a 2D approach would be sufficient. Therefore a shadowgraphy technique, or back lighting, is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is one of the only way to access these quantities. Due to the arc light interference and the relatively high speed of wire feed process, a high speed camera and an effective image processing algorithms are required \cite{WANG}. The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ per second \cite{WANG}. Therefore the algorithms have to be able to extract the geometrical information (area, size and others) from the macro drop and droplets, from a huge amount of data. In addition, the voltage and current signals are directly related with the droplet formation at the wire \cite{BALSAMO}. Good synchronizations methods have to be applied between shadowgraphies frames and electrical signals.

\section{Image processing background}
\label{image_processing_background}

Some definitions and brief description of generals principles used in image processing are required to better understand how is work the algorithms utilized by the erCv library.

\subsection{Some definitions}
\label{some_definitions}

A numerical grey image can be describe as 3D surface discretized by a grid mesh in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis, the grey level.

A strong relief change or high gradient greyness values at the image are perceive by human eyes as light changes, and can be interpreted as objects edges. 
Sometimes, a regular relief patrons or regular greyness variation can be distinguish. The human eyes can perceive these patrons as texture and interpret the space between different textures zones as edges.
There exist a large spectrum of algorithms to image treatment, in particular to edges detect. Most of them can be classified by the way that his operate above the image pixels and grey level.

\subsection{Filters}
\label{filters}

The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  $f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others. The impulse filters such Canny are widely use to edge detection \cite{COCQUEREZ}. These filter have an impulse response to most important greyness gradient in the image; this allows the filter a better edges localisation (see figure \ref{photo-explication-filter}). For this reason, Canny filter is widely use at erCv library to detect the welding elements edges. However, it is sensible to noise or secondary greyness gradients in the image and, in consequence, it have some difficulties to define closer surface.

\subsection{Snake and level set}
\label{snake-and-level-set}

Curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure \ref{photo-explication-snake}). The central idea behind such an approach is to evolve a curve towards the lowest potential of a cost function. However at each stage of curve evolution, each curve point potential has to be computed. A lot of point (better curve resolution) take a lot computing time, and therefore are not yet apply to real time detection or relatively speed automatic image processing. For this reason snake algorithms are not used at erCv.

\begin{Segmentation}
\label{segmentation}

Let $B$ an image and let $R_{i}$ a region of $B$ such:

\begin{equation}
B = \bigcup_{i}R_{i}\  
\forall i  R_{i} \neq \emptyset\ 
\forall i, j avec i \neq j\ R_{i}\bigcap R_{j} = \emptyset 
\label{equation-segmentation}
\end{equation}

A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. Each region is a connected set of pixels with common properties (intensity, texture,...) \cite{COCQUEREZ}. The partition is generated by operations or comparisons methods between regions. Generally, this treatment offers a good detection edges if the elements and surrounding area have different textures (see figure \ref{photo-explication-segmentation}). 
Note that different regions can belong to the same partition and not be placed together, therefore the surface is not always connected and, in consequence, the edges of the interest regions are not always closed.

\begin{figure}[h!]
\begin{center}    
\subfigure[Weld pool image in static GTAW process]{\label{photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-patron.png}}
\subfigure[Canny filter treatment]{\label{photo-explication-filters}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-filters.png}}\\
\subfigure[Snake treatment]{\label{photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-snake.png}}
\subfigure[Segmentation image by 2 cluster sample comparison]{\label{photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{photo-explication-segmentation.png}}
\end{center}
\caption{{\small Samples of different methods technique for image processing}}
\label{photo-explication}
\end{figure}

\section{Image treatment library (erCv)}
\label{image-treatment-library-ercv}

As mentioned, a multipurpose image processing library was developed and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different welding objects such: Macro drop, droplets (for GMAW process) and weld pool (for GTAW process).
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable and portable library able to perform real time contour detection. erCv is build in Phyton scripts link to C++, making it relatively convivial to use.
erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD camera are not calibrated and present light inhomogeneities and noise. In order to obtain the real shape and size of weld elements, this module include calibrations algorithms. To detect the welding objects contours it is necessary to improve the weld element image. This module has the pre-processing treatments to noise reduction and image enhancement. Then to start the edges detection process, this module includes processing algorithms as segmentations by samples comparators, watershed transformation, filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module has to end the edge detection process, completing and in some cases extrapolating the weld elements edge. It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes. This module uses a full geometry algorithm library, which include different algorithms such as triangulations and mesh generation, alpha shape and convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the welding object edge from the image; this required some criteria such as continuity, length or closer condition.  This module use graph algorithms to convert edges pixels points into connected segments, and therefore, identify and select the welding element edge using the criteria. This module is compose by connect segments, estimates minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of functions use to execute, show and/or register the different steps at the image process.
\end{description}

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
\caption{{\small Flow diagram of erCv library composition}}
\label{schema-erCv}
\end{center}
\end{figure}

\section{Experimental Setup}
\label{experimental_setup}

\subsection{Multi-physics platform}
\label{multi_physics_platform}

The objective is to perform geometrical analysis of weld pool in a GTAW process. Notes that geometrical analysis refers to surface value and contour detection of weld pool in static and dynamic GTAW process. The methods choose is the image treatment of recorded image of GTAW static and dynamic process by a high speed CCD camera.

To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; therefore an accurate, reliable and synchronizes systems are requires due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).

A platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}). The platform was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-platform.png}
\caption{{\small Experimental platform and specific device}}
\label{schema-platform}
\end{center}
\end{figure}

To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).

\subsection{ Image acquisition setup}
\label{ image_acquisition_setup}

Using a similar technique employed by Kovacevic et al. \cite{KOVACEVIC}, the GTAW static process has been recorded by the specular reflection optical method. A $650\ nm$ laser diode has been used to light the weld process from an estimate angle of $35\ degree$. The laser beam width ($ $) was sufficient to guarantee a homogeneous illumination of the welding process. The laser projects an image by reflection of welding objects (weld pool and surrounding metal substrate) to the other side of the welding place. At this place and aligned with the optical path of reflected laser beam, a Phantom V5.0 high speed camera has been placed in order to record the process images (see figure \ref{schema-montage-experimental-GTAW}).

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-montage-experimental-GMAW.png}
\caption{{\small Experimental setup to detect weld pool edges in GTAW process}}
\label{schema-montage-experimental-GTAW}
\end{center}
\end{figure}

To enhance the image contrast of the weld objects inside the electric discharge, the intensity rate between arc light and laser diode have to be reduce. In order to this a $650\ \pm 10\ nm$ band pass filter, which correspond to the laser diode wavelength, has been placed in front of the camera lens to attenuate the arc light. Nevertheless, the raw images remain highly noisy by the arc light.

\subsection{ Welding condition}
\label{ welding_conditions}

Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. The target is a steel disk of $10\ mm$ of thickness and ER70S steel welding wire.
The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and percentage of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon). Welding parameters values are summarize in tables \ref{table-parameters-static} to static and \ref{table-parameters-change} to variables parameters.

\begin{table}
\begin{center}
\begin{tabular}{|cc|}
\hline
Welding wire type & ER70S \\ 
Wire diameter ($mm$) or $drw$ & 1 \\  
Contact tip to work distance ($mm$) & 20 \\
Shielding gaz flowrate ($l/min$) & 18 \\ \hline
\end{tabular}
\caption{{\small Determined constant welding parameters used in experiments}}
\label{table-parameters-static}
\end{center}
\end{table}

\begin{table}
begin{center}
\begin{tabular}{|cc|}
\hline
Welding wire type & ER70S \\ 
Wire diameter ($mm$) or $drw$ & 1 \\  
Contact tip to work distance ($mm$) & 20 \\
Shielding gaz flowrate ($l/min$) & 18 \\ \hline
\end{tabular}
\caption{{\small Variable welding parameters used in experiments}}
\label{table-parameters-change}
\end{center}
\end{table}

Welding current and arc voltage are recorded at $30\ kHz$ sampling rate. The images are recorded at $4000$ frames per seconds, which is enough to measure macro drop radius and apparent liquid-solid contact angle histories. The images and electrical signals are synchronize, thanks to the automatically approach made in the multi physics platform.

Measurements are made using the erCv library.

\section{ System definitions}
\label{system_definitions}
\subsection{ Weld Pool}
\label{ weld_pool}

The purpose is to study the evolution of weld pool object in a GTAW process. Therefore it is necessary to detect the contour, without predetermined shape, of the weld pool and calculate his surface area.

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
\caption{{\small Overview schematics of welding objects in a GTAW process}
\label{schema-macro-drop-droplet-parameters}
\end{center}
\end{figure}

At figure \ref{figure_1} appears the geometrical elements to be study at the weld pool: the weld pool contour and surface area.

\section{ The Analyze methods}
\label{ the-analyze-methods}

\subsection{ Image Calibration}
\label{ image_calibration}

As was shown in section \ref{image-acquisition-setup}, the camera recording a specular reflection of the welding process. Therefore the image of the welding objects is not orthogonal to the optical axes of the camera. In order to correct the image perspective, a control image (small chessboard image with known real dimensions) has been recorded at the weld pool place. A transformation matrix has been build between the control image (chessboard recorded image) and the original digital image. To calibrate the image dimension (in pixels) to the real objects dimension (in millimeters), a conversion scale has been applied with the real dimensions of chessboard control image $conv = 1\ mm/ 20\ pixels$.

\begin{figure}[h!]
\begin{center}    
\subfigure[Chessboard control image]{\label{photo-calibration-cuadro-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-patron.png}}
\subfigure[Chessboard original digital image]{\label{photo-calibration-cuadro-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-origin.png}}\\
\subfigure[Raw recorded image]{\label{photo-calibration-image-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-origin.png}}
\subfigure[Perspective corrected image]{\label{photo-calibration-image-corrected}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-corrected.png}}
\end{center}
\caption{{\small Perspective image correction samples}}
\label{photo-calibration}
\end{figure}

\subsection{ Image Treatment}
\label{ image_treatment}

The idea is to recognize the weld pool from the raw image and therefore calculate his 2D surface area. This requires the identification of a well define weld pool contour. Several approaches could be uses to obtain the weld pool contour, such as edge detection techniques \cite{WU2}, Hough transforms \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}. Nevertheless the most common approach is the image segmentation \cite{WANG}. That means to split in two or more fields the image.  The object, in this case the weld pool, would be colored in one color and the rest of the image in other color \cite{COCQUEREZ}. Thanks to the optical method acquisition (specular reflection) a natural way to segment the images, could be separate its between the roughness (non homogeneous lighting colored zone) and non roughness zone (see figures \ref{photo-macro-drop-original}). Into the lighting zone at the images, the mirror like surface of the weld pool reflect a uniform dark surface to the camera while the solid metal surface reflect a diffuse colored surface \cite{WU2}. This particularity in the color and in the light distribution (roughness) at the image could be interpreted as different textures zones \cite{MATERKA}, in the same the way as the eyes recognize the texture in the object surface and$/$or images.
The texture analysis method to perform image segmentation is an image processing technique widely uses in biomedicine, satellite recognition, industrial quality control and others fields requiring image processing. There exist different approaches to texture analysis, each one using their own image analysis methods:
\begin{description}
\item[Structural] Represent texture by well defined primitives, and a hierarchy of spatial arrangements of those primitives.
\item[Statistical] Represent the texture indirectly by the non-deterministic properties that govern the distributions and relationship between the grey levels of an images.
\item[Model based] Using fractal and stochastic models, attempt to interpret an image texture by use of, respectively, generative image model and stochastic model.
\item[Transform methods] Using Fourier and wavelet transforms, represent an image in a space whose co-ordinate system has an interpretation.
\end{description}

. Most of them required complex image analysis using hierarchy decomposition (structural), fractal or stochastic models (model based) and Fourier or wavelet transforms (transforms methods) 
 Di BLA BLA use this  has been thedescribe  where the shadows zones are the projection of the macro drop and droplet.

### 2011-05-18 articles/TIG/doc_broullion/latex/paper_bain2.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\usepackage{graphicx}
\usepackage[sf]{subfigure}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

\begin{document}
\bibliographystyle{unsrt}

\title[Image Processing  for edge detection during GTAW]
{Image Processing and geometrical analysis for edge detection during Gaz Tugnsten Metal Arc Welding}

\author{E Romero, J Chapuis, C Bordreuil, F Souli\'e, G Fras}

\address{Laboratoire de M\'ecanique et G\'enie Civil,
CC048, Place Eug\`ene Bataillon, Universit\'e Montpellier 2,
34095 Montpellier, France}
\ead{cyril.bordreuil@univ-montp2.fr}

\begin{abstract}
The paper describes some new image treatment algorithm used to 
detect profiles during arc welding process. The new algorithm 
is an aggregation of some available algorithm of image treatment,
computational geometry and graph theory. The algorithm allows to extract precise
geometrical entities as closed or open profiles that could be used for monitoring
of welding process. The algorithm  is shown to be really efficient
and could be used for real time monitoring.
\end{abstract}

%Uncomment for PACS numbers title message
%\pacs{00.00, 20.00, 42.10}
% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
%\vspace{2pc}
\noindent{\it Keywords}: Arc welding, Image treatment, weld pool,  geometrical analysis, Monitoring, 
% Uncomment for Submitted to journal title message
\submitto{\MST}
% Comment out if separate title page not required
\maketitle

\section{Introduction}

Gas Tungsten Arc Welding (GTAW), which uses a non-consumable tungsten electrode and an inert gas for arc shielding, is an extremely important arc welding process. It is commonly used for welding hard-to-weld metals such as stainless steel \cite{JUANG} and widely use in modern and basic industries. To achieve good weld quality in GTAW process, several weldment characteristics or objects should be sensed and controlled \cite{DOUMANIDIS}. It is shown that the geometry of the weld pool, in particular his shape and size, contains sufficient information about weld penetration to evaluate the weld quality \cite{ZHANG}. Furthermore it has been shown that the welding arc parameters to simulation and weld quality are directly relate to the weld pool geometry \cite{LU}.
Basically the weld pool object is the key in quality control to automated welding process \cite{KOVACEVIC}. 
According to this a better comprehension of weld pool behavior presents a GTAW process, could help to improve numerical simulations and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.

Many studies have been realized using visual sensing techniques to observe weld pool image \cite{BAE}. Optical sensors like high speed CCD cameras and lighting systems have been widely use in GTAW process to realize image acquisition \cite{GUANGJUN}, control process \cite{BAE} and parametric studies \cite{BALSAMO}. However, the extremely noisy environment require image processing techniques to extract useful information from visual scenes, which play a critical role in the weld pool analysis \cite{WANG}.
Nevertheless the strong interference from the arc lightning required more than standard image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}.

Previous work has shown that is possible to perform geometrical analysis in weld pools \cite{WU1}. Parameters such as weld pool contour and surface has been detected and measure using different and specifics processing images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}. However, to date, effectively automatic images processing of GTAW process has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.

To perform geometrical analysis in weld pool; a multipurpose C++ based library (erCv) has been developed by the Weld/Assembly group of LMGC laboratory. These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical analysis, graph theory applications and image visualization.

In a first step, and despite the different static and dynamic weld conditions, as well as different current regime, a reliable 2D profiles and geometrical parameters from weld pool, has been obtained using the mentioned library. Using this, a dimension and dimensionless analysis has been performed into a static and dynamic GTAW process. The intention is contribute to simplify futures numerical models of weld pool-arc interaction and quality process.

\section{Experimental Setup}
\label{experimental_setup}

\subsection{Multi-physics platform}
\label{multi_physics_platform}

The objective is to perform geometrical analysis of weld pool in a GTAW process. Notes that geometrical analysis refers to surface value and contour detection of weld pool in static and dynamic GTAW process. Techniques as pool oscillations, ultrasonic sensing or infrared sensing could indirectly detect these geometric objects. However to obtain more precise measurements direct methods as vision based techniques assisted with image processing may be more promising \cite{KOVACEVIC}. According to this, the methods choose has been the direct image acquisition by a high speed CCD camera combined with an adequate image processing technique.

To perform the geometrical analyses of weld pool, it has been necessary correlate the weld pool images with the welding parameters. Then different signals of control and measurements have had to be synchronized and recorded \cite{CHAPUIS}. This require accurate, reliable and synchronizes systems due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).

In order to this, a platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}). The platform was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go per test). This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.

%\begin{figure}
%\begin{center}
%\includegraphics[width=7cm,height=4cm]{schema-platform.png}
%\caption{{\small Experimental platform and specific device}}
%\label{schema-platform}
%\end{center}
%\end{figure}

To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).

\subsection{ Image acquisition setup}
\label{image_acquisition_setup}

Using a similar technique employed by Kovacevic et al. \cite{KOVACEVIC}, the GTAW static process has been recorded by the specular reflection optical method. A $650\ nm$ laser diode has been used to light the weld process from an estimate angle of $35\ degree$. The laser beam width ($ $) has been enough to guarantee a homogeneous illumination of the welding process. The laser projected an image of welding objects (weld pool and surrounding metal substrate) by reflection to the other side of the welding place. At this place and aligned with the optical path of reflected laser beam, a Phantom V5.0 high speed camera has been placed in order to record the images of the process (see figure \ref{schema-montage-experimental-GTAW}).

%\begin{figure}
%\begin{center}
%\includegraphics[width=7cm,height=4cm]{schema-montage-experimental-GMAW.png}
%\caption{{\small Experimental setup to detect weld pool edges in GTAW process}}
%\label{schema-montage-experimental-GTAW}
%\end{center}
%\end{figure}

To enhance the image contrast of the weld objects inside the electric discharge, the intensity rate between arc light and laser diode have to be reduce. In order to this a $650\ \pm 10\ nm$ band pass filter, which correspond to the laser diode wavelength, has been placed in front of the camera lens to attenuate the arc light. Nevertheless, the raw images remain highly noisy due to the arc light intensity and disturbed by the non-homogeneous reflections over the dynamic and non-flat weld pool surface.

% ON CONTINUE ICI
\subsection{ Welding condition}
\label{ welding_conditions}

\subsection{Weld pool geometrical parameters}
\label{weld-pool-geometrical-parameters}

The purpose is to study the evolution of weld pool object surface and shape in a GTAW process. Therefore it is necessary to detect the contour of the weld pool and calculate the surface area enclose by this.

%\begin{figure}
%\begin{center}
%\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
%\caption{{\small Overview schematics of welding objects in a GTAW process}
%\label{schema-macro-drop-droplet-parameters}
%\end{center}
%\end{figure}

At figure \ref{figure_1} appears the geometrical elements to be study at the weld pool: the weld pool contour and surface area.

\section{Image processing tools} 
\label{ image_processing_tools}

Some definitions and brief description of general principles used in
 image processing are required to measure the profiles. Then, the design of the library 
mixing different techniques
is briefly detailed  to detect the profile in the noisy environment.

\subsection{Image treatment basics}
\subsubsection{Some definitions}
\label{some_definitions}

A numerical grey image can be described as 3D surface divided by a grid mesh
 in the X,Y plane. Each square represents a pixel and the relief surface at Z axis,
 the grey level. 
A strong relief change or high gradient greyness values at
 the image are perceived by human eyes as light changes, and can be interpreted
 as objects edges.

Sometimes, a regular relief patrons or regular greyness
 variation can be distinguished. The human eyes can perceive these patrons as texture 
and interpret the space between different textures zones as edges.
There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
 Most of them can be classified by the way  is operated above the image pixels and grey level.

\subsubsection{Filters}
\label{filters}

The filters are algorithms that operate as mathematical functions $f$ above the 
$X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
Different kind of filters can be mentioned as median, Gaussian, impulse,
 adaptive and others. The impulse filters such Canny are 
widely use to edge detection \cite{COCQUEREZ}. These filters have an
 impulse response to most important greyness gradient in the 
image; this allows the filter a better edges localisation
 (see figure \ref{fig::photo-explication-filter}). 
For this reason, Canny filter is widely 
used in the library to detect the welding elements edges. 
However, it is sensible to noise or secondary greyness gradients in the image
 and, in consequence, it have some difficulties to define closed surface.

\subsubsection{Snake and level set}
\label{snake_and_level_set}

Curve propagation is a popular technique in image analysis for object extraction,
 object tracking, edge detection and others (see figure 
\ref{fig::photo-explication-snake}). The central idea behind such an approach
 is to evolve a curve towards the lowest potential of a cost function. 
However at each stage of curve evolution, each curve point potential has
 to be computed. A lot of point (better curve resolution) take a lot 
computing time, and therefore are not yet apply to real time detection
 or relatively speed automatic image processing. For this reason snake algorithms are not used in the library.

\subsubsection{Segmentation}
\label{segmentation}

Let $B$ an image and let $R_{i}$ a region of $B$ such:

\begin{eqnarray}
B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
\mbox{with}\ R_{i} \neq \emptyset \\
\mbox{and}\  R_{i}\bigcap R_{j} = \emptyset\ \forall i, j\ \mbox{with}\ i \neq j\ 
\label{equation-segmentation}
\end{eqnarray}

A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. 
Each region is a connected set of pixels with 
common properties (intensity, texture,...) \cite{COCQUEREZ}.
 The partition is generated by operations or comparisons methods between 
regions. Generally, this treatment offers a good detection edges if
 the elements and surrounding area have different textures (see figure
 \ref{fig::photo-explication-segmentation}). 
Note that different regions can belong to the same partition,
 therefore the surface is not always connected and,
 in consequence, the edges of the interest regions are not always closed.

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[Weld pool image in static GTAW process]{\label{fig::photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{figure3a.png}}
%\subfigure[Canny filter treatment]{\label{fig::photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{figure3b.png}}\\
%\subfigure[Snake treatment]{\label{fig::photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{figure3c.png}}
%\subfigure[Segmentation image by 2 cluster sample comparison]{\label{fig::photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{figure3d.png}}
%\end{center}
%\caption{{\small Samples of different methods technique for image processing}}
%\label{fig::photo-explication}
%\end{figure}

\subsection{Image treatment library}
\label{image_treatment_library}

A multipurpose image processing library has been developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such as Macro drop, droplets and weld pool.
The library can manage different kinds of image acquisition (optical setup). 
The library is implemented in a oriented object C++ language.
Then,  erCv is a scalable 
and portable library able to perform real time
 contour detection. The library is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
To manage the edge detection during welding process,
the library is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments for noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentation by samples comparator, watershed transformation,
 filters edge detectors and histogram based methods.  
 Most of the functionality comes from \cite{OPENCV}.
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closing condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
   The algorithm of \cite{BOOSTGRAPH} are used.
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

%\begin{figure}
%\begin{center}
%\includegraphics[width=10cm]{figure4.png}
%\caption{{\small Flow diagram of erCv library composition}}
%\label{fig::schema-erCv}
%\end{center}
%\end{figure}

The originality of the library comes from the aggregation 
and complementarity of the different numerical tools.
The main difficulty is to find algorithms with good parameters all along the process.

% On s ARRETE LA

\section{ Applying image processing}
\label{ applying_image_processing}

\subsection{ Image Features}
\label{image_features}

Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image features imposed by the image acquisition procedure as: image view angle and image color, must be analyzed and modified.

\subsubsection{ Image Calibration}
\label{ image_calibration}

As was shown in section \ref{image-acquisition-setup}, the camera records a specular reflection of the welding process. Therefore the image of the welding objects is not orthogonal to the optical axes of the camera. In order to correct the image perspective, a function has been included in the image treatment module. A control image (small chessboard image with known real dimensions) is recorded at the weld pool place. An algorithm recognizes the chessboard corners and builds a transformation matrix between the control image (chessboard recorded image) and the original digital image. Finally, to calibrate the image dimension (in pixels) to the real objects dimension (in millimeters), a conversion scale is applied with the real dimensions of chessboard control image $conv = 1\ mm/ 20\ pixels$.

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[Chessboard control image]{\label{photo-calibration-cuadro-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-patron.png}}
%\subfigure[Chessboard original digital image]{\label{photo-calibration-cuadro-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-origin.png}}\\
%\subfigure[Raw recorded image]{\label{photo-calibration-image-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-origin.png}}
%\subfigure[Perspective corrected image]{\label{photo-calibration-image-corrected}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-corrected.png}}
%\end{center}
%\caption{{\small Perspective image correction samples}}
%\label{photo-calibration}
%\end{figure}

\subsubsection{Image color}
\label{image-color}

As has been mentioned in section \ref{filters}, most of the filter type algorithm (including canny filter) operates as function over the image grayness levels. Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image. In order to allow to use filters algorithm and to do more efficient the image processing a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).

  \subsection{ Image Preprocessing}
\label{image-preprocessing}

The idea is to recognize the weld pool from the raw image and therefore calculate his 2D surface area. This requires the identification of a well define weld pool contour. Several approaches could be uses to obtain the weld pool contour such as edge detection techniques  ( impulse filters) \cite{WU2}, Hough transforms \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}. Nevertheless the most common approach is the image segmentation \cite{WANG}.

Thanks to the optical method acquisition (specular reflection), the mirror like surface of the weld pool reflect a uniform dark surface to the camera while the solid metal surface reflect a diffuse lighting surface \cite{WU2}.

A natural way to segment the images, could be separate it between the roughness (non homogeneous lighting zone) and non roughness zone or dark zone as the weld pool area (see figures \ref{photo-macro-drop-original}).

However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides presents on the weld pool (see figure \ref{photo-macro-drop-original}), prevents to use a simply approach of existing techniques to isolate the weld pool. Perform 2D contour require an effective techniques combination, to correct the light reflection distortion into the weld pool, isolate the weld pool and extract his contour.
% ; using to this the basic image processing concepts previous mentioned (see section
% \ref{image-processing-background}).

\subsubsection{Impurities and reflex correction}
\label{impurities-and-reflex-correction}

To apply segmentation techniques able to isolate the weld pool from the image, the arc reflects and the impurities over the weld pool have to be reduced.

Note that the impurities and the high intensities reflection appear as white or high gray level blobs into the dark or homogeneous low gray level weld pool (see figure \ref{photo-grayness-level}. An algorithm able to detect the ÔÕwhiteÕÕ blobs into the weld pool and correct its has been developed and included into the image treatment module of erCv. The algorithm use the same principia used by the well known red eye detections and corrections algorithm \cite{GAUBATZ}.

The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g\_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g\_lower$ to define the maximal gray level of the weld pool and $s\_max$ to define the blob maximum pixel sizes.

Call $B$ an arbitrary ÔÕwhiteÕÕ blob set, $\partial B$ his boundary and $size(B)$ his size in pixels numbers. Call $(x, y)$ a pixel coordinates in the image and $gray\_level( x, y)$ the pixel associate grayness level.

 \begin{eqnarray*}
 ( x, y) \in B\ \mbox{if} \\
gray\_level( x, y) > g\_upper \\
\mbox{Then}\ B\ \mbox{is in the weld pool if} \\
gray\_level( x, y)\ \leq\ g\_lower\ \forall\ (x,y)\  \in\  \partial B \\ 
\mbox{and if}\ size(B)\ <\ s\_max
 \end{eqnarray*}

If $B$ is in the weld pool, the grayness level at each pixel $(x,y)$ inside $B$ is replaced by the grayness average value of the grayness level pixels of $\partial B$ (see equation \ref{equation-grayness-recouvrement}). Then the ÔÕwhiteÕÕ blob is replaced by a low average grayness level surface, similar to the rest of the weld pool grayness level.

\begin{equation}
gray\_level( x, y) = \frac{gray\_level( x, y_{\partial B}) + gray\_level( x_{\partial B}, y) }{ 2}
\label{equation-grayness-recouvrement}
\end{equation}

Using this algorithm, most of the impurities and the arc light reflections into the weld pool have been corrected.

\subsubsection{ Texture Analysis Principia}
\label{texture-analysis-principia}

Now, the weld pool appears as a more uniform dark surface, which contrast with the non uniform gray level values of the surrounding solid metal area.
This particularity in the grayness level distribution (roughness) at the image could be interpreted as different textures zones \cite{MATERKA}, in the same the way as the eyes recognize the texture in the object surface and$/$or images.

The texture analysis method to perform image segmentation is an image processing technique widely uses in biomedicine, satellite recognition, industrial quality control and others fields requiring image processing. There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \cite{MATERKA}.
The structural method requires complex logical analysis, while the transform and model based methods require mathematical analysis that required deterministic properties in grayness levels distributions \cite{MATERKA}. The statistical methods respond intuitively to what human eyes recognize: Two surfaces with different grayness level distribution or roughness.

As has been mentioned in section \ref{segmentation}, image segmentation means split into two or more fields the image. One field, would be mark in one color and the rest of the image in other color \cite{COCQUEREZ}.

\subsubsection{ Applying texture analysis}
\label{appliying-texture-analysis}

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[Macro drop raw image]{\label{fig::photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{figure5a.png}}
%\subfigure[Macro drop grayness image]{\label{fig::photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{figure5b.png}}\\
%\subfigure[First smooth filter]{\label{fig::photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{figure5c.png}}
%\subfigure[Adaptive threshold per regions]{\label{fig::photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{figure5d.png}}\\
%\subfigure[Median filter]{\label{fig::photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{figure5e.png}}
%\subfigure[Canny filter]{\label{fig::photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure5f.png}}\\
%\end{center}
%\caption{{\small Image treatment step by step of PGMAW process}}
%\label{fig::photo-macro-drop}
%\end{figure}

\subsection{Edge extraction}
\label{edge_extraction}

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t1 ]{\label{fig::photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure6a.png}}
%\subfigure[t2 ]{\label{fig::photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure6b.png}}\\
%\subfigure[t3 ]{\label{fig::photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure6c.png}}
%\subfigure[t4 ]{\label{fig::photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure6d.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-macro-drop}
%\end{figure}
%
%               
%                                  
%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t = ]{\label{fig::photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure7a.png}}
%\subfigure[t = ]{\label{fig::photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{figure7b.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-droplet}
%\end{figure}

A graph algorithm connects this segment and finds the longest closer segment.
 The longest closer segment corresponds to the metal transfer drop profile 
(see figure \ref{fig::photo-results-droplet}).

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t1 ]{\label{fig::photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure8a.png}}
%\subfigure[t2 ]{\label{fig::photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure8b.png}}\\
%\subfigure[t3 ]{\label{fig::photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure8c.png}}
%\subfigure[t4 ]{\label{fig::photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure8d.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-droplet}
%\end{figure}

\subsection{Geometrical Analysis}
\label{geometrical_analize}

\section{ Results}
\label{results}

\subsubsection{Discussions}
\label{discussion}

\section{ Conclusions}
\label{conclusions}

\section*{Acknowledgment}
The authors want to thanks the Agence National pour la Recherche (ANR) which grants this research
under the ANR-JCJC038 young scientist contract. 
\section*{References}
$ $
%\bibliographystyle{unsrt}
\bibliography{paper_bain_drop}

%\section*{References}
%\begin{thebibliography}{10}
%\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
%(Reading, MA: Addison-Wesley)
%\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')

% \cite{BALSAMO}
%\cite{WANG}
%\cite{CHO}
%\cite{LIN}
% \cite{ZHANG4}
%\cite{BAE}
%\cite{NORDBRUCH}
%\bibitem{CGAL} http://www.cgal.org 
%\cite{ChapuisThesis}
%\cite{WU1}
%\cite{SEED}
% \cite{COCQUEREZ}
% \cite{OPENCV}
% \cite{GEOMETRICAL}
% \cite{white}
%\end{thebibliography}
\end{document}

### 2011-05-31 articles/TIG/paper_bain.tex

--- 2011-04-08 articles/TIG/doc_broullion/latex/paper_bain.tex
@@
 
-Gas Tungsten Arc Welding (GTAW), which uses a non-consumable tungsten electrode and an inert gas for arc shielding, is an extremely important arc welding process.
-It is commonly used for welding hard-to-weld metals such as stainless steel \cite{JUANG} and therefore widely use in modern and basic industries.
-To achieve good weld quality in GTAW process, several weldment characteristics or objects should be sensed and controlled \cite{DOUMANIDIS}.
-It is shown that the geometry of the weld pool, in particular his shape and size, contains sufficient information about weld penetration to evaluate the weld quality \cite{ZHANG}.
-Furthermore it has been shown that the welding arc parameters to simulation and weld quality are directly relate to the weld pool geometry \cite{LU}.
-Basically the weld pool object is the key in quality control to automated welding process \cite{KOVACEVIC}. 
-According to this a better comprehension of weld pool behavior presents a GTAW process, could help to improve numerical simulations and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
+Gas Tungsten Arc Welding (GTAW), which uses a non-consumable tungsten 
+electrode and an inert gas for arc shielding, is an extremely 
+important arc welding process. It is commonly used for welding hard-to-weld
+ metals such as stainless steel \cite{JUANG} and therefore widely use in 
+modern and basic industries. To achieve good weld quality in GTAW process,
+ several weldment characteristics or objects should be sensed and
+ controlled \cite{DOUMANIDIS}. It is shown that the geometry of the weld 
+pool, in particular his shape and size, contains sufficient information
+ about weld penetration to evaluate the weld quality \cite{ZHANG}.
+ Furthermore it has been shown that the welding arc parameters to 
+simulation and weld quality are directly relate to the weld pool 
+geometry \cite{LU}.
+Basically the weld pool object is the key in quality control 
+to automated welding process \cite{KOVACEVIC}. 
+According to this a better comprehension of weld pool behavior
+ presents a GTAW process, could help to improve numerical 
+simulations and enhance welding quality in manufacturing 
+process \cite{LIN}, \cite{WU1}.
 
-There have been many studies on visual sensing techniques for observing weld pool image \cite{BAE}.
-Optical sensors like high speed CCD cameras and lighting systems have been widely use in GTAW process to realize image acquisition \cite{GUANGJUN}, control process \cite{BAE} and parametric studies \cite{BALSAMO}.
-Then image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
-Nevertheless the strong interference from the arc lightning required more than standard image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}.
-Previous work has shown that is possible to perform geometrical analysis in weld pools \cite{WU1}.
-Parameters such as weld pool contour and surface has been detected and measure using different and specifics processing images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}.
-However, to date, effectively automatic images processing of GTAW process has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.
+There have been many studies on visual sensing techniques
+ for observing weld pool image \cite{BAE}. Optical sensors
+ like high speed CCD cameras and lighting systems have been
+ widely use in GTAW process to realize image acquisition 
+\cite{GUANGJUN}, control process \cite{BAE} and parametric 
+studies \cite{BALSAMO}. Then image processing plays a critical
+ role in extracting useful information from visual scenes 
+\cite{WANG}. Nevertheless the strong interference from the
+ arc lightning required more than standard image treatment
+ to analyses the raw images of the welding process 
+\cite{NORDBRUCH}. Previous work has shown that is possible
+ to perform geometrical analysis in weld pools \cite{WU1}.
+ Parameters such as weld pool contour and surface has been
+ detected and measure using different and specifics processing 
+images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}.
+ However, to date, effectively automatic images processing 
+of GTAW process has not been developed, possibly due to the
+ level difficulty involved for welding researchers \cite{WANG}.
 
-To perform geometrical analysis in weld pool; a multipurpose C++ based library (erCv) was developed by the Weld/Assembly group of LMGC laboratory.
-These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical analysis, graph theory applications and image visualization.
+To perform geometrical analysis in weld pool; a multipurpose
+ C++ based library (erCv) was developed by the Weld/Assembly
+ group of LMGC laboratory. These library results from
+ selected functions join from highly reliable open source
+ libraries to images treatment, geometrical analysis, 
+graph theory applications and image visualization.
 
-In a first step, and despite the different static and dynamic weld conditions, as well as different current regime, a reliable 2D profiles and geometrical parameters from weld pool, has been obtained using the mentioned library.
-Using this, a dimension and dimensionless analysis has been performed into a static and dynamic GTAW process.
-The intention is contribute to simplify futures numerical models of weld pool-arc interaction and quality process.
+In a first step, and despite the different static and dynamic 
+weld conditions, as well as different current regime, a 
+reliable 2D profiles and geometrical parameters from weld
+ pool, has been obtained using the mentioned library. 
+Using this, a dimension and dimensionless analysis has 
+been performed into a static and dynamic GTAW process. 
+The intention is contribute to simplify futures numerical
+ models of weld pool-arc interaction and quality process.
 
@@
 
-Indirectly, the weld pool geometry could be detected by different methods such pool oscillations \cite{RENWICK}, ultrasonic sensing \cite{CARLSON}, radiography \cite{ROKHLIN}.
-However to obtain more precise measurements, direct acquisition methods, as vision based techniques, should be use \cite{KOVACEVIC}.
-Bradstreet was the first researcher to experimentally study the bead hump formation \cite{CHO}.
-Humping was defined as the series of undulations of the weld bead.
-Further studies as computer simulation made by CHO et al.
-\cite{CHO} shown a relation between the droplet momentum deposition and the hump size.
-Same relations has been found between metal transfer process and welding quality \cite{}
+Indirectly, the weld pool geometry could be detected 
+by different methods such pool oscillations \cite{RENWICK}, 
+ultrasonic sensing \cite{CARLSON}, radiography \cite{ROKHLIN}.
+ However to obtain more precise measurements, direct 
+acquisition methods, as vision based techniques, should 
+be use \cite{KOVACEVIC}.     Bradstreet was the first 
+researcher to experimentally study the bead hump formation
+ \cite{CHO}. Humping was defined as the series of 
+undulations of the weld bead. Further studies as computer
+ simulation made by CHO et al. \cite{CHO} shown a relation
+ between the droplet momentum deposition and the hump size.
+ Same relations has been found between metal transfer process
+ and welding quality \cite{}
 
-Then the shape and size kinetic analysis of macro drop and droplets could help to better understand and enhance the PGMAW process.
-To monitoring the shape and size of these welding objects, to a first step, a 2D approach would be sufficient.
-Therefore a shadowgraphy technique, or back lighting, is the natural choice to record the droplets and macro drops profiles \cite{BALSAMO}, furthermore is one of the only way to access these quantities.
-Due to the arc light interference and the relatively high speed of wire feed process, a high speed camera and an effective image processing algorithms are required \cite{WANG}.
-The typically frame rate acquisition to metal transfer drop kinetic analysis is $3000$ per second \cite{WANG}.
-Therefore the algorithms have to be able to extract the geometrical information (area, size and others) from the macro drop and droplets, from a huge amount of data.
-In addition, the voltage and current signals are directly related with the droplet formation at the wire \cite{BALSAMO}.
-Good synchronizations methods have to be applied between shadowgraphies frames and electrical signals.
+Then the shape and size kinetic analysis of macro drop and 
+droplets could help to better understand and enhance the PGMAW 
+process. To monitoring the shape and size of these welding 
+objects, to a first step, a 2D approach would be sufficient.
+ Therefore a shadowgraphy technique, or back lighting, is 
+the natural choice to record the droplets and macro drops 
+profiles \cite{BALSAMO}, furthermore is one of the only way
+ to access these quantities. Due to the arc light interference
+ and the relatively high speed of wire feed process, a high
+ speed camera and an effective image processing algorithms 
+are required \cite{WANG}. The typically frame rate acquisition
+ to metal transfer drop kinetic analysis is $3000$ per second 
+\cite{WANG}. Therefore the algorithms have to be able to extract
+ the geometrical information (area, size and others) from 
+the macro drop and droplets, from a huge amount of data. 
+In addition, the voltage and current signals are directly
+ related with the droplet formation at the wire \cite{BALSAMO}.
+ Good synchronizations methods have to be applied between 
+shadowgraphies frames and electrical signals.
 
@@
 
-A numerical grey image can be describe as 3D surface discretized by a grid mesh in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis, the grey level.
+A numerical grey image can be describe as 3D surface discretized by a grid 
+mesh in the X,Y plane. Each mesh represents a pixel and the relief surface
+ at Z axis, the grey level.
 
-A strong relief change or high gradient greyness values at the image are perceive by human eyes as light changes, and can be interpreted as objects edges. 
-Sometimes, a regular relief patrons or regular greyness variation can be distinguish.
-The human eyes can perceive these patrons as texture and interpret the space between different textures zones as edges.
-There exist a large spectrum of algorithms to image treatment, in particular to edges detect. Most of them can be classified by the way that his operate above the image pixels and grey level.
+A strong relief change or high gradient greyness values at the image are
+ perceive by human eyes as light changes, and can be interpreted as 
+objects edges. 
+Sometimes, a regular relief patrons or regular greyness variation 
+can be distinguish. The human eyes can perceive these patrons as 
+texture and interpret the space between different textures zones as edges.
+There exist a large spectrum of algorithms to image treatment, 
+in particular to edges detect. Most of them can be classified 
+by the way that his operate above the image pixels and grey level.
 
@@
 
-The filters are algorithms that operate as mathematical functions $f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  $f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
-Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others.
-The impulse filters such Canny are widely use to edge detection \cite{COCQUEREZ}.
-These filter have an impulse response to most important greyness gradient in the image; this allows the filter a better edges localisation (see figure \ref{photo-explication-filter}).
-For this reason, Canny filter is widely use at erCv library to detect the welding elements edges.
-However, it is sensible to noise or secondary greyness gradients in the image and, in consequence, it have some difficulties to define closer surface.
+The filters are algorithms that operate as mathematical functions 
+$f$ above the $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
+$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
+Different kind of filters can be mentioned as median, Gaussian, 
+impulse, adaptive and others. The impulse filters such Canny are
+ widely use to edge detection \cite{COCQUEREZ}. These filter have
+ an impulse response to most important greyness gradient in the 
+image; this allows the filter a better edges localisation (see 
+figure \ref{photo-explication-filter}). For this reason, Canny 
+filter is widely use at erCv library to detect the welding 
+elements edges. However, it is sensible to noise or secondary
+ greyness gradients in the image and, in consequence, it have 
+some difficulties to define closer surface.
 
@@
 
-Curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure \ref{photo-explication-snake}).
-The central idea behind such an approach is to evolve a curve towards the lowest potential of a cost function.
-However at each stage of curve evolution, each curve point potential has to be computed.
-A lot of point (better curve resolution) take a lot computing time, and therefore are not yet apply to real time detection or relatively speed automatic image processing.
-For this reason snake algorithms are not used at erCv.
+Curve propagation is a popular technique in image analysis 
+for object extraction, object tracking, edge detection and 
+others (see figure \ref{photo-explication-snake}). The central
+ idea behind such an approach is to evolve a curve towards 
+the lowest potential of a cost function. However at each 
+stage of curve evolution, each curve point potential has 
+to be computed. A lot of point (better curve resolution) 
+take a lot computing time, and therefore are not yet apply
+ to real time detection or relatively speed automatic image
+ processing. For this reason snake algorithms are not used at erCv.
 
@@
 
-A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions.
-Each region is a connected set of pixels with common properties (intensity, texture,...) \cite{COCQUEREZ}.
-The partition is generated by operations or comparisons methods between regions.
-Generally, this treatment offers a good detection edges if the elements and surrounding area have different textures (see figure \ref{photo-explication-segmentation}).
-Note that different regions can belong to the same partition and not be placed together, therefore the surface is not always connected and, in consequence, the edges of the interest regions are not always closed.
+A $B$ segmentation is an image treatment which generate a $B$ 
+partition in $R_{i}$ regions. Each region is a connected set of
+ pixels with common properties (intensity, texture,...) 
+\cite{COCQUEREZ}. The partition is generated by operations
+ or comparisons methods between regions. Generally, this 
+treatment offers a good detection edges if the elements 
+and surrounding area have different textures (see figure
+ \ref{photo-explication-segmentation}). 
+Note that different regions can belong to the same partition
+ and not be placed together, therefore the surface is not 
+always connected and, in consequence, the edges of the interest
+ regions are not always closed.
 
@@
 
-As mentioned, a multipurpose image processing library was developed and currently use at the laboratory, in order to analyze welding process objects.
-erCv is able to perform edge detection and geometrical analysis in a different welding objects such: Macro drop, droplets (for GMAW process) and weld pool (for GTAW process).
-erCv is a modular library assembled in a oriented object C++ language.
-Then erCv is a scalable and portable library able to perform real time contour detection.
-erCv is build in Phyton scripts link to C++, making it relatively convivial to use.
-erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
+As mentioned, a multipurpose image processing library was developed
+ and currently use at the laboratory, in order to analyze welding
+ process objects.
+erCv is able to perform edge detection and geometrical analysis
+ in a different welding objects such: Macro drop, droplets 
+(for GMAW process) and weld pool (for GTAW process).
+erCv is a modular library assembled in a oriented object C++ 
+language. Then erCv is a scalable and portable library able 
+to perform real time contour detection. erCv is build in Phyton 
+scripts link to C++, making it relatively convivial to use.
+erCv is compose by four processing modules based in C,  
+C++ and python language (see figure \ref{schema-erCv}). These modules are: 
 \begin{description}
-\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD camera are not calibrated and present light inhomogeneities and noise.
-In order to obtain the real shape and size of weld elements, this module include calibrations algorithms.
-To detect the welding objects contours it is necessary to improve the weld element image.
-This module has the pre-processing treatments to noise reduction and image enhancement.
-Then to start the edges detection process, this module includes processing algorithms as segmentations by samples comparators, watershed transformation, filters edge detectors and histogram based methods.
-\item[Geometrical Treatment and Analysis:] This module has to end the edge detection process, completing and in some cases extrapolating the weld elements edge.
-It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes.
-This module uses a full geometry algorithm library, which include different algorithms such as triangulations and mesh generation, alpha shape and convex hull generation and polygonal structures.
-\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the welding object edge from the image; this required some criteria such as continuity, length or closer condition.
-This module use graph algorithms to convert edges pixels points into connected segments, and therefore, identify and select the welding element edge using the criteria.
-This module is compose by connect segments, estimates minimal cut, determine largest chain segments and others algorithms.
-\item[Visualization:] This module is a set of functions use to execute, show and/or register the different steps at the image process.
+\item[Image Treatment:] Due to weld process conditions such
+ arc lightening, heat and electrodes positions; the raw image
+ registered by CCD camera are not calibrated and present light
+ inhomogeneities and noise. In order to obtain the real shape
+ and size of weld elements, this module include calibrations
+ algorithms. To detect the welding objects contours it is necessary
+ to improve the weld element image. This module has the pre-processing
+ treatments to noise reduction and image enhancement. Then to start
+ the edges detection process, this module includes processing 
+algorithms as segmentations by samples comparators, watershed
+ transformation, filters edge detectors and histogram based
+ methods.  
+\item[Geometrical Treatment and Analysis:] This module has 
+to end the edge detection process, completing and in some 
+cases extrapolating the weld elements edge. It is also 
+responsible to compute the geometrical data of welding 
+elements such weld pool surface and metal transfer drop 
+volumes. This module uses a full geometry algorithm library,
+ which include different algorithms such as triangulations 
+and mesh generation, alpha shape and convex hull generation
+ and polygonal structures.
+\item[Graph Theories:] To compute the geometrical data of
+ welding elements it is necessary to extract the welding 
+object edge from the image; this required some criteria 
+such as continuity, length or closer condition.  This module 
+use graph algorithms to convert edges pixels points into 
+connected segments, and therefore, identify and select the 
+welding element edge using the criteria. This module is compose
+ by connect segments, estimates minimal cut, determine largest
+ chain segments and others algorithms. 
+\item[Visualization:] This module is a set of functions use
+ to execute, show and/or register the different steps at the
+ image process.
 \end{description}
@@
 
-The objective is to perform geometrical analysis of weld pool in a GTAW process.
-Notes that geometrical analysis refers to surface value and contour detection of weld pool in static and dynamic GTAW process.
-The methods choose is the image treatment of recorded image of GTAW static and dynamic process by a high speed CCD camera.
+The objective is to perform geometrical analysis of weld pool
+ in a GTAW process. Notes that geometrical analysis refers to
+ surface value and contour detection of weld pool in static and 
+dynamic GTAW process. The methods choose is the image treatment 
+of recorded image of GTAW static and dynamic process by a high
+ speed CCD camera.
 
-To perform the geometrical analyses, different signals have to be synchronizes and recorder \cite{CHAPUIS}; therefore an accurate, reliable and synchronizes systems are requires due to the high amount of data and highly noisy environment (electromagnetic noise and arc light radiation).
+To perform the geometrical analyses, different signals have to be 
+synchronizes and recorder \cite{CHAPUIS}; therefore an accurate,
+ reliable and synchronizes systems are requires due to the high
+ amount of data and highly noisy environment (electromagnetic 
+noise and arc light radiation).
 
-A platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}).
-The platform was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go per test).
-This characteristic allows synchronizing (in time) the current and voltage signals with the acquired images.
+A platform has been developed at the laboratory to perform multi-physics
+ measures in arc welding process (see figure \ref{schema-platform}). 
+The platform was conceive with an automatically procedure to synchronize,
+ to acquire, to manage and to exploit large flow of multi-physical
+ experimental data (up to 2 Go per test). This characteristic allows
+ synchronizing (in time) the current and voltage signals with 
+the acquired images.
 
@@
 
-To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).
+To compare and analyze the data two open source numerical libraries
+ have been developed: The BAME (multi-physics measures data base)
+ for all general data and the erCv specific to image treatment 
+(including the spreading of welding pool geometry during welding).
 
@@
 
-Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. The target is a steel disk of $10\ mm$ of thickness and ER70S steel welding wire.
-The test campaign began by a reference test, with parameters fixed to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency droplets $113\ Hz$ and percentage of shielding gas ($CO_{2}$) $8$ (so $92\%$ argon).
-Welding parameters values are summarize in tables \ref{table-parameters-static} to static and \ref{table-parameters-change} to variables parameters.
+Stationary spots weld are made using the GMAW process with the Oerlikon
+ CitoWave 500 generator. The target is a steel disk of $10\ mm$ of
+ thickness and ER70S steel welding wire.
+The test campaign began by a reference test, with parameters fixed
+ to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency 
+droplets $113\ Hz$ and percentage of shielding gas ($CO_{2}$) $8$
+ (so $92\%$ argon). Welding parameters values are summarize in 
+tables \ref{table-parameters-static} to static and
+ \ref{table-parameters-change} to variables parameters.
 
@@
 
-Welding current and arc voltage are recorded at $30\ kHz$ sampling rate.
-The images are recorded at $4000$ frames per seconds, which is enough to measure macro drop radius and apparent liquid-solid contact angle histories.
-The images and electrical signals are synchronize, thanks to the automatically approach made in the multi physics platform.
+Welding current and arc voltage are recorded at $30\ kHz$ 
+sampling rate. The images are recorded at $4000$ frames per
+ seconds, which is enough to measure macro drop radius and 
+apparent liquid-solid contact angle histories. The images 
+and electrical signals are synchronize, thanks to the 
+automatically approach made in the multi physics platform.
 
@@
 
-The purpose is to study the evolution of weld pool object in a GTAW process.
-Therefore it is necessary to detect the contour, without predetermined shape, of the weld pool and calculate his surface area.
+The purpose is to study the evolution of weld pool 
+object in a GTAW process. Therefore it is necessary 
+to detect the contour, without predetermined shape, 
+of the weld pool and calculate his surface area.
 
@@
 
-At figure \ref{figure_1} appears the geometrical elements to be study at the weld pool: the weld pool contour and surface area.
+At figure \ref{figure_1} appears the geometrical elements
+ to be study at the weld pool: the weld pool contour and surface area.
 
@@
 
-As was shown in section \ref{image-acquisition-setup}, the camera recording a specular reflection of the welding process.
-Therefore the image of the welding objects is not orthogonal to the optical axes of the camera.
-In order to correct the image perspective, a control image (small chessboard image with known real dimensions) has been recorded at the weld pool place.
-A transformation matrix has been build between the control image (chessboard recorded image) and the original digital image.
-To calibrate the image dimension (in pixels) to the real objects dimension (in millimeters), a conversion scale has been applied with the real dimensions of chessboard control image $conv = 1\ mm/ 20\ pixels$.
+As was shown in section \ref{image-acquisition-setup}, the 
+camera recording a specular reflection of the welding process.
+ Therefore the image of the welding objects is not orthogonal
+ to the optical axes of the camera. In order to correct the 
+image perspective, a control image (small chessboard image 
+with known real dimensions) has been recorded at the weld 
+pool place. A transformation matrix has been build between 
+the control image (chessboard recorded image) and the original
+ digital image. To calibrate the image dimension (in pixels) 
+to the real objects dimension (in millimeters), a conversion
+ scale has been applied with the real dimensions of chessboard 
+control image $conv = 1\ mm/ 20\ pixels$.
 
@@
 
-The idea is to recognize the weld pool from the raw image and therefore calculate his 2D surface area.
-This requires the identification of a well define weld pool contour.
-Several approaches could be uses to obtain the weld pool contour, such as edge detection techniques \cite{WU2}, Hough transforms \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}.
-Nevertheless the most common approach is the image segmentation \cite{WANG}.
-That means to split in two or more fields the image.
-The object, in this case the weld pool, would be colored in one color and the rest of the image in other color \cite{COCQUEREZ}.
-Thanks to the optical method acquisition (specular reflection) a natural way to segment the images, could be separate its between the roughness (non homogeneous lighting colored zone) and non roughness zone (see figures \ref{photo-macro-drop-original}).
-Into the lighting zone at the images, the mirror like surface of the weld pool reflect a uniform dark surface to the camera while the solid metal surface reflect a diffuse colored surface \cite{WU2}.
-This particularity in the color and in the light distribution (roughness) at the image could be interpreted as different textures zones \cite{MATERKA}, in the same the way as the eyes recognize the texture in the object surface and$/$or images.
-The texture analysis method to perform image segmentation is an image processing technique widely uses in biomedicine, satellite recognition, industrial quality control and others fields requiring image processing.
-There exist different approaches to texture analysis, each one using their own image analysis methods:
+The idea is to recognize the weld pool from the raw image and 
+therefore calculate his 2D surface area. This requires the 
+identification of a well define weld pool contour. Several
+ approaches could be uses to obtain the weld pool contour, such
+ as edge detection techniques \cite{WU2}, Hough transforms
+ \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}.
+ Nevertheless the most common approach is the image segmentation
+ \cite{WANG}. That means to split in two or more fields the image.
+  The object, in this case the weld pool, would be colored in one
+ color and the rest of the image in other color \cite{COCQUEREZ}.
+ Thanks to the optical method acquisition (specular reflection) a
+ natural way to segment the images, could be separate its between
+ the roughness (non homogeneous lighting colored zone) and non 
+roughness zone (see figures \ref{photo-macro-drop-original}). 
+Into the lighting zone at the images, the mirror like surface 
+of the weld pool reflect a uniform dark surface to the camera
+ while the solid metal surface reflect a diffuse colored 
+surface \cite{WU2}. This particularity in the color and in
+ the light distribution (roughness) at the image could be 
+interpreted as different textures zones \cite{MATERKA}, in
+ the same the way as the eyes recognize the texture in the object
+ surface and$/$or images.
+The texture analysis method to perform image segmentation is an
+ image processing technique widely uses in biomedicine, satellite 
+recognition, industrial quality control and others fields requiring
+ image processing. There exist different approaches to texture 
+analysis, each one using their own image analysis methods:
 \begin{description}
-\item[Structural] Represent texture by well defined primitives, and a hierarchy of spatial arrangements of those primitives.
-\item[Statistical] Represent the texture indirectly by the non-deterministic properties that govern the distributions and relationship between the grey levels of an images.
-\item[Model based] Using fractal and stochastic models, attempt to interpret an image texture by use of, respectively, generative image model and stochastic model.
-\item[Transform methods] Using Fourier and wavelet transforms, represent an image in a space whose co-ordinate system has an interpretation.
+\item[Structural] Represent texture by well defined primitives,
+ and a hierarchy of spatial arrangements of those primitives.
+\item[Statistical] Represent the texture indirectly by the 
+non-deterministic properties that govern the distributions 
+and relationship between the grey levels of an images.
+\item[Model based] Using fractal and stochastic models, 
+attempt to interpret an image texture by use of, respectively,
+ generative image model and stochastic model.
+\item[Transform methods] Using Fourier and wavelet transforms, 
+represent an image in a space whose co-ordinate system has an interpretation.
 \end{description}
 
-. Most of them required complex image analysis using hierarchy decomposition (structural), fractal or stochastic models (model based) and Fourier or wavelet transforms (transforms methods) 
+. Most of them required complex image analysis using
+ hierarchy decomposition (structural), fractal or stochastic model
+s (model based) and Fourier or wavelet transforms (transforms methods) 
  Di BLA BLA use this  has been thedescribe  where the shadows zones are the projection of the macro drop and droplet.

### 2011-05-31 examples/melt_pool_TIG/fusion_bain_move_python.cpp

@@ -22,15 +22,13 @@ int main( int hola, char** file_name)
 { // Zone d interet dans l image retournee
   CvRect rect;
   rect.x=138;rect.y=71;rect.width=261;rect.height=281;
-  //rect.x=50;rect.y=50;rect.width=150;rect.height=190;
-  erWhitBP whi( 150, 150, 5, 100);
-  erSmootP p1(BLUR,9), p2(MEDIAN,9);
+  erWhitBP whi ( 150, 150, 5, 100);
+  erSmootP p1  (BLUR,9), p2(MEDIAN,7);
   erCannyP cann(500,500);
-  erDilatP dil(1); 
-  erThresP thr(THRESH_BINARY_,139,255); //** <
-  CvRect rec_tem;
+  erDilatP dil (2); 
+  erThresP thr(THRESH_BINARY_,121,255); //** <
+  CvRect   rec_tem;
   rec_tem.x = 231; rec_tem.y = 254; rec_tem.width = 5; rec_tem.height = 5;
-  //rec_tem.x = 14; rec_tem.y = 20; rec_tem.width = 5; rec_tem.height = 5;
   erTemplP templ(SQDIFF_NORMED, rec_tem, true); 
   erAlphaP alp(1);
   erWeldPoolAnalysis wpa("bain_move");
@@ -38,28 +36,18 @@ int main( int hola, char** file_name)
   wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
   wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);
   
-  //<<<<<<< .mine
-  //   //wpa.doIt( "imageExemple_3.bmp");
+
   std::string img_base="../pictures/gtaw_for_edward_0587.bmp";
-  for(int i = 1; i < 40;i++)
+  for(int i = 1; i < 80;i++)
     {
-      std::string filename = erLoadImageSeriesAnalysis( img_base, 10);
+      std::string filename = erLoadImageSeriesAnalysis( img_base, 5);
       std::cout << "file name: " << filename << std::endl;
       std::cout << "hola0" << std::endl;
       wpa.doIt(filename);
       img_base = filename;
     };
   wpa.saveParameters( "result/test.out");
-  //=======
   
-  //wpa.doIt( "example_full_bain_1.bmp");
-  //wpa.doIt( "example_full_bain_2.bmp");
[…]

### 2011-05-31 examples/melt_pool_TIG/fusion_bain_move_python.py

@@ -1,0 +1,26 @@
+import sys
+sys.path.append('../../lib/erCv')
+
+from PyerCv import *
+from pylab import *
+rect    = CvRect();
+rect.x  = 138;rect.y=71;rect.width=261;rect.height=281;
+whi     = erWhitBP  ( 150, 150, 5, 100);
+p1      = erSmootP (BLUR,9)
+p2      = erSmootP(MEDIAN,7);
+cann    = erCannyP (500,500);
+dil     = erDilatP(2); 
+thr     = erThresP(THRESH_BINARY_,121,255); 
+rec_tem = CvRect();
+rec_tem.x = 231; rec_tem.y = 254; rec_tem.width = 5; rec_tem.height = 5;
+templ   = erTemplP(SQDIFF_NORMED, rec_tem, True); 
+alp     = erAlphaP(1);
+wpa     = erWeldPoolAnalysis("bain_move_python");
+wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
+wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);
+img_base="../pictures/gtaw_for_edward_0";
+i_dep = 587
+for i in arange(0,20):
+    im = img_base+str(i_dep+i*20)+'.bmp'
+    wpa.doIt(im)
+    print '------image:',im

### 2011-05-31 include/erCv/erCalibration.hpp

@@ -85,7 +85,7 @@ public:
       \param int           : nombre des carres de l echequier a prendre en compte (hauteur)
       \param char*         : nom du ficher avec les facteurs de conversion
   */
-  erCalibration( char*,char*, int, int, char* file_dimention = "cuadro_size.dat");
+  erCalibration( const char*,const char*, int, int, char* file_dimention = "cuadro_size.dat");
 
   /** \brief Destructeur */
   ~erCalibration(); 

### 2011-05-31 include/erCv/utilities/erFileUtilities.hpp

@@ -44,7 +44,7 @@
 /** \addtogroup utilities */
 /*@{*/
 /** \brief Permet de tester si un fichier dont le chemin est l argument existe */
-bool erFileExists( char*);
+bool erFileExists(const char*);
 /*@}*/
 
 #endif

### 2011-05-31 src/erCalibration.cpp

@@ -46,7 +46,7 @@
 erCalibration::erCalibration(){};
 
 
-erCalibration::erCalibration( char* name_image_patron, char* name_image_mesure, int board_w, int board_h, char* file_dimention)
+erCalibration::erCalibration(const char* name_image_patron,const char* name_image_mesure, int board_w, int board_h, char* file_dimention)
 { 
   _board_w              = board_w;
   _board_h              = board_h;

### 2011-05-31 src/erCvAnalysis.cpp

@@ -484,7 +484,7 @@ void erWeldPoolAnalysis::setOutputGeometryFile(std::string file) //** Le fichier
 {
   output_geometry_file = dir_analysis+"/"+file+"_wep"+".geo";
   std::ofstream out(output_geometry_file.c_str());
-  out << "Nom_du_fichier\t\tCentroid_x\tCentroid_y\tAire\tAxe_Princ_x\tAxe_Princ_y\tFit(0-1)\n";
+  out << "Nom_du_fichier\t\t\t\tCentroid_x\tCentroid_y\tAire\tAxe_Princ_x\tAxe_Princ_y\tFit(0-1)\n";
 
 };
 
@@ -532,7 +532,7 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
   erCvThreshold( &ee, &param_threshold);
 
   erCvCanny( &ee, &param_canny);
-  erShowImage( "result canny 2", &ee);
+  //erShowImage( "result canny 2", &ee);
   //erSaveImage2Analysis( &ee, file_name, fich, "can");
 
   IsEqualTo is_equal_255(255);

### 2011-05-31 src/erFileUtilities.cpp

@@ -34,7 +34,7 @@
 // knowledge of the CeCILL license and that you accept its terms.
 #include <erCv/utilities/erFileUtilities.hpp>
 
-bool erFileExists(char* name_file)
+bool erFileExists(const char* name_file)
 {   bool exist=true;
     FILE * file    = fopen(name_file,"r");
     if(file==NULL)

### 2011-05-31 src/Gui/erCvSegmentationUser.cpp

@@ -39,6 +39,8 @@
 #include <erCv/Gui/erCvSegmentationUser.hpp>
 #include <iostream>
 #include <fstream>
+#include<map>
+#include<vector>
 //#include "highgui.h"
 //#include <cstdio>
 

### 2011-05-31 src/erCvSegmentation.cpp

@@ -37,7 +37,8 @@
 #include <erCv/erCvSegmentation.hpp>
 #include <iostream>
 #include <fstream>
-
+#include<map>
+#include<vector>
 struct coordinate
 {
   unsigned int x, y;

### 2011-06-20 articles/TIG/paper_bain.tex

@@
-\title{ Weld pool detection and geometrical analysis during GTAW process by image processing library}
+\title{ Weld pool detection and geometrical analysis during GTAW process}
+
+\author{E Romero, J Chapuis ,C Bordreuil, F Souli\'e, G Fras}
+
+\address{Laboratoire de Mécanique et Génie Civil,
+CC048, Place Eugène Bataillon, Université Montpellier 2,
+34095 Montpellier, France}
+\ead{cyril.bordreuil@univ-montp2.fr}
 
@@
  controlled \cite{DOUMANIDIS}. It is shown that the geometry of the weld 
-pool, in particular his shape and size, contains sufficient information
+pool, in particular its shape and size, contains sufficient information
  about weld penetration to evaluate the weld quality \cite{ZHANG}.
@@
  role in extracting useful information from visual scenes 
-\cite{WANG}. Nevertheless the strong interference from the
+\cite{WANG}. Nevertheless, the strong interference from the
  arc lightning required more than standard image treatment
@@
 images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}.
- However, to date, effectively automatic images processing 
-of GTAW process has not been developed, possibly due to the
- level difficulty involved for welding researchers \cite{WANG}.
+ %However, to date, effectively automatic images processing 
+%of GTAW process has not been developed, possibly due to the
+% level difficulty involved for welding researchers \cite{WANG}.
 
-To perform geometrical analysis in weld pool; a multipurpose
- C++ based library (erCv) was developed by the Weld/Assembly
- group of LMGC laboratory. These library results from
+To perform geometrical analysis in weld pool in real time monitoring, a multipurpose
+ C++ based library (erCv) was developed at the lab. 
+The purpose of the library is to monitor the weld pool and to extract geometrical 
+information as weld pool surface or contour.
+This library results from
  selected functions join from highly reliable open source
@@
 graph theory applications and image visualization.
+The originality of the implemented library comes from 
+the aggregation of the different libraries, each contributing to solve different
+issues.
 
@@
 been performed into a static and dynamic GTAW process. 
-The intention is contribute to simplify futures numerical
+The intention is to contribute to enhance futur numerical
  models of weld pool-arc interaction and quality process.
@@
 
-Some definitions and brief description of generals principles used in image processing are required to better understand how is work the algorithms utilized by the erCv library.
+Some definitions and brief description of generals principles used in image 
+processing are required to better understand how the algorithms are gathered by the erCv library.
 
@@
 
-A numerical grey image can be describe as 3D surface discretized by a grid 
+A numerical grey image can be described as 3D surface discretized by a grid 
 mesh in the X,Y plane. Each mesh represents a pixel and the relief surface
@@
 There exist a large spectrum of algorithms to image treatment, 
-in particular to edges detect. Most of them can be classified 
-by the way that his operate above the image pixels and grey level.
+in particular to edges detection. Most of them can be classified 
+by the way that is operated on the image pixels and grey level.
 
@@
 impulse, adaptive and others. The impulse filters such Canny are
- widely use to edge detection \cite{COCQUEREZ}. These filter have
+ widely use for edge detection \cite{COCQUEREZ}. These filter have
  an impulse response to most important greyness gradient in the 
@@
  to real time detection or relatively speed automatic image
- processing. For this reason snake algorithms are not used at erCv.
+ processing. For this reason snake algorithms are not used in the library.
 
@@
 
-\section{Image treatment library (erCv)}
+\section{Image treatment library}
 \label{image-treatment-library-ercv}
@@
  in a different welding objects such: Macro drop, droplets 
-(for GMAW process) and weld pool (for GTAW process).
+(for GMAW process) \cite{ROMERO1} and weld pool (for GTAW process).
 erCv is a modular library assembled in a oriented object C++ 
-language. Then erCv is a scalable and portable library able 
+language. The library is a scalable and portable library able 
 to perform real time contour detection. erCv is build in Phyton 
 scripts link to C++, making it relatively convivial to use.
-erCv is compose by four processing modules based in C,  
+erCv is composed by four processing modules based in C,  
 C++ and python language (see figure \ref{schema-erCv}). These modules are: 
@@
  and size of weld elements, this module include calibrations
- algorithms. To detect the welding objects contours it is necessary
+ algorithms. To detect the welding object contours: it is necessary
  to improve the weld element image. This module has the pre-processing
@@
  transformation, filters edge detectors and histogram based
- methods.  
+ methods.  Basic algorithms come from OpenCv \cite{OPENCV} and are enriched 
+ by some implementations.
 \item[Geometrical Treatment and Analysis:] This module has 
-to end the edge detection process, completing and in some 
+to close the edge detection process, completing and in some 
 cases extrapolating the weld elements edge. It is also 
@@
 and mesh generation, alpha shape and convex hull generation
- and polygonal structures.
+ and polygonal structures. Basic algorithm come from CGAL \cite{CGAL} 
 \item[Graph Theories:] To compute the geometrical data of
@@
 object edge from the image; this required some criteria 
-such as continuity, length or closer condition.  This module 
+such as continuity, length or closure condition.  This module 
 use graph algorithms to convert edges pixels points into 
@@
 
-To perform the geometrical analyses, different signals have to be 
-synchronizes and recorder \cite{CHAPUIS}; therefore an accurate,
- reliable and synchronizes systems are requires due to the high
+To perform the geometrical analysis, different signals have to be 
+synchronized and recorded \cite{CHAPUIS}; therefore an accurate,
+ reliable and synchronized systems are required due to the high
  amount of data and highly noisy environment (electromagnetic 
@@
  measures in arc welding process (see figure \ref{schema-platform}). 
-The platform was conceive with an automatically procedure to synchronize,
+The platform was designed with an automatically procedure to synchronize,
  to acquire, to manage and to exploit large flow of multi-physical
@@
 
-Using a similar technique employed by Kovacevic et al.
-\cite{KOVACEVIC}, the GTAW static process has been recorded by the specular reflection optical method.
-A $650\ nm$ laser diode has been used to light the weld process from an estimate angle of $35\ degree$.
-The laser beam width ($ $) was sufficient to guarantee a homogeneous illumination of the welding process.
-The laser projects an image by reflection of welding objects (weld pool and surrounding metal substrate) to the other side of the welding place.
-At this place and aligned with the optical path of reflected laser beam, a Phantom V5.0 high speed camera has been placed in order to record the process images (see figure \ref{schema-montage-experimental-GTAW}).
+Using a similar technique employed by Kovacevic et al. \cite{KOVACEVIC}, 
+the GTAW static process has been recorded by the specular reflection optical method. 
+A $650\ nm$ laser diode has been used to light the weld process from an estimate angle
+ of $35\ degree$. The laser beam width ($ $) was sufficient to guarantee a homogeneous 
+illumination of the welding process. The laser projects an image by reflection of welding 
+objects (weld pool and surrounding metal substrate) to the other side of the welding place.
+ At this place and aligned with the optical path of reflected laser beam, a Phantom V5.0 
+high speed camera has been placed in order to record the process images (see figure \ref{schema-montage-experimental-GTAW}).
 
@@
 
-To enhance the image contrast of the weld objects inside the electric discharge, the intensity rate between arc light and laser diode have to be reduce.
-In order to this a $650\ \pm 10\ nm$ band pass filter, which correspond to the laser diode wavelength, has been placed in front of the camera lens to attenuate the arc light.
-Nevertheless, the raw images remain highly noisy by the arc light.
+To enhance the image contrast of the weld objects inside the electric discharge, 
+the intensity rate between arc light and laser diode have to be reduce. In order to 
+this a $650\ \pm 10\ nm$ band pass filter, which correspond to the laser diode wavelength,
+ has been placed in front of the camera lens to attenuate the arc light. Nevertheless, 
+the raw images remain highly noisy by the arc light.
 
@@
 
-Stationary spots weld are made using the GMAW process with the Oerlikon
- CitoWave 500 generator. The target is a steel disk of $10\ mm$ of
+Stationary spots weld are made using the GTAW process with the Sincosald
+ generator. The target is a steel disk of $10\ mm$ of
  thickness and ER70S steel welding wire.
 The test campaign began by a reference test, with parameters fixed
- to:  welding time $4\ s$, wire feed speed $6\ m/min$, frequency 
-droplets $113\ Hz$ and percentage of shielding gas ($CO_{2}$) $8$
- (so $92\%$ argon). Welding parameters values are summarize in 
+ to:  welding time $4\ s$ and the shielding gas is 
+ $100\%$ argon. Welding parameters values are summarized in 
 tables \ref{table-parameters-static} to static and
@@
 
+For weld bead on a flat plate, a travel speed of 30cm/min is chosen.
 \begin{table}
@@
 Welding wire type & ER70S \\ 
-Wire diameter ($mm$) or $drw$ & 1 \\  
 Contact tip to work distance ($mm$) & 20 \\
@@
 Contact tip to work distance ($mm$) & 20 \\
+Travel Speed (cm/min) & 30 \\
 Shielding gaz flowrate ($l/min$) & 18 \\ \hline
@@
 Welding current and arc voltage are recorded at $30\ kHz$ 
-sampling rate. The images are recorded at $4000$ frames per
- seconds, which is enough to measure macro drop radius and 
-apparent liquid-solid contact angle histories. The images 
+sampling rate. The images are recorded at $1000$ frames per
+ seconds, which is enough to measure liquid-solid interface. The images 
 and electrical signals are synchronize, thanks to the 
@@
 object in a GTAW process. Therefore it is necessary 
-to detect the contour, without predetermined shape, 
-of the weld pool and calculate his surface area.
+to detect the contour (polygon), without predetermined shape, 
+of the weld pool and calculate its surface area.
 
@@
 
-. Most of them required complex image analysis using
+Most of them required complex image analysis using
  hierarchy decomposition (structural), fractal or stochastic model

### 2011-06-21 articles/TIG/paper_bain3.tex

--- 2011-05-18 articles/TIG/doc_broullion/latex/paper_bain2.tex
@@
  the grey level. 
-A strong relief change or high gradient greyness values at
+A strong relief change or high gradient grey values at
  the image are perceived by human eyes as light changes, and can be interpreted
@@
 
-Sometimes, a regular relief patrons or regular greyness
+Sometimes, a regular relief patrons or regular greyness level
  variation can be distinguished. The human eyes can perceive these patrons as texture 
@@
 There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
- Most of them can be classified by the way  is operated above the image pixels and grey level.
+ Most of them can be classified by the way  is operated above the image pixels and grayness level.
 
@@
 widely use to edge detection \cite{COCQUEREZ}. These filters have an
- impulse response to most important greyness gradient in the 
-image; this allows the filter a better edges localisation
+ impulse response to most important grayness level gradient in the 
+image; this allows the filter a better edges localization
  (see figure \ref{fig::photo-explication-filter}). 
@@
 used in the library to detect the welding elements edges. 
-However, it is sensible to noise or secondary greyness gradients in the image
+However, it is sensible to noise or secondary grayness gradients in the image
  and, in consequence, it have some difficulties to define closed surface.
@@
 
-\subsection{ Image Features}
+\subsection{ Image Adjustments}
 \label{image_features}
 
-Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image features imposed by the image acquisition procedure as: image view angle and image color, must be analyzed and modified.
-
-\subsubsection{ Image Calibration}
-\label{ image_calibration}
+Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image physical characteristics imposed by the image acquisition procedure as: image view angle and image color, has been analyzed and modified.
 
@@
 
-\subsubsection{Image color}
-\label{image-color}
-
-As has been mentioned in section \ref{filters}, most of the filter type algorithm (including canny filter) operates as function over the image grayness levels.
+Concerning the image color, it has been mentioned in section \ref{filters}, that most of the filter type algorithm (including canny filter) operates as function over the image grayness levels.
 Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image.
-In order to allow to use filters algorithm and to do more efficient the image processing a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).
+In order to allow to use filters algorithm and to do more efficient the image processing, a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).
 
@@
 
-The idea is to recognize the weld pool from the raw image and therefore calculate his 2D surface area.
-This requires the identification of a well define weld pool contour.
-Several approaches could be uses to obtain the weld pool contour such as edge detection techniques  ( impulse filters) \cite{WU2}, Hough transforms \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}.
-Nevertheless the most common approach is the image segmentation \cite{WANG}.
+The idea is to recognize the weld pool into the raw image, extract a well define weld pool contour and therefore calculate his 2D surface area.
+Several approaches have been developed and can be used to obtain the weld pool contour.
+The edge detection techniques \cite{WU2} as level set or impulse filters, the Hough transforms \cite{OLSON} or the geometrical weld pool division \cite{KOVACEVIC}; nevertheless the most common approach is the image segmentation \cite{WANG}.
 
-Thanks to the optical method acquisition (specular reflection), the mirror like surface of the weld pool reflect a uniform dark surface to the camera while the solid metal surface reflect a diffuse lighting surface \cite{WU2}.
+Previous works \cite{WU2}, \cite{KOVACEVIC} have been showed that thanks to the optical acquisition method (specular reflection), the mirror like surface of the weld pool reflect a smoothness dark surface to the camera while the solid metal surface reflect a irregular grayness level surface.
+In the same the way as the eyes recognize the texture in a object surface and$/$or image, this particularity in the image grayness level distribution could be interpreted as roughness variations or different textures zones \cite{MATERKA}.
+And this propriety can be used to perform images segmentation dividing the image between the roughness zone and the smoothness dark zone (as the weld pool area, see figures \ref{photo-macro-drop-original}).
 
-A natural way to segment the images, could be separate it between the roughness (non homogeneous lighting zone) and non roughness zone or dark zone as the weld pool area (see figures \ref{photo-macro-drop-original}).
+This technique know as texture analysis is an image processing technique widely used in biomedicine, satellite recognition, quality control and others fields requiring image processing.
+There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \ref{MATERKA}.
+The structural method requires complex logical analysis, while the transform and model based methods require the identification and analysis of deterministic properties in the grayness level distributions \ref{MATERKA}.
+Finally the statistical method compares intuitively to what human eyes recognize: surfaces with an irregular grayness level distribution or roughness, which matches to what have been observed in the recorded images (see images \ref{}).
 
-However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides presents on the weld pool (see figure \ref{photo-macro-drop-original}), prevents to use a simply approach of existing techniques to isolate the weld pool.
-Perform 2D contour require an effective techniques combination, to correct the light reflection distortion into the weld pool, isolate the weld pool and extract his contour.
-% ; using to this the basic image processing concepts previous mentioned (see section
-% \ref{image-processing-background}).
+However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides present in both surface: (see figure \ref{photo-macro-drop-original}), induce error in the texture analysis.
+The impurities outside the weld pool, could be interpreted as dark smoothness zone like the weld pool and not as roughness zone, while the edge of impurities and light reflections into the weld pool could be interpreted as roughness zone.
+Therefore isolate the weld pool require more than a simply approach using one of the existing techniques.
+Indeed perform 2D contour require an effective techniques combination to correct the light reflection distortions and impurities, isolate the weld pool from the image and extract his contour.
 
-\subsubsection{Impurities and reflex correction}
+\subsubsection{Impurities and light reflects correction on the weld pool}
 \label{impurities-and-reflex-correction}
 
-To apply segmentation techniques able to isolate the weld pool from the image, the arc reflects and the impurities over the weld pool have to be reduced.
+%Before isolate the weld pool from the image, the arc reflects and the impurities over the 
+%weld pool have to be reduced.
 
-Note that the impurities and the high intensities reflection appear as white or high gray level blobs into the dark or homogeneous low gray level weld pool (see figure \ref{photo-grayness-level}.
+Note that the impurities and the high intensities reflection appear as white blobs (high gray values set of pixels) into the dark weld pool (low gray values set of pixel, see figure \ref{photo-grayness-level}).
 An algorithm able to detect the ÔÕwhiteÕÕ blobs into the weld pool and correct its has been developed and included into the image treatment module of erCv.
-The algorithm use the same principia used by the well known red eye detections and corrections algorithm \cite{GAUBATZ}.
+The algorithm use the same principia used by the red eye detections and corrections algorithm \cite{GAUBATZ}.
 
-The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g\_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g\_lower$ to define the maximal gray level of the weld pool and $s\_max$ to define the blob maximum pixel sizes.
+The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g_lower$ to define the maximal gray level of the weld pool and $s_max$ to define the blob maximum pixel sizes.
 
@@
 \begin{eqnarray*}
- ( x, y) \in B\ \mbox{if} \\
-gray\_level( x, y) > g\_upper \\
+( x, y)\ \in\ B\ \mbox{if} \\
+gray\_ level( x, y) > g\_ upper \\
 \mbox{Then}\ B\ \mbox{is in the weld pool if} \\
-gray\_level( x, y)\ \leq\ g\_lower\ \forall\ (x,y)\  \in\  \partial B \\ 
-\mbox{and if}\ size(B)\ <\ s\_max
+gray\_ level( x, y)\ \leq\ g\_ lower\ \forall\ (x,y) \in\ \partial B \\ 
+\mbox{and if}\ size(B)\ <\ s\_ max
 \end{eqnarray*}
 
-If $B$ is in the weld pool, the grayness level at each pixel $(x,y)$ inside $B$ is replaced by the grayness average value of the grayness level pixels of $\partial B$ (see equation \ref{equation-grayness-recouvrement}).
+If $B$ is into the weld pool, the gray value at each pixel $(x,y)$ inside $B$ is replaced by the gray average value of the gray value pixels of $\partial B$ (see equation \ref{equation-grayness-recouvrement}).
 Then the ÔÕwhiteÕÕ blob is replaced by a low average grayness level surface, similar to the rest of the weld pool grayness level.
@@
 \begin{equation}
-gray\_level( x, y) = \frac{gray\_level( x, y_{\partial B}) + gray\_level( x_{\partial B}, y) }{ 2}
+gray\_level( x, y)\ =\ \frac{gray\_level( x, y_{\partial B}) + gray\_level( x_{\partial B}, y) }{ 2}
 \label{equation-grayness-recouvrement}
@@
 
-\subsubsection{ Texture Analysis Principia}
-\label{texture-analysis-principia}
+\subsubsection{ Impurities and light reflects corrections surrounding the weld pool}
+\label{impurities-and-light-reflects-corrections-surroinding-the-weld-pool}
 
-Now, the weld pool appears as a more uniform dark surface, which contrast with the non uniform gray level values of the surrounding solid metal area.
-This particularity in the grayness level distribution (roughness) at the image could be interpreted as different textures zones \cite{MATERKA}, in the same the way as the eyes recognize the texture in the object surface and$/$or images.
+As mentioned the presence of some oxides impurities into the solid metal surface, closer to the weld pool edge, rest a mayor problem to image segmentation.
+A combination of filtering and segmentation techniques has been applied to reduce the brightness points and dark zones due to impurities presence into the roughness zone.
 
-The texture analysis method to perform image segmentation is an image processing technique widely uses in biomedicine, satellite recognition, industrial quality control and others fields requiring image processing.
-There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \cite{MATERKA}.
-The structural method requires complex logical analysis, while the transform and model based methods require mathematical analysis that required deterministic properties in grayness levels distributions \cite{MATERKA}.
-The statistical methods respond intuitively to what human eyes recognize: Two surfaces with different grayness level distribution or roughness.
+First, an impulse response filter to grayness level gradient is applied (Canny filter).
+This edge detection filter converts the grayness level images into images composed only by white segments, which represent the edges profile.
+Adjusting the filter parameters to maximum gradient detection, the canny filter read the irregular grayness level distribution as multiple grayness level gradients.
+Then the roughness surfaces are converted into irregular white segments distributions and the smoothness zone are converted into zero level zones (black zones) with some white segments, as the weld pool.
+The impurities appear as small black zones surrounded by numerous white segments into the roughness zone or solid metal surface (see image \ref{}).
 
-As has been mentioned in section \ref{segmentation}, image segmentation means split into two or more fields the image.
-One field, would be mark in one color and the rest of the image in other color \cite{COCQUEREZ}.
+The idea is replace the roughness zone by a more homogeneous white surface recovering the small black zones.
+A dilate filter have been applied (twice) to enhance the white segments up to small white surfaces reducing the small black zones corresponding to the impurities into the solid metal surface.
+This filter operate taking the maximum value over a $3\times 3$ pixel neighborhood.
+A smooth classical filter (blur) have been used to smooth the ÔÕwhite surfaces edgeÕÕ.
+This filter replaces the values of squares of $5\times 5$ pixels by their average values.
+The small black zones into the biggest white surface appears diffused due to the smoothness effect over the edges (see figure \ref{}).
+The same effect is observed into the biggest black zone (weld pool), where the small white surfaces become highly diffused.
+Then, a median filter types have been used to enhance the image by gray values region, and homogenized the surfaces.
+This filter compute the grayness median value over $5\times 5$ pixels region.
+The image is enhance in his black (weld pool) and white (solid metal) regions (see image \ref{}), resulting in more homogeneous white and black surfaces.
 
-\subsubsection{ Applying texture analysis}
-\label{appliying-texture-analysis}
+\subsubsection{Completing the image segmentation}
+\label{completing-the-image-segmentation}
 
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[Macro drop raw image]{\label{fig::photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{figure5a.png}}
-%\subfigure[Macro drop grayness image]{\label{fig::photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{figure5b.png}}\\
-%\subfigure[First smooth filter]{\label{fig::photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{figure5c.png}}
-%\subfigure[Adaptive threshold per regions]{\label{fig::photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{figure5d.png}}\\
-%\subfigure[Median filter]{\label{fig::photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{figure5e.png}}
-%\subfigure[Canny filter]{\label{fig::photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure5f.png}}\\
-%\end{center}
-%\caption{{\small Image treatment step by step of PGMAW process}}
-%\label{fig::photo-macro-drop}
-%\end{figure}
+In order to recognize and isolate the weld pool element (central black surface into the image, see image \ref{}),  a segmentation statistical algorithm have been applied.
+A small region of interest (ROI) is defined into the weld pool.
+Then the algorithm scans the image surface by regions of equal ROI size.
+The algorithm find similarities to the ROI using a normalize correlation method.
+The gray values of the resulting regions are adjusted depending their level of correlation with the ROI; $0$ gray value means non correlation at all while $255$ gray value means that it is the same surface.
+Note that the weld pool became the big central white region (see image \ref{})
+
+A threshold of type binary have been applied to enhance the edge of the white surfaces, converting the image into a binary white and black regions follows the criteria:
+
+$
+\begin{array}{l}
+gray\_ level\_ threshold(x,y) = 
+\end{array}
+\left\{ 
+\begin{array}{lcr}
+    0 & if & gray\_ level\_ original(x,y)\ <\ 200 \\
+255 & if & gray\_ level\_ original(x,y)\ \geq\ 200 
+\end{array}
+\right\} $
+
+Where $gray_level_original(x,y)$ is the gray value of a image pixel before threshold and $gray_level_threshold$ is the gray value assign to the pixel after threshold.
+
+Finally a Canny filter has been applied to extract the principal edges presents in the image.
+Note that for a binary image all edges are principal, therefore Canny detect all edges presents into the image (see figure \ref{}).
 
@@
 
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[t1 ]{\label{fig::photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure6a.png}}
-%\subfigure[t2 ]{\label{fig::photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure6b.png}}\\
-%\subfigure[t3 ]{\label{fig::photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure6c.png}}
-%\subfigure[t4 ]{\label{fig::photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure6d.png}}\\
-%\end{center}
-%\caption{{\small Images series of macro drop profiles}}
-%\label{fig::photo-results-macro-drop}
-%\end{figure}
-%
-%               
-%                                  
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[t = ]{\label{fig::photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure7a.png}}
-%\subfigure[t = ]{\label{fig::photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{figure7b.png}}\\
-%\end{center}
-%\caption{{\small Images series of macro drop profiles}}
-%\label{fig::photo-results-droplet}
-%\end{figure}
+Despite the performance achieved by the image processing, the canny filter generates many edges or strings into the image.
+These strings are composed by white points and are interpreted by the algorithms as individualÕs points.
+In order to automate the weld pool edge extraction process, geometrical and graph algorithms have been used to connect the points belonging to the weld pool border, convert it into connected segments and compute the area surrounded by the segments.
 
-A graph algorithm connects this segment and finds the longest closer segment.
- The longest closer segment corresponds to the metal transfer drop profile 
-(see figure \ref{fig::photo-results-droplet}).
+Note that the weld pool appears as the biggest closer string into the image (see figure \ref{}). The idea is to build segments around the string and take the longest closer set of segments.
 
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[t1 ]{\label{fig::photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure8a.png}}
-%\subfigure[t2 ]{\label{fig::photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure8b.png}}\\
-%\subfigure[t3 ]{\label{fig::photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure8c.png}}
-%\subfigure[t4 ]{\label{fig::photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure8d.png}}\\
-%\end{center}
-%\caption{{\small Images series of macro drop profiles}}
-%\label{fig::photo-results-droplet}
-%\end{figure}
+Give $S$ the set of points into the space image.
+The segments could be built between wherever two points of $S$.
+However to fulfill the strings with segments, only the points placed together could define a segment.
+To choose the correct point of $S$ a Delaunay Triangulation is made over $S$ \cite{CGAL}.
+Each point of $S$ is a vertex of a triangle and then each potential segment is an edge of a triangle.
+The Delaunay triangulations guarantees a unique solution with minimal internal angles for each triangle, which means minimal length sides to the triangles \cite{BERG}.
+Give $\beta$ the string surrounding the external hull of the Delaunay triangulation of $S$.
+An alpha shape algorithm uses a  $\alpha\ \in\ N$ parameter, or square radius of a test  circle, to travel from outside $\beta$ to inside the triangulation.
+The  circle has to go  through the triangles sides without  touching  the vertices.
+Give $n$ the number of triangles  sides of the triangulation and $l_{i}$ with $i\ \in\ {1,n}$ the length  of each side, if $\sqrt{\alpha}\ >\ l_{i}$ with $i\ \in\ {1,n}$ , a segment is marked between the respective vertices or points.
+At the end of the process, a set of segments knows as $\alpha$-shape has been created.
+Note if $\sqrt{\alpha} > l_{i}\ \forall\ i$, the circle can not go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL}.
+If $\sqrt{\alpha}\ <\  l_{i}\ \forall\ i$ the circle go through every side in the triangulation, then  no segment  is created and $\alpha$-shape became $S$.
+The points that compound the weld pool borders are all contact neighbors.
+Then $\alpha\ =\ 1$ is sufficient to create a segment set around the droplet (see figure \ref{}).
+
+A graph algorithm connects these segments and finds the longest closer segment. The longer closer segment corresponds to the weld pool perimeter (see figure \ref{}).
 

### 2011-06-21 examples/melt_pool_TIG/fusion_bain_python.cpp

@@ -33,7 +33,7 @@ int main( int hola, char** file_name)
   //rec_tem.x = 14; rec_tem.y = 20; rec_tem.width = 5; rec_tem.height = 5;
   erTemplP templ(SQDIFF_NORMED, rec_tem, true); 
   erAlphaP alp(1);
-  erWeldPoolAnalysis wpa("full_bain_3");
+  erWeldPoolAnalysis wpa("full_bain_4");
 
   wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
   wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);
@@ -51,13 +51,16 @@ int main( int hola, char** file_name)
 //     };
 //   wpa.saveParameters( "result/test.out");
 //=======
-  wpa.doIt( "example_full_bain_1.bmp");
-  wpa.doIt( "example_full_bain_2.bmp");
-  wpa.doIt( "example_full_bain_3.bmp");
+  //wpa.doIt( "example_full_bain_1.bmp");
+  //wpa.doIt( "example_full_bain_2.bmp");
+
+  wpa.doIt( "example_full_bain_4.bmp");
+  std::cout << "HOLA_1" << std::endl;
+
   erSmootP p12(BLUR,7), p22(MEDIAN,7);
   erThresP thr2(THRESH_BINARY_,215,255); 
   wpa.defineParameters( rect, whi, p12, p22, cann, dil, thr2, templ, alp);
-  wpa.doIt( "example_full_bain_4.bmp");
+  //wpa.doIt( "example_full_bain_4.bmp");
 //>>>>>>> .r124
   
   return(0);

### 2011-06-21 src/erCvAnalysis.cpp

@@ -502,15 +502,23 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
   boost::tie(ea, loaded) = erLoadImage( file_name);
   if( !loaded) return false;
 
-  eb = erConvertToBlackAndWhite( &ea);
-  erSaveImage( &eb, file_name, nom);
- 
+
+  eb = erConvertToBlackAndWhite( &ea); 
+  char* nomc= const_cast< char*>( (output_name+"b&w").c_str());
+  erSaveImage( &eb, file_name, nomc);
+  erShowImage( "b&w", &eb);
+
   erWhiteBlobCorrection( &eb, &param_white_blob);
+  nomc = const_cast< char*>( (output_name+"blob").c_str());
+  erSaveImage(&eb,file_name,nomc);
+  erShowImage( "blob", &eb);  
   
+
   if( _with_calibration)
     {
       ec = _calibration.transform_image(eb);
-      erSaveImage(&ec,file_name,nom);
+      //erSaveImage(&ec,file_name, nom+'calib');
+      //erShowImage( "calib", &ec);
     }
   else
     {
@@ -520,35 +528,60 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
   ed = erDef_ROI( &ec, &rectOI);
   
   erCvCanny( &ed, &param_canny);
- 
+  nomc= const_cast< char*>( (output_name+"canny").c_str());
+  erSaveImage( &ed, file_name, nomc);
+  erShowImage( "canny", &ed); 
+
   erCvDilate( &ed, &param_dilate);
+  nomc= const_cast< char*>( (output_name+"dilate").c_str());
+  erSaveImage( &ed, file_name, nomc);
+  erShowImage( "dilate", &ed);
 
   erCvSmooth( &ed, &param_smooth1);
+  nomc= const_cast< char*>( (output_name+"blur").c_str());
+  erSaveImage( &ed, file_name, nomc);
+  erShowImage( "blur", &ed);
 
   erCvSmooth( &ed, &param_smooth2);
+  nomc= const_cast< char*>( (output_name+"median").c_str());
+  erSaveImage( &ed, file_name, nomc);
+  erShowImage( "median", &ed);
 
   ee = erCvTemplate( &ed, &param_template);
+  nomc= const_cast< char*>( (output_name+"temp").c_str());
+  erSaveImage( &ee, file_name, nomc);
+  erShowImage( "temp", &ee);
 
[…]

### 2012-01-19 articles/TIG/doc_broullion/latex/paper_bain5.tex

--- 2011-06-21 articles/TIG/paper_bain3.tex
@@
 \title[Image Processing  for edge detection during GTAW]
-{Image Processing and geometrical analysis for edge detection during Gaz Tugnsten Metal Arc Welding}
+{Image Processing and geometrical analysis for edge detection during Gaz Tungsten Metal Arc Welding}
 
@@
 \begin{abstract}
-The paper describes some new image treatment algorithm used to 
+This paper describes some new image treatment algorithm used to 
 detect profiles during arc welding process. The new algorithm 
@@
 Gas Tungsten Arc Welding (GTAW), which uses a non-consumable tungsten electrode and an inert gas for arc shielding, is an extremely important arc welding process.
-It is commonly used for welding hard-to-weld metals such as stainless steel \cite{JUANG} and widely use in modern and basic industries.
+It is commonly used for welding hard-to-weld metals such as stainless steel \cite{JUANG} and is widely use in modern and in basic industries.
 To achieve good weld quality in GTAW process, several weldment characteristics or objects should be sensed and controlled \cite{DOUMANIDIS}.
-It is shown that the geometry of the weld pool, in particular his shape and size, contains sufficient information about weld penetration to evaluate the weld quality \cite{ZHANG}.
+It has been shown by Zhang et al \cite{ZHANG} that the geometry of the weld pool, in particular his shape and size, contains sufficient information about weld penetration to evaluate the weld quality.
 Furthermore it has been shown that the welding arc parameters to simulation and weld quality are directly relate to the weld pool geometry \cite{LU}.
 Basically the weld pool object is the key in quality control to automated welding process \cite{KOVACEVIC}. 
-According to this a better comprehension of weld pool behavior presents a GTAW process, could help to improve numerical simulations and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
+According to this a better comprehension of the weld pool behavior presents a GTAW process, could help to improve numerical simulations and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
 
-Many studies have been realized using visual sensing techniques to observe weld pool image \cite{BAE}.
-Optical sensors like high speed CCD cameras and lighting systems have been widely use in GTAW process to realize image acquisition \cite{GUANGJUN}, control process \cite{BAE} and parametric studies \cite{BALSAMO}.
+Many studies has been realized using visual sensing techniques to observe weld pool image \cite{BAE}.
+Optical sensors like high speed CCD cameras and lighting systems has been widely use in GTAW process to realize image acquisition \cite{GUANGJUN}, control process \cite{BAE} and parametric studies \cite{BALSAMO}.
 However, the extremely noisy environment require image processing techniques to extract useful information from visual scenes, which play a critical role in the weld pool analysis \cite{WANG}.
@@
 Previous work has shown that is possible to perform geometrical analysis in weld pools \cite{WU1}.
-Parameters such as weld pool contour and surface has been detected and measure using different and specifics processing images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}.
-However, to date, effectively automatic images processing of GTAW process has not been developed, possibly due to the level difficulty involved for welding researchers \cite{WANG}.
+Parameters such as weld pool contour and surface has been detected and measured using different and specifics processing images algorithms \cite{KOVACEVIC}, \cite{WU1}, \cite{SAEED}.
+However, to date, effectively automatic images processing of GTAW process has not been developed, possibly due to the level difficulty involved for the welding researchers \cite{WANG}.
 
 To perform geometrical analysis in weld pool; a multipurpose C++ based library (erCv) has been developed by the Weld/Assembly group of LMGC laboratory.
-These library results from selected functions join from highly reliable open source libraries to images treatment, geometrical analysis, graph theory applications and image visualization.
+In the construction of this library we employed highly reliable open source libraries for image treatment, geometrical analysis, graph theory applications and image visualization.
 
-In a first step, and despite the different static and dynamic weld conditions, as well as different current regime, a reliable 2D profiles and geometrical parameters from weld pool, has been obtained using the mentioned library.
+In a first step, a reliable 2D profiles and geometrical parameters has been obtained from the weld pool using the mentioned library.
+This was achieved for different welding conditions: static and dynamic welding process, as well as for different current regime.
 Using this, a dimension and dimensionless analysis has been performed into a static and dynamic GTAW process.
-The intention is contribute to simplify futures numerical models of weld pool-arc interaction and quality process.
+The intention has been to contribute to simplify futures numerical models of weld pool-arc interaction and quality process.
 
@@
 
-The objective is to perform geometrical analysis of weld pool in a GTAW process.
-Notes that geometrical analysis refers to surface value and contour detection of weld pool in static and dynamic GTAW process.
+The objective has been to perform the surface value estimation and the contour detection of the weld pool in statics and dynamics GTAW process (see \ref{fig::scheme-weld-pool-parameters}).
 Techniques as pool oscillations, ultrasonic sensing or infrared sensing could indirectly detect these geometric objects.
-However to obtain more precise measurements direct methods as vision based techniques assisted with image processing may be more promising \cite{KOVACEVIC}.
-According to this, the methods choose has been the direct image acquisition by a high speed CCD camera combined with an adequate image processing technique.
+However to obtain more precise measurements, Kovacevic et al.
+suggest direct methods as vision based techniques assisted with image processing which appears more promising \cite{KOVACEVIC}.
+According to this, the methods choose has been the direct image acquisition by a high speed CCD camera combined with adequate image processing techniques.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=7cm,height=4cm]{scheme-weld-pool-parameters.png}
+\caption{{\small Overview schematics of welding objects in a GTAW process}}
+\label{fig::scheme-weld-pool-parameters}
+\end{center}
+\end{figure}
 
@@
 
-In order to this, a platform has been developed at the laboratory to perform multi-physics measures in arc welding process (see figure \ref{schema-platform}).
+In order to this, a platform has been developed at the laboratory to perform multi-physics measures in arc welding process 
+%(see figure \ref{fig::schema-platform}). 
 The platform was conceive with an automatically procedure to synchronize, to acquire, to manage and to exploit large flow of multi-physical experimental data (up to 2 Go per test).
@@
 %\caption{{\small Experimental platform and specific device}}
-%\label{schema-platform}
+%\label{fig::schema-platform}
 %\end{center}
@@
 
-To compare and analyze the data two open source numerical libraries have been developed: The BAME (multi-physics measures data base) for all general data and the erCv specific to image treatment (including the spreading of welding pool geometry during welding).
+The general data (without the image) analyzes and processing has been performed using a multi-physics measures database; a numerical open source library developed by the laboratory.
 
@@
 A $650\ nm$ laser diode has been used to light the weld process from an estimate angle of $35\ degree$.
-The laser beam width ($ $) has been enough to guarantee a homogeneous illumination of the welding process.
-The laser projected an image of welding objects (weld pool and surrounding metal substrate) by reflection to the other side of the welding place.
-At this place and aligned with the optical path of reflected laser beam, a Phantom V5.0 high speed camera has been placed in order to record the images of the process (see figure \ref{schema-montage-experimental-GTAW}).
+The laser beam width ($ ???
+$) has been enough to guarantee a homogeneous illumination of the welding process.
+The laser projects, by reflection, an image of the welding objects (weld pool and surrounding metal substrate) to the other side of the welding place.
+In this place and aligned with the optical path of the reflected laser beam, a Phantom V5.0 high speed camera has been placed in order to record the images of the process (see figure \ref{fig::scheme-adquisition-setup}).
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=7cm,height=4cm]{schema-montage-experimental-GMAW.png}
-%\caption{{\small Experimental setup to detect weld pool edges in GTAW process}}
-%\label{schema-montage-experimental-GTAW}
-%\end{center}
-%\end{figure}
+\begin{figure}
+\begin{center}
+\includegraphics[width=7cm,height=4cm]{scheme-adquisition-setup.png}
+\caption{{\small Experimental setup to detect weld pool edges in GTAW process}}
+\label{fig::scheme-adquisition-setup}
+\end{center}
+\end{figure}
 
-To enhance the image contrast of the weld objects inside the electric discharge, the intensity rate between arc light and laser diode have to be reduce.
+To enhance the image contrast of the weld objects inside the electric discharge, the intensity rate between the arc light and the laser diode must have been reduced.
 In order to this a $650\ \pm 10\ nm$ band pass filter, which correspond to the laser diode wavelength, has been placed in front of the camera lens to attenuate the arc light.
@@
 
-\subsection{Weld pool geometrical parameters}
-\label{weld-pool-geometrical-parameters}
+\subsection{Image treatment library}
+\label{image_treatment_library}
 
-The purpose is to study the evolution of weld pool object surface and shape in a GTAW process.
-Therefore it is necessary to detect the contour of the weld pool and calculate the surface area enclose by this.
+In order to solve the mentioned limitations of the image acquisition technique and to perform geometrical analysis above the weld elements, a multipurpose image processing library has been developed and is currently use at the laboratory.
+This library, called erCv, can manage different kinds of image acquisition (optical setup).
+And therefore is able to perform edge detection and geometrical analysis in different welding elements such as macro drop, droplets and weld pool.
+The library is implemented in an oriented object C++ language.
+Then, erCv is a scalable and portable library able to perform real time contour detection.
+The library is implemented in C++ with some bindings in python, making it relatively convivial to use for non-programmers.
+To manage the edge detection during welding process, four processing modules compose the library (see figure \ref{fig::scheme-structure-library}):
+\begin{description}
+\item[Image Treatment:] Due to weld process conditions such arc lightening, heat and electrodes positions; the raw image registered by CCD camera are not calibrated and present light inhomogeneities and noise.
+In order to obtain the real shape and size of the welding elements, this module includes calibration algorithms.
+To detect the welding elements contours it is necessary to improve the welding images.
+This module has the pre-processing treatments for noise reduction and image enhancement.
+Then to start the edges detection process, this module includes processing algorithms as segmentation by samples comparator, watershed transformation, filters edge detectors and histogram based methods.
+Most of the functionality comes from \cite{OPENCV}.
+\item[Geometrical Treatment and Analysis:] This module convert the isolated points of the edges pixels into connected segments to conclude the edge detection process, completing and in some cases extrapolating the welding elements edge.
+It is also responsible to compute the geometrical data of welding elements such weld pool surface and metal transfer drop volumes.
+  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms such as triangulations and mesh generation, alpha shape and convex hull generation and polygonal structures.
+\item[Graph Theories:] To compute the geometrical data of welding elements it is necessary to extract the profile contour of the welding element from the image; this require some criteria such as continuity, length or closing condition.
+Applying these criteria, this module use graph algorithms to identify and to select the welding element contour.
+This module is composed by connected segments, estimates minimal cut, determine largest chain segments and others algorithms.
+   The algorithm of \cite{BOOSTGRAPH} are used.
+\item[Visualization:] This module is a set of functions used to execute, show and/or register the different steps at the image processing.
+\end{description}
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=7cm,height=4cm]{schema-erCv.png}
-%\caption{{\small Overview schematics of welding objects in a GTAW process}
-%\label{schema-macro-drop-droplet-parameters}
-%\end{center}
-%\end{figure}
+\begin{figure}
+\begin{center}
+\includegraphics[width=10cm]{scheme-structure-library.png}
+\caption{{\small Flow diagram of erCv library composition}}
+\label{fig::scheme-structure-library}
+\end{center}
+\end{figure}
 
-At figure \ref{figure_1} appears the geometrical elements to be study at the weld pool: the weld pool contour and surface area.
+The originality of the library comes from the aggregation and complementarities of the different numerical tools.
+The main difficulty is to find algorithms with good parameters all along the process.
 
@@
 
-Some definitions and brief description of general principles used in
- image processing are required to measure the profiles. Then, the design of the library 
-mixing different techniques
-is briefly detailed  to detect the profile in the noisy environment.
+Some definitions and a brief description of the general principles used in image processing are required to better understand how erCv perform the geometrical analysis of the weld pool, despite the noisy environment.
 
@@
 
-A numerical grey image can be described as 3D surface divided by a grid mesh
- in the X,Y plane. Each square represents a pixel and the relief surface at Z axis,
- the grey level. 
-A strong relief change or high gradient grey values at
- the image are perceived by human eyes as light changes, and can be interpreted
- as objects edges.
+A numerical grey image can be described as a 3D surface divided by a grid mesh in the $(X,Y)$ plane. Each square represents a pixel and the relief surface in $Z$ axis the grey level. 
+A strong relief change at the image, or high gradient of grey values in the plane $(X,Y)$, are perceived by human eyes as light changes and can be interpreted as objects edges.
 
-Sometimes, a regular relief patrons or regular greyness level
- variation can be distinguished. The human eyes can perceive these patrons as texture 
-and interpret the space between different textures zones as edges.
-There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
- Most of them can be classified by the way  is operated above the image pixels and grayness level.
+Sometimes, a regular relief patrons or regular grayness level variation can be distinguished.
+The human eyes can perceive these patrons as texture and interpret the space between different textures zones as edges.
+There exist a large spectrum of algorithms to perform image treatment, in particular for edges detection.
+Most of them can be classified in the way that they operate above the image pixels and grayness level.
 
@@
 
-The filters are algorithms that operate as mathematical functions $f$ above the 
+The filters are algorithms which operates as mathematical functions $f$ above the 
 $X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
-$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
-Different kind of filters can be mentioned as median, Gaussian, impulse,
- adaptive and others. The impulse filters such Canny are 
-widely use to edge detection \cite{COCQUEREZ}. These filters have an
- impulse response to most important grayness level gradient in the 
-image; this allows the filter a better edges localization
- (see figure \ref{fig::photo-explication-filter}). 
-For this reason, Canny filter is widely 
-used in the library to detect the welding elements edges. 
-However, it is sensible to noise or secondary grayness gradients in the image
- and, in consequence, it have some difficulties to define closed surface.
+$f(X)$ or $f(Y)$)  modifying his grayness value or $Z$ component. 
+Different kind of filters can be mentioned as median, Gaussian, impulse, adaptive and others.
+The impulse filters, such as Canny, are widely uses to perform edge detection \cite{COCQUEREZ}.
+These filters have an impulse response to most of the important grayness level gradient in the image; this allows the filter a better edges localization (see figure \ref{fig::image-explanation-filter}).
+For this reason, Canny filter has been extensively used into the library to detect welding elements edges. 
+However, the Canny filter is sensible to noise or secondary grayness gradients in the image and, in consequence, it have some difficulties to define closed surface.
 
@@
 
-Curve propagation is a popular technique in image analysis for object extraction,
- object tracking, edge detection and others (see figure 
-\ref{fig::photo-explication-snake}). The central idea behind such an approach
- is to evolve a curve towards the lowest potential of a cost function. 
-However at each stage of curve evolution, each curve point potential has
- to be computed. A lot of point (better curve resolution) take a lot 
-computing time, and therefore are not yet apply to real time detection
- or relatively speed automatic image processing. For this reason snake algorithms are not used in the library.
+The curve propagation is a popular technique in image analysis for object extraction, object tracking, edge detection and others (see figure 
+\ref{fig::image-explanation-snake}). The central idea behind this approach is to make evolve a curve towards the lowest potential of a cost function. 
+However at each stage of the curve evolution, the potential at each curve point has to be computed.
+A lot of point (better curve resolution) take a lot computing time, and therefore are not yet apply to real time detection or relatively high frequency automatic image processing.
+For this reason snake algorithms has not been used into the erCv library.
 
@@
 
-Let $B$ an image and let $R_{i}$ a region of $B$ such:
+Let $B$ an image and let $R_{i}$ an arbitrary region of $B$ such:
 
@@
 
-A $B$ segmentation is an image treatment which generate a $B$ partition in $R_{i}$ regions. 
-Each region is a connected set of pixels with 
-common properties (intensity, texture,...) \cite{COCQUEREZ}.
- The partition is generated by operations or comparisons methods between 
-regions. Generally, this treatment offers a good detection edges if
- the elements and surrounding area have different textures (see figure
- \ref{fig::photo-explication-segmentation}). 
-Note that different regions can belong to the same partition,
- therefore the surface is not always connected and,
- in consequence, the edges of the interest regions are not always closed.
+Perform a $B$ segmentation means perform an image treatment which generate a $B$ partition in $R_{i}$ regions. 
+Each region is a connected set of pixels with common properties (intensity, texture and others) \cite{COCQUEREZ}.
+ The partition is generated by operations or comparisons methods between regions.
+Generally, this treatment offers a good edge detection if the elements and his surrounding area have different textures (see figure \ref{fig::image-explanation-segmentation}).
+Note that different regions can belong to the same partition, therefore the surface is not always connected and, in consequence, the edges of the interest regions are not always closed.
 
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[Weld pool image in static GTAW process]{\label{fig::photo-explication-patron}\includegraphics[width=3.5cm,height=3.5cm]{figure3a.png}}
-%\subfigure[Canny filter treatment]{\label{fig::photo-explication-filter}\includegraphics[width=3.5cm,height=3.5cm]{figure3b.png}}\\
-%\subfigure[Snake treatment]{\label{fig::photo-explication-snake}\includegraphics[width=3.5cm,height=3.5cm]{figure3c.png}}
-%\subfigure[Segmentation image by 2 cluster sample comparison]{\label{fig::photo-explication-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{figure3d.png}}
-%\end{center}
-%\caption{{\small Samples of different methods technique for image processing}}
-%\label{fig::photo-explication}
-%\end{figure}
-
-\subsection{Image treatment library}
-\label{image_treatment_library}
-
-A multipurpose image processing library has been developed 
-and currently use at the laboratory, in order to analyze welding process objects.
-erCv is able to perform edge detection and geometrical analysis in a different 
-welding objects such as Macro drop, droplets and weld pool.
-The library can manage different kinds of image acquisition (optical setup). 
-The library is implemented in a oriented object C++ language.
-Then,  erCv is a scalable 
-and portable library able to perform real time
- contour detection. The library is implemented in  C++ with some bindings in python,
- making it relatively convivial to use for non-programmers.
-To manage the edge detection during welding process,
-the library is composed by four processing modules: 
-\begin{description}
-\item[Image Treatment:] Due to weld process conditions such arc lightening, 
- heat and electrodes positions; the raw image registered by CCD 
- camera are not calibrated and present light inhomogeneities and 
- noise. In order to obtain the real shape and size of weld elements, this module 
- includes calibration algorithms. To detect the welding objects contours it is 
- necessary to improve the weld element image. This module has the 
- pre-processing treatments for noise reduction and image enhancement.
- Then to start the edges detection process, this module includes processing
- algorithms as segmentation by samples comparator, watershed transformation,
- filters edge detectors and histogram based methods.  
- Most of the functionality comes from \cite{OPENCV}.
-\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
-   segments to conclude the edge detection
-  process, completing and in some cases extrapolating the weld
-  elements edge. It is also responsible to compute the geometrical 
-  data of welding elements such weld pool surface and metal transfer drop volumes. 
-  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
-  such as triangulations and mesh generation, alpha shape and 
-  convex hull generation and polygonal structures.
-\item[Graph Theories:] To compute the geometrical data of welding elements
-   it is necessary to extract the welding object edge from the image; this
-   required some criteria such as continuity, length or closing condition.
-   This module use graph algorithms to  identify and select the welding element edge using the
-   criteria. This module is composed by connected segments, estimates
-   minimal cut, determine largest chain segments and others algorithms. 
-   The algorithm of \cite{BOOSTGRAPH} are used.
-\item[Visualization:] This module is a set of 
-  functions use to execute, show and/or register the 
-  different steps at the image process.
-\end{description}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=10cm]{figure4.png}
-%\caption{{\small Flow diagram of erCv library composition}}
-%\label{fig::schema-erCv}
-%\end{center}
-%\end{figure}
-
-The originality of the library comes from the aggregation 
-and complementarity of the different numerical tools.
-The main difficulty is to find algorithms with good parameters all along the process.
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[Weld pool image in static GTAW process]{\label{fig::image-explanation-patron}\includegraphics[width=3.5cm,height=3.5cm]{image-explanation-patron.png}}
+\subfigure[Canny filter treatment]{\label{fig::image-explanation-filter}\includegraphics[width=3.5cm,height=3.5cm]{image-explanation-filter.png}}\\
+\subfigure[Snake treatment]{\label{fig::image-explanation-snake}\includegraphics[width=3.5cm,height=3.5cm]{image-explanation-snake.png}}
+\subfigure[Segmentation image by 2 cluster sample comparison]{\label{fig::image-explanation-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{image-explanation-segmentation.png}}
+\end{center}
+\caption{{\small Representative samples of the different methods technique to perform image processing}}
+\label{fig::image-explanation}
+\end{figure}
 
@@
 
-\subsection{ Image Adjustments}
-\label{image_features}
+\subsection{ First Image Adjustment}
+\label{first_image_features}
 
-Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image physical characteristics imposed by the image acquisition procedure as: image view angle and image color, has been analyzed and modified.
+It has been mentioned in section \ref{filters}, that most of the filter type algorithm (including canny filter) operates as function over the image grayness levels.
+Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image.
+In order to allow to use filters algorithm and to do more efficient the image processing, a function has been include into the treatment module to convert the color image of the weld pool into a grayness level image (see image \ref{fig::image-weldpool-greyness}).
 
-As was shown in section \ref{image-acquisition-setup}, the camera records a specular reflection of the welding process.
-Therefore the image of the welding objects is not orthogonal to the optical axes of the camera.
-In order to correct the image perspective, a function has been included in the image treatment module.
-A control image (small chessboard image with known real dimensions) is recorded at the weld pool place.
-An algorithm recognizes the chessboard corners and builds a transformation matrix between the control image (chessboard recorded image) and the original digital image.
-Finally, to calibrate the image dimension (in pixels) to the real objects dimension (in millimeters), a conversion scale is applied with the real dimensions of chessboard control image $conv = 1\ mm/ 20\ pixels$.
-
-%\begin{figure}[h!]
-%\begin{center}    
-%\subfigure[Chessboard control image]{\label{photo-calibration-cuadro-patron}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-patron.png}}
-%\subfigure[Chessboard original digital image]{\label{photo-calibration-cuadro-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-cuadro-origin.png}}\\
-%\subfigure[Raw recorded image]{\label{photo-calibration-image-origin}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-origin.png}}
-%\subfigure[Perspective corrected image]{\label{photo-calibration-image-corrected}\includegraphics[width=3.5cm,height=3.5cm]{photo-calibration-image-corrected.png}}
-%\end{center}
-%\caption{{\small Perspective image correction samples}}
-%\label{photo-calibration}
-%\end{figure}
-
-Concerning the image color, it has been mentioned in section \ref{filters}, that most of the filter type algorithm (including canny filter) operates as function over the image grayness levels.
-Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image.
-In order to allow to use filters algorithm and to do more efficient the image processing, a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[Raw image]{\label{fig::image-weldpool-original}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-original.png}}
+\subfigure[Grey level image]{\label{fig::image-weldpool-greyness}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-greyness.png}}\\
+\end{center}
+\caption{{\small Raw recording image}}
+\label{image-correction}
+\end{figure}
 
@@
 The idea is to recognize the weld pool into the raw image, extract a well define weld pool contour and therefore calculate his 2D surface area.
-Several approaches have been developed and can be used to obtain the weld pool contour.
-The edge detection techniques \cite{WU2} as level set or impulse filters, the Hough transforms \cite{OLSON} or the geometrical weld pool division \cite{KOVACEVIC}; nevertheless the most common approach is the image segmentation \cite{WANG}.
+Several approaches have been developed and can be used to obtain the weld pool contour: the edge detection techniques \cite{WU2} as level set or impulse filters, the Hough transforms \cite{OLSON} or the geometrical weld pool division \cite{KOVACEVIC}; nevertheless the most common approach is the image segmentation \cite{WANG}.
 
-Previous works \cite{WU2}, \cite{KOVACEVIC} have been showed that thanks to the optical acquisition method (specular reflection), the mirror like surface of the weld pool reflect a smoothness dark surface to the camera while the solid metal surface reflect a irregular grayness level surface.
-In the same the way as the eyes recognize the texture in a object surface and$/$or image, this particularity in the image grayness level distribution could be interpreted as roughness variations or different textures zones \cite{MATERKA}.
-And this propriety can be used to perform images segmentation dividing the image between the roughness zone and the smoothness dark zone (as the weld pool area, see figures \ref{photo-macro-drop-original}).
+Previous works \cite{WU2}, \cite{KOVACEVIC} has shown that thanks to the optical acquisition method (specular reflection), the mirror like surface of the weld pool reflect a smoothness dark surface to the camera while the solid metal surface reflect an irregular grayness level surface.
+As like as the eyes recognize the texture in a object surface and$/$or image, this particularity in the grayness level distribution at the image could be interpreted as roughness variations or different textures zones \cite{MATERKA}.
+And this propriety can be used to perform images segmentation dividing the image between the roughness zone and the smoothness dark zone (like the weld pool area, see figures \ref{fig::image-weldpool-greyness}).
 
 This technique know as texture analysis is an image processing technique widely used in biomedicine, satellite recognition, quality control and others fields requiring image processing.
-There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \ref{MATERKA}.
-The structural method requires complex logical analysis, while the transform and model based methods require the identification and analysis of deterministic properties in the grayness level distributions \ref{MATERKA}.
-Finally the statistical method compares intuitively to what human eyes recognize: surfaces with an irregular grayness level distribution or roughness, which matches to what have been observed in the recorded images (see images \ref{}).
+There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \cite{MATERKA}.
+The structural method requires complex logical analysis, while the transform and model based methods require the identification and analysis of deterministic properties in the grayness level distributions \cite{MATERKA}.
+Finally the statistical method compares intuitively to what human eyes recognize: surfaces with an irregular grayness level distribution or roughness, which matches to what has been observed in the recorded images (see images \ref{fig::image-weldpool-greyness}).
 
-However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides present in both surface: (see figure \ref{photo-macro-drop-original}), induce error in the texture analysis.
-The impurities outside the weld pool, could be interpreted as dark smoothness zone like the weld pool and not as roughness zone, while the edge of impurities and light reflections into the weld pool could be interpreted as roughness zone.
+However the low intensity contrast between the weld pool and the surrounding surface (solid metal, induce error in the texture analysis.
+It is due to the radiation from the pool, as well as the impurities or oxides present in both surfaces (see figure \ref{fig::image-weldpool-greyness}).
+The impurities outside the weld pool could be interpreted as dark smoothness zone like the weld pool and not as roughness zone, while the edge of impurities and light reflections into the weld pool could be interpreted as roughness zone.
 Therefore isolate the weld pool require more than a simply approach using one of the existing techniques.
@@
 
-Note that the impurities and the high intensities reflection appear as white blobs (high gray values set of pixels) into the dark weld pool (low gray values set of pixel, see figure \ref{photo-grayness-level}).
+Note that the impurities and the high intensities reflection appear as white blobs (high gray values set of pixels) into the dark weld pool (low gray values set of pixel, see figure \ref{fig::image-weldpool-greyness}).
 An algorithm able to detect the ÔÕwhiteÕÕ blobs into the weld pool and correct its has been developed and included into the image treatment module of erCv.
@@
 
-The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g_lower$ to define the maximal gray level of the weld pool and $s_max$ to define the blob maximum pixel sizes.
+The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g_{upper}$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g_{lower}$ to define the maximal gray level of the weld pool and $s_{max}$ to define the blob maximum pixel sizes.
 
 Call $B$ an arbitrary ÔÕwhiteÕÕ blob set, $\partial B$ his boundary and $size(B)$ his size in pixels numbers.
-Call $(x, y)$ a pixel coordinates in the image and $gray\_level( x, y)$ the pixel associate grayness level.
+Call $(x, y)$ a pixel coordinates at the image and $gray\_level( x, y)$ the pixel associate grayness level.
 
@@
 ( x, y)\ \in\ B\ \mbox{if} \\
-gray\_ level( x, y) > g\_ upper \\
+gray\_ level( x, y) > g_{upper} \\
 \mbox{Then}\ B\ \mbox{is in the weld pool if} \\
-gray\_ level( x, y)\ \leq\ g\_ lower\ \forall\ (x,y) \in\ \partial B \\ 
-\mbox{and if}\ size(B)\ <\ s\_ max
+gray\_ level( x, y)\ \leq\ g_{lower}\ \forall\ (x,y) \in\ \partial B \\ 
+\mbox{and if}\ size(B)\ <\ s_{max}
 \end{eqnarray*}
@@
 
-Using this algorithm, most of the impurities and the arc light reflections into the weld pool have been corrected.
+Using this algorithm, most of the impurities and the arc light reflections into the weld pool have been corrected (see figure \ref{fig::image-correction-weldpool-whiteblob}).
+
+\subsection{ First Image Adjustment}
+\label{first_image_features}
+
+Before to describes an effective procedure using filtering or segmentation algorithms from the erCv library, the image view angle imposed by the image acquisition procedure, have had to be modified.
+
+As shown in section \ref{image_acquisition_setup}, the camera records a specular reflection of the welding process.
+Therefore the image of the welding objects is not orthogonal to the optical axes of the camera.
+In order to correct the image perspective, a function has been included in the image treatment module.
+A control image (small chessboard image with known real dimensions) is recorded at the weld pool place (see figure \ref{fig::image-correction-chessboard-raw}).
+An algorithm recognizes the chessboard corners and builds a transformation matrix between the chessboard recorded image and the original digital image (see figures \ref{fig::image-correction-chessboard-draw}).
+This transformation matrix allows the algorithms to correct the weld pool image perspective (see figures \ref{fig::image-correction-weldpool-whiteblob}, \ref{fig::image-correction-weldpool-perspective}) Finally, to calibrate the image dimension (in pixels) to the real objects dimension (in millimeters), a conversion scale is applied with the real dimensions of chessboard control image $conv = 1\ mm/ 20\ pixels$.
+
+\begin{figure}[h!]
+\begin{center}    
+\subfigure[Chessboard control image]{\label{fig::image-correction-chessboard-raw}\includegraphics[width=3.5cm,height=3.5cm]{image-correction-chessboard-raw.png}}
+\subfigure[Chessboard original digital image]{\label{fig::image-correction-chessboard-draw}\includegraphics[width=3.5cm,height=3.5cm]{image-correction-chessboard-draw.png}}\\
+\subfigure[White blob corrected image]{\label{fig::image-correction-weldpool-whiteblob}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-whiteblob.png}}
+\subfigure[Perspective corrected image ]{\label{fig::image-correction-weldpool-perspective}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-perspective.png}}\\
+\end{center}
+\caption{{\small Perspective image correction patrons}}
+\label{image-correction}
+\end{figure}
 
@@
 First, an impulse response filter to grayness level gradient is applied (Canny filter).
-This edge detection filter converts the grayness level images into images composed only by white segments, which represent the edges profile.
+This filter converts the grayness level images into images composed only by white segments (the edges profiles).
 Adjusting the filter parameters to maximum gradient detection, the canny filter read the irregular grayness level distribution as multiple grayness level gradients.
-Then the roughness surfaces are converted into irregular white segments distributions and the smoothness zone are converted into zero level zones (black zones) with some white segments, as the weld pool.
-The impurities appear as small black zones surrounded by numerous white segments into the roughness zone or solid metal surface (see image \ref{}).
+Then the roughness surfaces are converted into irregular and dense zone with white segments distributions and the smoothness zone are converted into almost zero level zones (black zones as the weld pool).
+The impurities appear as small black zones surrounded by numerous white segments into the roughness zone or solid metal surface (see image \ref{fig::image-weldpool-canny1}).
 
 The idea is replace the roughness zone by a more homogeneous white surface recovering the small black zones.
-A dilate filter have been applied (twice) to enhance the white segments up to small white surfaces reducing the small black zones corresponding to the impurities into the solid metal surface.
+A dilate filter have been applied (twice) to enhance the white segments up to small white surfaces reducing the small black zones corresponding to the impurities into the solid metal surface (see figure \ref{fig::image-weldpool-dilate}).
 This filter operate taking the maximum value over a $3\times 3$ pixel neighborhood.
-A smooth classical filter (blur) have been used to smooth the ÔÕwhite surfaces edgeÕÕ.
+A smooth classical filter (blur) has been used to smooth the ÔÕwhite surfaces edgesÕÕ.
 This filter replaces the values of squares of $5\times 5$ pixels by their average values.
-The small black zones into the biggest white surface appears diffused due to the smoothness effect over the edges (see figure \ref{}).
+The small black zones into the biggest white surface appears diffused due to the smoothness effect over the edges (see figure \ref{fig::image-weldpool-smooth}).
 The same effect is observed into the biggest black zone (weld pool), where the small white surfaces become highly diffused.
@@
 This filter compute the grayness median value over $5\times 5$ pixels region.
-The image is enhance in his black (weld pool) and white (solid metal) regions (see image \ref{}), resulting in more homogeneous white and black surfaces.
+The image is enhance in his black (weld pool) and white (solid metal) regions (see image \ref{fig::image-weldpool-median}), resulting in a more homogeneous white and black surfaces.
 
@@
 
-In order to recognize and isolate the weld pool element (central black surface into the image, see image \ref{}),  a segmentation statistical algorithm have been applied.
+In order to recognize and to isolate the weld pool element, which now appears as a central black surface into the image (see image \ref{fig::image-weldpool-median}),  a segmentation statistical algorithm has been applied.
 A small region of interest (ROI) is defined into the weld pool.
@@
 The gray values of the resulting regions are adjusted depending their level of correlation with the ROI; $0$ gray value means non correlation at all while $255$ gray value means that it is the same surface.
-Note that the weld pool became the big central white region (see image \ref{})
+Note that the weld pool became the big central white region (see image \ref{fig::image-weldpool-segmentation})
 
@@
 
-Where $gray_level_original(x,y)$ is the gray value of a image pixel before threshold and $gray_level_threshold$ is the gray value assign to the pixel after threshold.
+Where $gray\_level\_original(x,y)$ is the gray value of a image pixel before the threshold and $gray\_level\_threshold$ is the gray value assign to the pixel after the threshold (see figure \ref{fig::image-weldpool-threshold}.
 
 Finally a Canny filter has been applied to extract the principal edges presents in the image.
-Note that for a binary image all edges are principal, therefore Canny detect all edges presents into the image (see figure \ref{}).
+Note that for a binary image all edges are principal, therefore Canny detect all edges presents into the image (see figure \ref{fig::image-weldpool-canny2}).
+
+\begin{figure}[h!]
+\begin{center}    
+%\subfigure[Raw image]{\label{fig::image-weldpool-original}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-original.png}}
+%\subfigure[Grey level image]{\label{fig::image-weldpool-greyness}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-greyness.png}}\\
+%\subfigure[White blob corrected image]{\label{fig::image-weldpool-whitblob}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-whiteblob.png}}
+%\subfigure[Perspective corrected image ]{\label{fig::image-weldpool-perspective}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-perspective.png}}\\
+\subfigure[First canny filter application]{\label{fig::image-weldpool-canny1}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-canny1.png}}
+\subfigure[Dilate application]{\label{fig::image-weldpool-dilate}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-dilate.png}}\\
+\subfigure[Smooth application]{\label{fig::image-weldpool-smooth}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-smooth.png}}
+\subfigure[Median application]{\label{fig::image-weldpool-median}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-median.png}}\\
+\subfigure[Segmentation algorithm]{\label{fig::image-weldpool-segmentation}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-segmentation.png}}
+\subfigure[Threshold application]{\label{fig::image-weldpool-threshold}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-threshold.png}}\\
+\subfigure[Second canny filter application]{\label{fig::image-weldpool-canny2}\includegraphics[width=3.5cm,height=3.5cm]{image-weldpool-canny2.png}}
+\end{center}
+\caption{{\small Perspective image correction samples}}
+\label{image-correction}
+\end{figure}
 
@@
 
-Note that the weld pool appears as the biggest closer string into the image (see figure \ref{}). The idea is to build segments around the string and take the longest closer set of segments.
+Note that the weld pool appears as the biggest closer string into the figure \ref{fig::image-weldpool-canny2}.
+The idea is to build segments around the string and take the longest closer set of segments.
 
@@
 The points that compound the weld pool borders are all contact neighbors.
-Then $\alpha\ =\ 1$ is sufficient to create a segment set around the droplet (see figure \ref{}).
+Then $\alpha\ =\ 1$ is sufficient to create a segment set around the droplet (see figure \ref{fig::image-weldpool-alphashape}).
 
-A graph algorithm connects these segments and finds the longest closer segment. The longer closer segment corresponds to the weld pool perimeter (see figure \ref{}).
+A graph algorithm connects these segments and finds the longest closer segment. The longer closer segment corresponds to the weld pool perimeter (see figure \ref{fig::image-weldpool-graphconected}).
 

### 2012-01-19 examples/melt_pool_TIG/fusion_bain.cpp

@@ -70,6 +70,7 @@ int main(int HOLA, char** file_name)
   
   erCalibration ca( "cuadro5-rescale-511.jpg", "rec_droite_256_2.bmp", 3, 3); /* Calibration des images */
   
+ 
   boost::tie(ea,loaded) = erLoadImage(name);
 
   eb = erConvertToBlackAndWhite( &ea); /* Conversion en 8 bit single channel */ 

### 2012-01-19 examples/melt_pool_TIG/fusion_bain_python.cpp

@@ -33,7 +33,7 @@ int main( int hola, char** file_name)
   //rec_tem.x = 14; rec_tem.y = 20; rec_tem.width = 5; rec_tem.height = 5;
   erTemplP templ(SQDIFF_NORMED, rec_tem, true); 
   erAlphaP alp(1);
-  erWeldPoolAnalysis wpa("full_bain_4");
+  erWeldPoolAnalysis wpa("full_bain_5");
 
   wpa.defineCalibration("calibration_source.jpg","calibration_target.bmp");
   wpa.defineParameters( rect, whi, p1, p2, cann, dil, thr, templ, alp);
@@ -55,12 +55,13 @@ int main( int hola, char** file_name)
   //wpa.doIt( "example_full_bain_2.bmp");
 
   wpa.doIt( "example_full_bain_4.bmp");
-  std::cout << "HOLA_1" << std::endl;
+  //std::cout << "HOLA_0" << std::endl;
 
   erSmootP p12(BLUR,7), p22(MEDIAN,7);
   erThresP thr2(THRESH_BINARY_,215,255); 
+ 
   wpa.defineParameters( rect, whi, p12, p22, cann, dil, thr2, templ, alp);
-  //wpa.doIt( "example_full_bain_4.bmp");
+  //  wpa.doIt( "example_full_bain_4.bmp");
 //>>>>>>> .r124
   
   return(0);

### 2012-01-19 src/erCvAnalysis.cpp

@@ -703,6 +703,7 @@ bool erWeldPoolAnalysis::doIt(std::string fich)
   if( !loaded)return false;
   doItImage(ea);
 };
+
 bool erWeldPoolAnalysis::doItImage(erImage& ea)
 {
   erImage  eb, ec, ed, ee;
@@ -711,20 +712,23 @@ bool erWeldPoolAnalysis::doItImage(erImage& ea)
   std::list< CgalSegmt> cgalSeg, bgraphSeg;
   output_name = (dir_analysis+"/"+name+"_wep");
   char* nom = const_cast< char*>( output_name.c_str());
-  eb = erConvertToBlackAndWhite( &ea); 
   
+  eb = erConvertToBlackAndWhite( &ea); 
+  //erSaveImage2(&ec, file_name, nom, "grey");
+  //erShowImage( "grey", &ec);
  
   erWhiteBlobCorrection( &eb, &param_white_blob);
-  
+  //erSaveImage2(&ec, file_name, nom, "wblob");
+  //erShowImage( "wblob", &ec);
   
   /** Modif temp */
-  erCvSmooth( &eb, &param_smooth1);
- 
+  //erCvSmooth( &eb, &param_smooth1);
+
   /** Jusque la */
   if( _with_calibration)
     {
       ec = _calibration.transform_image(eb);
-      //erSaveImage(&ec,file_name, nom+'calib');
+      //erSaveImage2(&ec, file_name, nom, "calib");
       //erShowImage( "calib", &ec);
     }
   else
@@ -735,39 +739,48 @@ bool erWeldPoolAnalysis::doItImage(erImage& ea)
   ed = erDef_ROI( &ec, &rectOI);
   
   erCvCanny( &ed, &param_canny);
- 
+  //erSaveImage2(&ec, file_name, nom, "canny1");
+  //erShowImage( "canny1", &ec);
   
   erCvDilate( &ed, &param_dilate);
- 
+  //erSaveImage2(&ec, file_name, nom, "dilate");
+  //erShowImage( "dilate", &ec);
 
-  /**
+  
   erCvSmooth( &ed, &param_smooth1);
-  nomc= const_cast< char*>( (output_name+"blur").c_str());
-  erSaveImage( &ed, file_name, nomc);
-  erShowImage( "blur", &ed);
-  */
+  //char * nomc = const_cast< char*>( (output_name+"blur").c_str());
[…]

### 2012-01-20 include/erCv/erCvAnalysis.hpp

@@ -55,6 +55,9 @@
  \brief Base class to others. Pure virtual.
 
  */
+
+typedef std::list< CgalSegmt> SegmentList;
+
 struct erAnalysis
 {
   erAnalysis( );
@@ -78,10 +81,18 @@ struct erAnalysis
 
   /** Creation de la matrix de calibration pour les images
    */
-  void  defineCalibration( std::string, std::string);
-  char*  currentFileName();
-  void   setCurrentFileName(char*);
-
+  void        defineCalibration( std::string, std::string);
+  char*       currentFileName();
+  void        setCurrentFileName(char*);
+  void        setOutputGeometryFile(std::string);
+  void        writeOutGeometry(SegmentList&);
+  std::string outputGeometryFile();
+  bool        outputGeometry();
+  bool        outputConvex();
+  void        setOutputConvex(bool);
+  void        setOuputGeometry(bool);
+  bool        outputAxisymmetricGeometry();
+  void        setOutputAxisymmetricGeometry(bool);
   /* \brief Application de l Analysis avec des parametres introduit dans le ficher de finition de l 'experiance.
    */
   virtual bool doIt     ( std::string)=0; 
@@ -92,6 +103,10 @@ struct erAnalysis
   std::string          output_name;  /** < Nom du fichier de sortie des resultats*/
   erCalibration        _calibration;
   bool                 _with_calibration;  // Pour savoir si on active la calibration
+  bool                 _output_geometry_characteristics;
+  bool                 _output_axisymmetric;
+  bool                 _output_convex;
+  std::string          _output_geometry_file;
   char* file_name;
 };
 
@@ -267,8 +282,8 @@ struct erMetalTransfertAnalysis:public erAnalysis
   void loadParameters( std::string);               /** <  Pas encore active */
 
 
-  void setOutputGeometryFile(std::string);         /** <  Methode pour reinitialiser le nom du fichier de geometrie
-						          A chaque passage, l ancien fichier est ecrase      */
+  //void setOutputGeometryFile(std::string);         /** <  Methode pour reinitialiser le nom du fichier de geometrie
+  //						          A chaque passage, l ancien fichier est ecrase      */
   CvRect         rectOI;                           /** <  Position de la zone d etude dans l image */
   erSmootP       param_smooth1, param_smooth2;     /**  
 							Premier lissage du type BLUR: Augmente ou diminue l homegenite de l image.
[…]

### 2012-01-20 include/erCv/geometry/erCgalConvexPolygone.hpp

@@ -45,7 +45,7 @@ typedef CGAL::Polygon_2<K> Polygon_2;
 typedef Polygon_2::Vertex_iterator Polygon_vertex_iterator;
 
 template< class Container, class Container2>
-void convex_hull( Container bgraphSegments, Container2& cgalPoint)
+void erConvexHull( Container bgraphSegments, Container2& cgalPoint)
 {		    
   cgalPoint =  erGeometryExtractConvexPolygon( bgraphSegments.begin(), bgraphSegments.end());
 }

### 2012-01-20 include/erCv/geometry/erGeometricalCharacteristics.hpp

@@ -36,8 +36,16 @@
 #define  _ERCV_GEOMETRICAL_CHARACTERISTICS_HPP_
 
 #include <erCv/geometry/erConstrainedTriangulation2.hpp>
+#include <CGAL/Constrained_Delaunay_triangulation_2.h>
+#include <CGAL/Delaunay_mesher_2.h>
+#include <CGAL/Delaunay_mesh_face_base_2.h>
+#include <CGAL/Delaunay_mesh_size_criteria_2.h>
 
-
+typedef CGAL::Triangulation_vertex_base_2<K> VVb;
+typedef CGAL::Delaunay_mesh_face_base_2<K> VFb;
+typedef CGAL::Triangulation_data_structure_2<VVb, VFb> CTds;
+typedef CGAL::Constrained_Delaunay_triangulation_2<K, CTds> CgalDT;
+typedef CGAL::Delaunay_mesh_size_criteria_2<CgalDT> Criteria;
 
 template<typename InputSegmentIterator>
 std::list< CgalTrian> erGeometryExtractTriangles( InputSegmentIterator debut, InputSegmentIterator fin)
@@ -47,6 +55,7 @@ std::list< CgalTrian> erGeometryExtractTriangles( InputSegmentIterator debut, In
     {
       cdt.insert_constraint(icg->source(),icg->target());
     };
+ 
   initializeID(cdt);
   discoverComponents(cdt);
   std::list<CgalTrian> triangs;
@@ -63,21 +72,67 @@ std::list< CgalTrian> erGeometryExtractTriangles( InputSegmentIterator debut, In
 };
 
 template<typename InputSegmentIterator>
+ std::list< CgalTrian> erGeometryExtractTrianglesWithMesh( InputSegmentIterator debut, InputSegmentIterator fin)
+ {
+   CgalDT cgadt ;
+   for( InputSegmentIterator icg=debut;icg!=fin;icg++)
+     {
+       cgadt.insert_constraint(icg->source(),icg->target());
+     };
+   CGAL::refine_Delaunay_mesh_2(cgadt, Criteria(0.125, 2.));
+   
+   CgalDT::Finite_edges_iterator bed,nif;
+   // std::cout << "Nbre de noeuds:" << cgadt.number_of_vertices() << std::endl;
+   // int i;
+   // std::cin >> i;
+   bed=cgadt.finite_edges_begin();
+   nif=cgadt.finite_edges_end();
+   CDT cdt;
+   for(;bed!=nif;bed++)
+     {
[…]

### 2012-01-20 include/erCv/graph/erConnectedSegments.hpp

@@ -144,21 +144,44 @@ BgraphSegmt filterMapOfSegments( BgraphSegmtMap& map_of_connected, Criteria& cri
   uint current=0;
   
   for( deb = map_of_connected.begin(); deb != map_of_connected.end(); deb++)
-    {
+    { //std::cout << "----" << deb->second.size() << " " << nmax << std::endl;
       if( crit( deb->second.begin(), deb->second.end()))
-	{	  
+      	{	  
 	  if(deb->second.size() > nmax)
 	    {
-	      nmax=deb->second.size();
+	      nmax   = deb->second.size();
 	      output = deb->second;
+	      
 	    };
-	};
+	  	};
       
     };
   
   return output;
 };
 
+
+BgraphSegmt filterLargestMapOfSegments( BgraphSegmtMap& map_of_connected)
+{
+  BgraphSegmtMap::iterator deb,fi;
+  BgraphSegmt output;
+  uint nmax=0;
+  uint current=0;
+  
+  for( deb = map_of_connected.begin(); deb != map_of_connected.end(); deb++)
+    {  
+	  if(deb->second.size() > nmax)
+	    {
+	      nmax   = deb->second.size();
+	      output = deb->second;
+	      
+	    };
+	
+      
+    };
+  
+  return output;
+};
 
 
 
@@ -169,6 +192,13 @@ void erLargestClosedPolygon( Container cgalSegmts, Container2& bgraphSegmts)
 
   SegmentsSetIsClosed criteria;
   bgraphSegmts = filterMapOfSegments( c_segment, criteria);
-}
+};
 
+template< class Container, class Container2>
+void erLargestPolygon( Container cgalSegmts, Container2& bgraphSegmts)
+{
+  BgraphSegmtMap c_segment = getConnectedSegments( cgalSegmts.begin(), cgalSegmts.end());
+
+  bgraphSegmts = filterLargestMapOfSegments( c_segment);
+};
 #endif

### 2012-01-20 src/bindings/python/Py_erCvAnalysis.cpp

@@ -392,7 +392,8 @@ void export_erCvAnalysis(){
   //                                       - erMetalTransfer
   //                                       - erMeltPool
   bp::class_< erAnalysis_wrapper, boost::noncopyable >( "erAnalysis", bp::init< >() )    
-    .def( bp::init< std::string, bp::optional< std::string > >(( bp::arg("name"), bp::arg("infofile")="info" )) )    
+    .def( bp::init< std::string, bp::optional< std::string > >(( bp::arg("name"), 
+								 bp::arg("infofile")="info"  )) )    
     .def( 
 	 "create"
 	 , (void ( ::erAnalysis::* )(  ) )( &::erAnalysis::create ) )    
@@ -400,7 +401,19 @@ void export_erCvAnalysis(){
 	 "defineCalibration"
 	 , (void ( ::erAnalysis::* )(std::string,std::string) )( &::erAnalysis::defineCalibration )
 	 , ( bp::arg("arg0"), bp::arg("arg1") ) )    
-  
+    .def(
+		 "setOutputGeometryFile"
+		 ,(void  (::erAnalysis::*)(std::string) )( &::erAnalysis::setOutputGeometryFile)
+		 ,(bp::arg("arg0") ))
+    .def(
+		 "setOutputAxisymmetricGeometry"
+		 ,(void  (::erAnalysis::*)(bool) )( &::erAnalysis::setOutputAxisymmetricGeometry)
+		 ,(bp::arg("arg0") ))	    
+	    //std::string outputGeometryFile();
+	    //bool        outputGeometry();
+	    //void        setOuputGeometry(bool);
+	    //bool        outputAxisymmetricGeometry();
+	    //void        setOutputAxisymmetricGeometry(bool);
     .def( 
 	 "doIt"
 	 , bp::pure_virtual( (bool ( ::erAnalysis::* )( std::string ) )(&::erAnalysis::doIt) )
@@ -485,16 +498,16 @@ void export_erCvAnalysis(){
 	 "saveParameters"
 	 , (void ( ::erMetalTransfertAnalysis::* )( std::string ) )( &::erMetalTransfertAnalysis::saveParameters )
 	 , ( bp::arg("arg0") ) )   
-    .def( 
-	 "setOutputGeometryFile"
-	 , (void ( ::erMetalTransfertAnalysis::* )( std::string ) )( &::erMetalTransfertAnalysis::setOutputGeometryFile )
[…]

### 2012-01-20 src/erCvAnalysis.cpp

@@ -59,8 +59,6 @@
 #include<CGAL/linear_least_squares_fitting_2.h>
 
 
-
-
 std::string ANALYSIS_EXTENSION="_erCvAnalysis";
 
 /********************************************************************
@@ -73,7 +71,8 @@ std::string ANALYSIS_EXTENSION="_erCvAnalysis";
 erAnalysis::erAnalysis( ){ };
 
 erAnalysis::erAnalysis( std::string name, std::string infofile): 
-  name( name), infoFile( infofile),_with_calibration(false)
+  name( name), infoFile( infofile),_with_calibration(false),_output_geometry_characteristics(true),
+  _output_axisymmetric(false),_output_convex(false)
 {  
   dir_analysis = name + ANALYSIS_EXTENSION;
   create( );
@@ -95,11 +94,12 @@ void erAnalysis::create()
 
 //ATTENTION erCalibration doit inclure un ficher avec les facteurs de conversion
 void erAnalysis::defineCalibration(std::string source,std::string target)
-{  char* source_c    =  const_cast<char*>(source.c_str());
-   char*  target_c   =   const_cast<char*>(target.c_str());
+{  char* source_c    = const_cast<char*>(source.c_str());
+   char*  target_c   = const_cast<char*>(target.c_str());
    _calibration      = erCalibration(source_c,target_c,3,3);
    _with_calibration = true;
 };
+
 void erAnalysis::setCurrentFileName(char* file)
 {
   file_name = file;
@@ -109,6 +109,84 @@ char* erAnalysis::currentFileName()
 {
   return file_name;
 }
+bool        erAnalysis::outputGeometry()
+{
+  return _output_geometry_characteristics;
+};
+void erAnalysis::writeOutGeometry(SegmentList& bgraphSeg)
+{ 
+  if( outputGeometry() && bgraphSeg.size() > 6)
+    {
+      std::list<CgalTrian> triangs;
+      if(!outputAxisymmetricGeometry())
+	{
+	  triangs=erGeometryExtractTriangles(bgraphSeg.begin(),bgraphSeg.end());
+	}
+      else
+	{
+	  triangs=erGeometryExtractTrianglesWithMesh(bgraphSeg.begin(),bgraphSeg.end());
+	};
+	  double area; 
+	  CgalLine  line;
+	  CgalPoint pt;
[…]
